### 2013-07-11 paper.tex
Added paper abstract

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{tipa}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{linguex}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{slashbox}

\usepackage{amsfonts}
\newcommand{\tickYes}{\checkmark}
\usepackage{pifont}
\newcommand{\tickNo}{\hspace{1pt}\ding{55}}

\newcommand*\circled[1]{%
  \tikz[baseline=(C.base)]\node[draw,circle,inner sep=0.5pt](C) {#1};\!
}

\newcommand{\iep}{\textipa{1}}
\newcommand{\bet}{\textipa{B}}
\newcommand{\schwa}{\textipa{@}}

\title{The perceptual dimensions of sonority-driven epenthesis} \\ \large{Generals Paper}}
\author{Michelle A. Fullwood}
\date{July 2013}

\begin{document}

\maketitle

\begin{abstract}

Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority.
One explanation for this is perceptual faithfulness (Fleischhacker 2002, Steriade 2006): rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
This raises the question of how to compute the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.  
In this paper, I propose that the appropriate metric is {\sc Sonority Angle}, the angle formed by the contours C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V, and apply it in analyzing two case studies of sonority-driven epenthesis, Chaha and Irish.  A comparison is made to another possible metric,
{\sc Sonority Rise} (Flemming 2008), the ratio of the gradients of the two contours, as well as to Syllable Contact, which represents an alternative, markedness-based approach to the problem of sonority-driven epenthesis. 
\end{abstract}

\newpage
\tableofcontents

\newpage

\end{document}

### 2013-07-11 paper.tex
Took out some unneeded cruft in the preamble
Changed font size
Started bibliography

@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 \usepackage[margin=1in]{geometry}
+\usepackage{fullpage}
+\usepackage{mathpazo}
 \usepackage{tipa}
@@
 \usepackage{amsmath}
-\usepackage{fullpage}
 \usepackage{linguex}
@@
 
+\makeatletter
+\newcommand\textsubscript[1]{\@textsubscript{\selectfont#1}}
+\def\@textsubscript#1{{\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
 \newcommand{\iep}{\textipa{1}}
@@
 
-\title{The perceptual dimensions of sonority-driven epenthesis} \\ \large{Generals Paper}}
+\title{The perceptual dimensions of \\ sonority-driven epenthesis}
 \author{Michelle A. Fullwood}
 \date{July 2013}
-
 \begin{document}
@@
 Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority.
-One explanation for this is perceptual faithfulness (Fleischhacker 2002, Steriade 2006): rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
+One explanation for this is perceptual faithfulness (\cite{fleischhacker.2002}, \cite{steriade.2006}): rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
 This raises the question of how to compute the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
@@
 A comparison is made to another possible metric,
-{\sc Sonority Rise} (Flemming 2008), the ratio of the gradients of the two contours, as well as to Syllable Contact, which represents an alternative, markedness-based approach to the problem of sonority-driven epenthesis.
+{\sc Sonority Rise} (\cite{flemming.2008}), the ratio of the gradients of the two contours, as well as to Syllable Contact, which represents an alternative, markedness-based approach to the problem of sonority-driven epenthesis.
 \end{abstract}
@@
 \tableofcontents
-
 \newpage
 
+\section{Introduction}
+
+\bibliographystyle{lingua}
+\bibliography{sonangle}
+
 \end{document}

### 2013-07-11 paper.tex
Switched bibliography styles
Added introduction and layout of the rest of the paper

@@
 \usepackage{fullpage}
+\usepackage{natbib}
 \usepackage{mathpazo}
@@
 Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority.
-One explanation for this is perceptual faithfulness (\cite{fleischhacker.2002}, \cite{steriade.2006}): rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
+One explanation for this is perceptual faithfulness (\cite{fleischhacker.2002,steriade.2006}): rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
 This raises the question of how to compute the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
@@
 
-\bibliographystyle{lingua}
+Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority.
+There are two broad classes of explanation within Optimality Theory for such sonority-driven epenthesis.
+
+One is faithfulness-based: the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent
+output sequence [C\textsubscript{1}VC\textsubscript{2}] is small when the cluster is of rising sonority.
+Thus, epenthesis into such a sequence incurs a smaller faithfulness cost than epenthesis into a cluster of falling sonority.
+This is the basis of the analysis proposed by Fleischhacker (2002, 2005) to explain why rising sonority obstruent-sonorant clusters are more easily epenthesised in
+to than falling sonority sibilant-stop clusters.
+
+This faithfulness-based approach raises the question of how the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] should be computed in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
+Fleischhacker's analysis rested on empirical determinations of sonority contour faithfulness, and did not attempt to determine such a relation.
+
+\citet{steriade.2006} proposed that input and output sonority contours should match in terms of whether they are rising or falling, and to what degree, but did not suggest a concrete mathematical relation.
+\citet{flemming.2008} formalizes Steriade's approach with the metric {\sc Sonority Rise}, the ratio of the gradients of the two contours.
+
+\bigskip
+
+In this paper, I suggest an alternative metric, {\sc Sonority Angle}, namely the magnitude of the angle made by the vectors C\textsubscript{1}-C\textsubscript{2} and C\textsubscript{1}-V, and explore the ramifications of this choice.
+
+{\sc Sonority Angle} makes the same broad predictions as {\sc Sonority Rise} -- that clusters of rising sonority, having a relatively small angle between the underlying sonority contour /C\textsubscript{1}-C\textsubscript{2}/ and the overt sonority contour [C\textsubscript{1}-V], are perceptually more similar to their epenthetic output, and therefore more likely to undergo epenthesis, than clusters of falling sonority.
+Crucially, however, the exact hierarchy of susceptibility of clusters to epenthesis is predicted to be different.
+
+I take two instances where the predictions of {\sc Sonority Angle} and {\sc Sonority Rise} differ and illustrate with case studies of sonority-driven epenthesis in two different languages, namely Chaha and Irish, that the predictions of {\sc Sonority Angle} are more in line with the data than those of {\sc Sonority Rise}.
+
+\bigskip
+
+The other broad class of explanation for sonority-driven epenthesis is markedness-based.
+Syllable Contact \cite{murray.vennemann.1983} holds that across a syllable boundary, falling sonority clusters are more harmonic than rising sonority ones.
+Hence, rising sonority clusters are preferentially broken up by epenthesis.
+
+Syllable Contact forms the basis for the main existing analysis of Chaha epenthesis by \citet{rose.2000}.
+I show that the faithfulness-based analysis, powered by the metric of {\sc Sonority Angle}, is more economical.
+In the case of Irish, Syllable Contact makes incorrect predictions regarding the data.
+
+\bigskip
+
+The layout of this paper is as follows.  Section \ref{theoreticalmachinery} lays out the theoretical background for the sonority contour faithfulness approach to 
+sonority-driven epenthesis. I introduce the proposed {\sc Sonority Angle} metric as well as the competing {\sc Sonority Rise} metric \cite{flemming.2008}, 
+then lay out the alternative markedness-based approach to sonority-driven epenthesis, namely {\sc Syllable Contact}.
+
+Section \ref{irish} consists of a case study of sonority-driven epenthesis in Irish.
+Similarly to Irish, I show that the data are in line with the predictions of {\sc Sonority Angle} and not {\sc Sonority Rise}, while a Syllable Contact-based analysis would have to be very complicated to explain the same facts.
+
+Section \ref{chaha} is a major case study of epenthesis positioning in Chaha.  I detail the facts of epenthesis positioning in Chaha, based on the data given in \citet{rose.2000},
+and show that the sonority contour faithfulness approach explains these facts, with {\sc Sonority Angle} as the metric for comparing sonority contours.
+I compare it to {\sc Sonority Rise} and show that the former is the more successful analysis, and that overall, the approach just outlined is more economical than the
+Syllable Contact-based approach of \citet{rose.2000}.
+
+Section \ref{issues} looks at various issues regarding {\sc Sonority Angle}, such as its robustness.
+Section \ref{conclusion} concludes.
+
+\section{Theoretical machinery} \label{theoreticalmachinery}
+
+\section{Case study: Irish} \label{irish}
+
+\section{Case study: Chaha} \label{chaha}
+
+\section{Issues} \label{issues}
+
+\section{Conclusion} \label{conclusion}
+
+\bibliographystyle{unified}
 \bibliography{sonangle}

### 2013-07-11 paper.tex
Added SonAngle definition

@@
 
-\section{Theoretical machinery} \label{theoreticalmachinery}
+\section{Theoretical background} \label{theoreticalmachinery}
+
+This paper assumes as its basis the P-map hypothesis \cite{steriade.2001}, which states that the perceptual distance between underlying representations and potential surface forms projects a fixed ranking of faithfulness constraints.
+
+In order to determine what faithfulness constraints exist in {\sc Con} and what their rankings should be, therefore, we need to know the metrics of perceptual distance that are relevant to each change.
+In the case of vowel epenthesis, the perceptual distance to be measured is between two sonority contours, /C1-C2/ and [C\textsubscript{1}-V-C\textsubscript{2}].
+
+\subsection{Sonority Angle}
+
+The observation with which we started was that the more steeply rising the sonority profile of a consonant cluster, the more likely the cluster to undergo epenthesis.
+Thus the absolute difference in sonority between C\textsubscript{1} and C\textsubscript{2} must be factored into the metric.
+To this, I add the claim that the more sonorous C\textsubscript{1}, the more likely the cluster is to undergo epenthesis.
+
+These two factors are neatly captured by the metric {\sc Sonority Angle}, which is defined as the angle between the underlying C\textsubscript{1}C\textsubscript{2} sonority contour and the surface C\textsubscript{1}V contour:
+
+\ex. \label{sonangle_picture} \begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
+                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+                      \node[left] at (0,3) {C$_1$}; 
+                      \node[right] at (5,1) {C$_2$};
+                      \node[right] at (5,6) {V};
+    \coordinate (A) at (0,3);
+    \coordinate (B) at (5,1);
+    \coordinate (C) at (5,6);
+\end{tikzpicture}
+
+Assuming that the horizontal distance is 1 unit, we can compute the magnitude of this angle analytically with the following formula:
+
+\ex. \label{sonangle_formula} Formula: \textsc{SonAngle} = $arctan(V-C_1) - arctan(C_2-C_1)$
+
+In the diagram in \ref{sonangle_picture}, imagine fixing C\textsubscript{1} and lowering the sonority of C\textsubscript{2}.
+Intuitively, this increases the {\sc Sonority Angle}.
+The dependence of {\sc Sonority Angle} on this distance can also be seen in the second term in \ref{sonangle_formula}.
 

### 2013-07-11 paper.tex
Added further exposition on Sonority Angle

@@
 
-In the diagram in \ref{sonangle_picture}, imagine fixing C\textsubscript{1} and lowering the sonority of C\textsubscript{2}.
-Intuitively, this increases the {\sc Sonority Angle}.
+Let us verify that {\sc Sonority Angle} does indeed reflect the two generalisations we wish to make:
+first, that the smaller the sonority distance between C\textsubscript{1} and C\textsubscript{2},
+the smaller the sonority angle.
+Imagine fixing C\textsubscript{1} as in \ref{sonangle_picture} and raising the sonority of C\textsubscript{2}. Intuitively, this decreases the {\sc Sonority Angle}, comparing the two below.
+
+\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % left diagram
+                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
+                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+                      \node[left] at  (0,3) {C$_1$}; 
+                      \node[right] at (5,1) {C$_2$};
+                      \node[right] at (5,6) {V};
+					  % right diagram
+                      \draw (20,4) -- (15,3) -- (20,6) ; % falling sonority
+                      \node at (17.5, 4.0) {$\theta$}; % theta label for falling sonority
+                      \node[left] at (15,3) {C$_1$}; 
+                      \node[right] at (20,4) {C$_2$};
+                      \node[right] at (20,6) {V};
+\end{tikzpicture}
+
 The dependence of {\sc Sonority Angle} on this distance can also be seen in the second term in \ref{sonangle_formula}.
+
+The second generalisation is that the more sonorous the C\textsubscript{1}, the more likely
+epenthesis is to occur. This time, fix C\textsubscript{2} and lower the sonority of C\textsubscript{1}.
+
+\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					  % left diagram
+                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
+                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+                      \node[left] at  (0,3) {C$_1$}; 
+                      \node[right] at (5,1) {C$_2$};
+                      \node[right] at (5,6) {V};
+					  % right diagram
+                      \draw (20,1) -- (15,1) -- (20,6) ; % falling sonority
+                      \node at (17, 1.9) {$\theta$}; % theta label for falling sonority
+                      \node[left] at (15,1) {C$_1$}; 
+                      \node[right] at (20,1) {C$_2$};
+                      \node[right] at (20,6) {V};
+\end{tikzpicture}
+
+While the difference is less clear visually, the second angle is larger.
+The first term in the formula confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.
+
+Given a sonority scale where classes of consonants are mapped to a numerical sonority, we can now calculate
+the {\sc Sonority Angle} for any cluster, which can be thought of as the faithfulness cost of epenthesising
+between the two consonants.  Examples of the calculation are given below.
+
+In this paper, I adopt (with, later, minor modifications) the following standard scale:
+
+\ex. \label{standardsonorityscale} 
+      \begin{tabular}{cccccc}
+         T & F & N & R & G & V \\
+         stop & fricative & nasal & liquid & glide & vowel \\
+         1 & 2 & 3 & 4 & 5 & 6 \\
+      \end{tabular}
+
+The {\sc Sonority Angles} for NT, TT and TN are calculated as follows.
+
+\ex. \a. \textsc{SonAngle}(NT) =  $arctan(6-3) - arctan(1-3)$ = 2.35
+     \b. \textsc{SonAngle}(TT) =  $arctan(6-1) - arctan(1-1)$ = 1.37
+     \c. \textsc{SonAngle}(TN) =  $arctan(6-1) - arctan(3-1)$ = 0.27
+
+The larger the {\sc Sonority Angle}, the larger the faithfulness cost. We therefore expect it to be hardest to epenthesise into NT out of these three clusters, and easiest to epenthesise into TN.
+
+We formalise the idea of the faithfulness cost by defining a family of \textsc{Ident} constraints that penalise outputs that incur faithfulness costs of greater than a certain $n$.
+
+\ex. \textsc{Ident(SonAngle)}$<n$: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
+stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$. % TODO: change to it being a property of C1?
+
+These faithfulness constraints have a universal ranking, with the least stringent the highest-ranked.
+
+   \ex. ... \newline
+            $\gg$ \textsc{Ident(SonAngle)}$<$1.5 \newline
+            $\gg$ \textsc{Ident(SonAngle)}$<$1.0 \newline
+            $\gg$ \textsc{Ident(SonAngle)}$<$0.5 \newline
+            $\gg$ ...
+
+Note that I do not claim that this is the only dimension of perceptual similarity relevant to epenthesis.  
+As we will see later in the paper, other faithfulness constraints may prevent epenthesis, such as a restriction on epenthesising a vowel between two obstruents, which introduces an additional region of sonorance that had previously not existed \cite{flemming.2008}.
 

### 2013-07-11 paper.tex
Completed Sonority Angle section

@@
 \newcommand{\schwa}{\textipa{@}}
+
+\include{diagrams}
 
@@
 \citet{steriade.2006} proposed that input and output sonority contours should match in terms of whether they are rising or falling, and to what degree, but did not suggest a concrete mathematical relation.
-\citet{flemming.2008} formalizes Steriade's approach with the metric {\sc Sonority Rise}, the ratio of the gradients of the two contours.
+\citet{flemming.2008} formalises Steriade's approach with the metric {\sc Sonority Rise}, the ratio of the gradients of the two contours.
 
@@
 
-Note that I do not claim that this is the only dimension of perceptual similarity relevant to epenthesis.  
-As we will see later in the paper, other faithfulness constraints may prevent epenthesis, such as a restriction on epenthesising a vowel between two obstruents, which introduces an additional region of sonorance that had previously not existed \cite{flemming.2008}.
+The resulting hierarchy of clusters, ranked according to their resistance to epenthesis as defined
+by their {\sc Sonority Angle}, is as follows.
+
+\ex. {\sc Sonority Angle} hierarchy
+
+\vspace{-3em}
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressed}}
+
+Notice that out of the falling sonority clusters, those that decrease in sonority by a single step
+-- namely RN, NF and FT -- have smaller {\sc Sonority Angles} than the ones that have a greater fall
+in sonority.
+Furthermore, out of these three clusters, theone with the most sonorous C\textsubscript{1}, RN, has the smallest {\sc Sonority Angle}.
+We thus predict that out of the falling sonority clusters,
+RN is the most likely to be broken up by epenthesis. The case study on Chaha will demonstrate that this
+is the case.
+
+Similarly, between the clusters that fall in sonority by two steps -- RF and NT -- we expect
+NT to be less likely to undergo epenthesis, since N is less sonorous than R. We expect NT and RT
+to be the clusters most resistant to epenthesis out of all the clusters. This will be crucial 
+to our analysis of Irish sonority-driven epenthesis.
+
+\subsection{Another dimension of sonority contour faithfulness}
+
+Note that I do not claim that sonority contour faithfulness is the only dimension of perceptual similarity relevant to epenthesis.
+As we will see later in the paper, other faithfulness constraints may prevent epenthesis, such as a restriction on epenthesising a vowel between two obstruents, which introduces an additional region of sonorance that had previously not existed \citep{flemming.2008}.
 

### 2013-07-11 paper.tex
Completed Sonority Rise section

@@
 
+\subsection{Sonority Rise}
+
+I will contrast {\sc Sonority Angle} with an alternative metric of sonority contour faithfulness proposed by \citet{flemming.2008}, {\sc Sonority Rise}, which takes the ratio of the underlying sonority contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V].
+
+   \ex. \textsc{Sonority Rise} = $1-\frac{C_2-C_1}{V-C_1}$
+
+The following sample calculations illustrate how \textsc{SonRise} distance is computed:
+
+\ex.    \begin{center}
+    \begin{tabular}{c c | c c | c}
+    C\textsubscript{1}C\textsubscript{2}   & Rise & C\textsubscript{1}V & Rise & \textsc{SonRise} Distance\\ \hline
+    NT &  -2  &  N\textipa{1}T & 3 & $1-\frac{1-3}{6-3}=1.7$ \\
+    TT &  0   &  T\textipa{1}T & 5 & $1-\frac{1-1}{6-1}=1.0$ \\
+    TN &  2   &  T{\textipa{1}}N & 5 & $1-\frac{3-1}{6-1}=0.6$ \\ 
+    \end{tabular}
+    \end{center}
+
+As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<n$, defined similarly to {\sc Ident(SonAngle)}$<n$.
+
+{\sc Sonority Rise} also gives rise to a hierarchy of susceptbility of clusters.
+
+\ex. {\sc Sonority Rise} hierarchy
+
+\vspace{-3em}
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityrisehierarchycompressed}}
+
+Though in many ways similar to the {\sc Sonority Angle} hierarchy, it makes several crucially different predictions.
+For example, it does not share the prediction of {\sc Sonority Angle} that RN is the most likely of the falling sonority clusters to epenthesise -- rather, if RN undergoes epenthesis then we expect FT and NF to do the same.
+Furthermore, it predicts that if NT and RT fail to undergo epenthesis due to the high faithfulness cost of interrupting these clusters, then RF should also fail to undergo epenthesis.
+
 \subsection{Another dimension of sonority contour faithfulness}

### 2013-07-11 paper.tex
Began Syllable Contact section

@@
 
+\subsection{Syllable Contact}
+
+The alternative markedness-based approach to sonority-driven epenthesis that I will explore in this paper is Syllable Contact, which was first stated as the Syllable Contact Law by \citet{murray.vennemann.1983}:
+
+\ex. ``The preference for a syllabic structure $A$\$$B$, where $A$ and $B$ are marginal segments and $a$ and $b$ are the Consonantal Strength
+values of $A$ and $B$ respectively, increases with the value of $b$ minus $a$'' \citep{murray.vennemann.1983}
+
+\citet{rose.2000} reformulates this as a violable, but categorical, constraint within the context of Optimality Theory and uses it in an analysis of Chaha sonority-driven epenthesis:
+
+\ex.  \textsc{SyllCon}: The first segment of the onset of a syllable must be lower in sonority than the last segment in the immediately preceding syllable.
+
+More recently, Syllable Contact has been recast as a gradient family of constraints, for example by \citet{gouskova.2002, gouskova.2004}.
+She defines the distance {\sc Dis} between two consonants in a syllable contact situation as the sonority of the second minus the sonority of the first.
+For example, [t.s] = +1 if [s] and [t] are only one step apart on a sonority scale.
+She then defines the following family of constraints:
+
+\ex. {\sc *Dis-}$n$: Assign a violation mark if the {\sc Dis} between two adjacent heterosyllabic consonants is $n$ (adapted from \citep{gouskova.2002})
+
+This gives rise to a universal hierarchy:
+
+\ex. {\sc *Dis+7} $\gg$ {\sc *Dis+6} $\gg$ ... {\sc *Dis+0} $\gg$ {\sc *Dis-1} $\gg$ ... {\sc *Dis-7}.
+
+Thus heterosyllabic clusters that rise sharply in sonority -- that have a high {\sc Dis} -- are more marked than more falling clusters.
+
+The predicted hierarchy of susceptibility to epenthesis of the clusters is as follows:
+
+\ex. Syllable Contact hierarchy (based on {\sc *Dis}):
+
+\vspace{-3em}
+\noindent \resizebox{\linewidth}{!}{\usebox{\syllablecontacthierarchy}}
+
+\bigskip
+
+Syllable Contact applies only across syllable boundaries.
+Therefore, when sonority-driven epenthesis occurs in onsets or codas, other sonority-based markedness constraints must be employed.
+One such is {\sc Sonority Sequencing}, which we will see in the context of Rose's analysis in the next section.
+
 \subsection{Another dimension of sonority contour faithfulness}

### 2013-07-18 paper.tex
Finished Theoretical Background section

@@
 Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority.
-One explanation for this is perceptual faithfulness (\cite{fleischhacker.2002,steriade.2006}): rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
+One explanation for this is perceptual faithfulness \citep{fleischhacker.2002,steriade.2006}: rising sonority clusters are more susceptible to epenthesis because the perceptual distance between the underlying /C\textsubscript{1}C\textsubscript{2}/ sequence and its correspondent output sequence [C\textsubscript{1}VC\textsubscript{2}] is small, thus incurring a smaller faithfulness cost.
 This raises the question of how to compute the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
@@
 A comparison is made to another possible metric,
-{\sc Sonority Rise} (\cite{flemming.2008}), the ratio of the gradients of the two contours, as well as to Syllable Contact, which represents an alternative, markedness-based approach to the problem of sonority-driven epenthesis.
+{\sc Sonority Rise} \citep{flemming.2008}, the ratio of the gradients of the two contours, as well as to Syllable Contact, which represents an alternative, markedness-based approach to the problem of sonority-driven epenthesis.
 \end{abstract}
@@
 {\sc Sonority Angle} makes the same broad predictions as {\sc Sonority Rise} -- that clusters of rising sonority, having a relatively small angle between the underlying sonority contour /C\textsubscript{1}-C\textsubscript{2}/ and the overt sonority contour [C\textsubscript{1}-V], are perceptually more similar to their epenthetic output, and therefore more likely to undergo epenthesis, than clusters of falling sonority.
-Crucially, however, the exact hierarchy of susceptibility of clusters to epenthesis is predicted to be different.
+Crucially, however, the exact hierarchy of susceptibility of individual clusters to epenthesis is predicted to be different.
 
@@
 The other broad class of explanation for sonority-driven epenthesis is markedness-based.
-Syllable Contact \cite{murray.vennemann.1983} holds that across a syllable boundary, falling sonority clusters are more harmonic than rising sonority ones.
+Syllable Contact \citep{murray.vennemann.1983} holds that across a syllable boundary, falling sonority clusters are more harmonic than rising sonority ones.
 Hence, rising sonority clusters are preferentially broken up by epenthesis.
@@
 The layout of this paper is as follows.  Section \ref{theoreticalmachinery} lays out the theoretical background for the sonority contour faithfulness approach to 
-sonority-driven epenthesis. I introduce the proposed {\sc Sonority Angle} metric as well as the competing {\sc Sonority Rise} metric \cite{flemming.2008}, 
+sonority-driven epenthesis. I introduce the proposed {\sc Sonority Angle} metric as well as the competing {\sc Sonority Rise} metric \citep{flemming.2008}, 
 then lay out the alternative markedness-based approach to sonority-driven epenthesis, namely {\sc Syllable Contact}.
@@
 Section \ref{irish} consists of a case study of sonority-driven epenthesis in Irish.
-Similarly to Irish, I show that the data are in line with the predictions of {\sc Sonority Angle} and not {\sc Sonority Rise}, while a Syllable Contact-based analysis would have to be very complicated to explain the same facts.
+I show that the data are in line with the predictions of {\sc Sonority Angle} and not {\sc Sonority Rise}, while a Syllable Contact-based analysis would have to be very complicated to explain the same facts.
 
-Section \ref{chaha} is a major case study of epenthesis positioning in Chaha.  I detail the facts of epenthesis positioning in Chaha, based on the data given in \citet{rose.2000},
+Section \ref{chaha} is a case study of epenthesis positioning in Chaha.  I detail the facts of epenthesis positioning in Chaha, based on the data given in \citet{rose.2000},
 and show that the sonority contour faithfulness approach explains these facts, with {\sc Sonority Angle} as the metric for comparing sonority contours.
@@
 
-This paper assumes as its basis the P-map hypothesis \cite{steriade.2001}, which states that the perceptual distance between underlying representations and potential surface forms projects a fixed ranking of faithfulness constraints.
+This paper assumes as its basis the P-map hypothesis \citep{steriade.2001}, which states that the perceptual distance between underlying representations and potential surface forms projects a fixed ranking of faithfulness constraints.
 
@@
 Furthermore, it predicts that if NT and RT fail to undergo epenthesis due to the high faithfulness cost of interrupting these clusters, then RF should also fail to undergo epenthesis.
+Both of these predictions are contrary to the evidence of Irish and Chaha.
+
+\subsection{Another dimension of sonority contour faithfulness}
+
+Note that I do not claim that sonority contour faithfulness is the only dimension of perceptual similarity relevant to vowel epenthesis.
+For instance, I will adopt \citet{flemming.2008}'s suggestion that a further dimension of perceptual similarity restricts epenthesis to sites adjacent to a sonorant, based on patterns of epenthesis in languages such as Montana Salish, where epenthesis is disallowed between two obstruents.
+
+I will formalise this restriction with the constraint {\sc Dep(+sonorant)}.
+The epenthesis of a vowel between two obstruents, which bear the feature [$-$sonorant], necessitates the insertion of a new [+sonorant] feature, whereas when a vowel is epenthesised adjacent to a sonorant, the sonorant's [+sonorant] feature spreads and is shared between the vowel and the sonorant.
+
+This constraint will be used in the analysis of Chaha complex coda epenthesis, which in some idiolects
+cannot occur between obstruents, while in others, it can. My proposal will be that in the former, {\sc Dep(+sonorant)} is higher-ranked, thus blocking epenthesis.
 
@@
 Therefore, when sonority-driven epenthesis occurs in onsets or codas, other sonority-based markedness constraints must be employed.
-One such is {\sc Sonority Sequencing}, which we will see in the context of Rose's analysis in the next section.
-
-\subsection{Another dimension of sonority contour faithfulness}
-
-Note that I do not claim that sonority contour faithfulness is the only dimension of perceptual similarity relevant to epenthesis.
-As we will see later in the paper, other faithfulness constraints may prevent epenthesis, such as a restriction on epenthesising a vowel between two obstruents, which introduces an additional region of sonorance that had previously not existed \citep{flemming.2008}.
+One such is {\sc Sonority Sequencing} \citep{selkirk.1984}, which states that sonority must be strictly increasing in the onset and strictly decreasing in the coda.
+\citep{rose.2000} uses two variants of this constraint, one strict and one non-strict, in her analysis of Chaha.
 

### 2013-07-18 paper.tex
Added intro to Irish case study

@@
 
-The {\sc Sonority Angles} for NT, TT and TN are calculated as follows.
+The {\sc Sonority Angles} for NT, TT and TN are calculated as in the following examples.
 
@@
 
+Irish displays an unusual process of epenthesis that targets consonant clusters 
+whose first member is a sonorant \citep{carnie.1994, ni.chiosain.1999}, with the 
+exception of sonorant-voiceless stop clusters, which never undergo epenthesis. 
+I will show in this section that a {\sc Sonority Angle}-based faithfulness
+neatly captures these facts.
+
 \section{Case study: Chaha} \label{chaha}

### 2013-07-18 paper.tex
Added some basic data

@@
 
+\subsection{Data}
+
+Irish epenthesis targets sonorant-initial clusters and occurs both across syllable boundaries and in codas.
+The epenthetic vowel is [\textipa{@}] in nonpalatalised environments and [i] otherwise \citep{ni.chiosain.1999}.
+
+\ex. \a. /alb\textipa{@}/ $\rightarrow$ [al\textipa{@b@}] \\
+         {\it Alba} `Scotland'
+     \b. /dorx\textipa{@}/ $\rightarrow$ [dor\textipa{@x@}] \\
+         {\it dorcha} `dark'
+     \b. /gorm/  $\rightarrow$  [gor\textipa{@}m] \\
+         {\it gorm} `blue'
+     \b. /banb\textipa{@}/ $\rightarrow$ [ban\textipa{@b@}] \\
+         {\it Banba} `a name for Ireland'
+     \b. /kon\textipa{f@}/ $\rightarrow$ [kon\textipa{@f@}] \\
+         {\it confadh} `anger'
+     \b. /an\textsuperscript{j}m\textsuperscript{j}/ $\rightarrow$ [an\textsuperscript{j}im\textsuperscript{j}] \\
+         {\it ainm} `name'
+     \z.
+     (\citet{carnie.1994}:(37) and \citet{ni.chiosain.1999}:(2))
+
+The pattern of epenthesis outlined above does not apply to onset clusters.  Sonorant-initial clusters
+are attested in onsets.
+
+\ex. \a. [\textipa{mna:}] or [\textipa{mra:}] (depending on dialect) \\
+         {\it mn\'a} `women'
+     \b. [\textipa{m\textsuperscript{j}r\textsuperscript{j}i:ra:n}] \\
+         {\it mriath\'an} `sea-rods'
+     \z.
+     (\citet{swingle.1992}: 456)
+
 \section{Case study: Chaha} \label{chaha}

### 2013-07-18 paper.tex
More Irish analysis

@@
 \usepackage[margin=1in]{geometry}
+\usepackage[table]{xcolor}    %for shading*
 \usepackage{fullpage}
@@
 \usepackage{slashbox}
+\usepackage{pifont}    %for pointing hand
+\usepackage{arydshln}    %for dashed lines
+\usepackage{rotating}    %for angled text
 
@@
      \z.
-     (\citet{carnie.1994}:(37) and \citet{ni.chiosain.1999}:(2))
+     \citep[(37)]{carnie.1994} and \citep[(2)]{ni.chiosain.1999}
 
@@
      \z.
-     (\citet{swingle.1992}: 456)
+     \citep[456]{swingle.1992}
+
+There are two classes of exceptions to this process.  First, homorganic clusters are not broken up by epenthesis.
+
+\ex. \a. /farno\textipa{:g}/ $\rightarrow$ [farno\textipa{:g}], *[far\textipa{@}no\textipa{:g}] \\
+         {\it fearnog} `alder'
+     \b. /bord/ $\rightarrow$ [bord], *[bor\textipa{@}d] \\
+         {\it bord} `table'
+     \b. /kalr\textipa{@}/ $\rightarrow$ [kalr\textipa{@}], *[kal\textipa{@r@}] \\
+         {\it calra} `calorie'  
+     \z. 
+     \citep[(52)]{carnie.1994}\footnote{\citet{ni.chiosain.1999} has a more complicated set of facts as to which homorganic clusters are broken up by epenthesis.
+As this is not the focus of this paper, I will assume the simpler dataset that Carnie presents.}
+
+Second, epenthesis does not apply when the second consonant is a voiceless stop.
+
+\ex. \a. /kork/ $\rightarrow$ [kork], *[kor\textipa{@}k] \\
+         {\it Cork} `Cork (place name)' 
+     \b. /kork\textipa{@}/ $\rightarrow$ [kork\textipa{@}], *[kor\textipa{@k@}] \\
+         {\it corca} `people' 
+     \b. /korp/  $\rightarrow$ [korp], *[kor\textipa{@p}] \\
+         {\it corp} `body' %TODO : get some NT data in here!
+     \z.
+     \citep[(39a,b,c)]{carnie.1994}
+
+\subsection{Analysis}
+
+The fact that this process of epenthesis does not target obstruent-initial clusters is not problematic under the sonority contour faithfulness approach,
+as the {\sc Ident(SonAngle)} constraints limit epenthesis, rather than trigger it.  By choosing a more limited markedness constraint such as {\sc *Son-C},
+defined below, we can have epenthesis act only on sonorant-initial clusters.
+
+\ex. {\sc *Son-C}: Assign a violation mark for every sonorant consonant preceding another consonant.
+
+\ex. {\sc *Son-C} $\gg$ {\sc Dep}
+
+\vspace{-2em}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{gorm}/} & {\sc *Son-C} & {\sc Dep} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{gor@m} & & \cellcolor{lightgray}$\ast$ \\
+\hline b. & & \textipa{gorm} & $\ast$! & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Epenthesis does not break up onset sonorant-initial clusters.  This is likely due to the fact that
+with a small number of lexical exceptions, Irish words are stress-initial \citep[26]{o.siadhail.1989}.\footnote{With the exception of Munster Irish, where stress is attracted to syllables containing
+a long vowel or diphthong (Green 1996), but where onset clusters still are not broken up by
+epenthesis.  In this case, one would probably have to posit a positional faithfulness constraint
+protecting the word-initial cluster.}  
+Breaking up the onset cluster would result in an unstressable epenthetic vowel occupying the 
+preferred location of stress in Irish.
+
+I will assume initial stress is due to the following constraint, which is dominated only by 
+lexicon-specific constraints.
+
+\ex. {\sc Stress-Initial}: Assign a violation mark if the initial syllable of a word is not stressed.
+
+\citet{alderete.2000} proposes a general constraint {\sc Head-Dependence} against making an epenthetic segment a prosodic head, which I adopt and state informally here:
+
+\ex. {\sc Head-Dep}: Assign a violation mark for every stressed vowel not present in the input.
+
+Together, these two constraints ranking above {\sc *Son-C} predict that onset epenthesis does not occur.
+
+\ex. {\sc Stress-Initial}, {\sc Head-Dep} $\gg$ {\sc *Son-C}
+
+\vspace{-2em}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{mna:}/} & {\sc Stress-Initial} & {\sc Head-Dep} & {\sc *Son-C} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{"mna:} & & & \cellcolor{lightgray}$\ast$ \\
+\hline b. & & \textipa{"m@.na:} & & $\ast$! & \cellcolor{lightgray} \\
+\hline c. & & \textipa{m@."na:} & $\ast$! & & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
 

### 2013-07-18 paper.tex
Finished Irish SonAngle section

@@
 with a small number of lexical exceptions, Irish words are stress-initial \citep[26]{o.siadhail.1989}.\footnote{With the exception of Munster Irish, where stress is attracted to syllables containing
-a long vowel or diphthong (Green 1996), but where onset clusters still are not broken up by
+a long vowel or diphthong (Green 1996), %TODO
+but where onset clusters still are not broken up by
 epenthesis.  In this case, one would probably have to posit a positional faithfulness constraint
@@
 
+In codas and across syllable boundaries, epenthesis does not apply to homorganic clusters.  
+I suggest that this is due to the action of the Obligatory Contour Principle (OCP).  
+I adopt Walter 2007's %TODO
+formulation of the OCP, which bans successive identical oral gestures.
+A cluster such as [nt] would consist of a single oral constriction gesture at the alveolar ridge, and would not constitute a violation of the OCP.
+Splitting it by epenthesis to form [n\textipa{@}t] would require a repeated identical constriction gesture, and therefore be a violation of the OCP.
+
+\ex. OCP $\gg$ {\sc *Son-C}
+
+\vspace{-2em}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{bord}/} & OCP & {\sc *Son-C} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{bord} & & \cellcolor{lightgray}$\ast$ \\
+\hline b. & & \textipa{bor@d} & $\ast$! & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Lastly, we come to the sonority-driven aspect of the analysis.  
+Epenthesis is allowed when C1 is ``followed by a voiced stop, fricative, nasal or liquid, but not when it is followed by a voiceless stop.'' \citep{carnie.1994}
+
+This requires a revision to the standard sonority scale, splitting up voiceless and voiced stops:
+
+\ex.  \begin{center}
+   \begin{tabular}{cccccccc}
+    Voiceless stop & Voiced stop  & Fricative    & Nasal        & Liquid & Glide        & Vowel \\
+      T            &     D       &          F    &    N &    R   &   G          & V     \\
+      1            &     1.5     &          2   &    3  &    4   &   5          & 6     \\
+     \end{tabular}
+ \end{center}
+
+Now let us calculate the sonority angles for the relevant set of sonorant-initial clusters in Irish.
+
+\ex. {\sc Sonority Angles} of sonorant-initial clusters using revised sonority scale
+
+  \begin{tikzpicture}[shorten >=1pt,->,scale=0.5]
+     \tikzstyle{line} = [draw]%, -latex']
+
+        \node (NT) at (2.48619449019234 * 15, 0) {NT}; % 2.35619449019234 - repositioning for visual clarity
+        \node (ND) at (2.28183949564558 * 15, 0) {ND}; % 2.23183949564558 
+        \node (NF) at (2.03444393579570 * 15, 0) {NF};
+        \node (NN) at (1.24904577239825 * 15, 0) {NN};
+        \node (NR) at (0.60 * 15, 0) {NR}; % 0.4636476090008
+
+        \node (RT) at (2.48619449019234 * 15, 0.7) {RT};% 2.35619449019234 - repositioning for visual clarity
+        \node (RD) at (2.37743866747662 * 15, 0) {RD}; % 2.29743866747662 
+        \node (RF) at (2.19429743558818 * 15, 0) {RF}; % 2.21429743558818 
+        \node (RN) at (1.89254688119154 * 15, 0) {RN};
+        \node (RR) at (1.10714871779409 * 15, 0) {RR};
+
+    \node (axisstart) at (0.5 * 15,-1) {};
+    \node (axisend)   at (2.6 * 15,-1) {};
+    \draw (axisstart) -- (axisend);
+   \node (xaxislabel) at (2.6 * 15,-2.5) {\textsc{Sonority Angle}};
+
+  \node (dividinglinestart) at (2.43 * 15,2) {};
+  \node (dividinglineend)   at (2.43 * 15,-2) {};
+  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
+
+  \node (2pointlabel) at (2.43 * 15,-1.5) {2.3};
+
+    \end{tikzpicture} %TODO : draw arrow and mark 1.0, 1.5, 2.0, 2.5
+
+\bigskip
+
+The sonorant-voiceless stop clusters can be neatly separated from the rest of the clusters in terms of {\sc Sonority Angle}.
+The correct constraint ranking is therefore the following:
+
+\ex. {\sc Ident(SonAngle)$<$2.3} $\gg$ {\sc *Son-C} $\gg$ {\sc Ident(SonAngle)$<$2.4}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{kork}/} & {\sc Ident(SonAngle)$<$2.3} & {\sc *Son-C} & {\sc Ident(SonAngle)$<$2.4} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{kork} & & \cellcolor{lightgray}$\ast$ & \cellcolor{lightgray} \\
+\hline b. & & \textipa{kor@k} & 2.35 $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray}2.35 $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{alb@}/} & {\sc Ident(SonAngle)$<$2.3} & {\sc *Son-C} & {\sc Ident(SonAngle)$<$2.4} \\[0.5ex]
+\hline \hline c. & \ding{43} & \textipa{al@b@} & 2.29 & & \cellcolor{lightgray} 2.29 \\
+\hline d. & & \textipa{alb@} & & $\ast$! & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+A note on the nasal-voiceless stop clusters is in order here: such clusters tend to be homorganic on the surface.  
+It is therefore unclear whether such clusters failed to be broken up by epenthesis because of OCP, 
+or because of the large sonority contour faithfulness violation.  
+I argue that in general, it is for the second reason.
+
+Suppose nasal-voiceless stop clusters were banned from epenthesising because of the OCP.
+Then we would expect to see surface
+sequences of [NVP] where N and P have different places of articulation and V is an epenthetic vowel, 
+just as we see [NVB] sequences:
+
+\ex. \a. [\textipa{b\textsuperscript{j}in\textsuperscript{j}ib}] \\
+         {\it binb} `venom'
+     \b. [\textipa{ban@b@}] \\
+         {\it Banba} `Banba (a name for Ireland)'
+     \z.
+     \citep[2c]{carnie.1994}
+
+To my knowledge, no [NVP] sequences with the properties stated above exist.
+
+Further, albeit marginal, evidence comes from the existence of words with heterorganic [NP] sequences,
+which are not broken up by epenthesis.
+
+\ex. \a. [\textipa{s\textsuperscript{j}e:mt}] \\
+         {\it s\'eimt} `the act of playing music', dialectal variant of {\it seinm})
+     \b. [\textipa{k2r\textsuperscript{j}@m\textsuperscript{j}k\textsuperscript{j}}] \\
+         {\it cuirimc} `I observe, pay attention to' (Connaught dialect) \\
+     (Words found in \citet{dinneen.2007}) %TODO
+
+I conclude that in general, epenthesis does not occur in /NT/ sequences due to the large sonority angle between NT and NVT, and not to the non-existence of underlying heterorganic /NP/ clusters in the lexicon.
+
 \section{Case study: Chaha} \label{chaha}

### 2013-07-18 paper.tex
Added SonRise section to Irish

@@
 with a small number of lexical exceptions, Irish words are stress-initial \citep[26]{o.siadhail.1989}.\footnote{With the exception of Munster Irish, where stress is attracted to syllables containing
-a long vowel or diphthong (Green 1996), %TODO
+a long vowel or diphthong \citep{green.1996},
 but where onset clusters still are not broken up by
@@
 I suggest that this is due to the action of the Obligatory Contour Principle (OCP).  
-I adopt Walter 2007's %TODO
+I adopt \citet{walters.2007}'s
 formulation of the OCP, which bans successive identical oral gestures.
@@
          {\it cuirimc} `I observe, pay attention to' (Connaught dialect) \\
-     (Words found in \citet{dinneen.2007}) %TODO
+     (Words found in \citet{dineen.2007})
 
-I conclude that in general, epenthesis does not occur in /NT/ sequences due to the large sonority angle between NT and NVT, and not to the non-existence of underlying heterorganic /NP/ clusters in the lexicon.
+I conclude that in general, epenthesis does not occur in /NT/ sequences due to the large {\sc Sonority Angle} between NT and NVT, and not to the non-existence of underlying heterorganic /NP/ clusters in the lexicon.
+The epenthetic facts of Irish thus support the ranking of NT and RT clusters at the bottom of the hierarchy of susceptibility to epenthesis, which is consistent with the {\sc Sonority Angle} metric.
+
+\subsection{Comparison to other approaches}
+
+Using the same revised sonority scale, the {\sc Sonority Rise} calculations are as follows for the relevant clusters:
+
+\ex. {\sc Sonority Rises} of sonorant-initial clusters using revised sonority scale
+
+ \begin{center}
+  \begin{tikzpicture}[shorten >=1pt,->,scale=0.5]
+     \tikzstyle{line} = [draw]%, -latex']
+
+        \node (NT) at (1.66666666666667 * 15, 0) {NT}; 
+        \node (ND) at (1.5 * 15, 0) {ND}; 
+        \node (NF) at (1.33333333333333 * 15, 0) {NF};
+        \node (NN) at (1 * 15, 0) {NN};
+        \node (NR) at (0.666666666666667 * 15, 0) {NR};
+
+        \node (RT) at (2.5 * 15, 0) {RT};
+        \node (RD) at (2.25 * 15, 0) {RD}; 
+        \node (RF) at (2 * 15, 0) {RF}; 
+        \node (RN) at (1.5 * 15, 0.7) {RN};
+        \node (RR) at (1 * 15, 0.7) {RR};
+
+    \node (axisstart) at (0.5 * 15,-1) {};
+    \node (axisend)   at (2.6 * 15,-1) {};
+    \draw (axisstart) -- (axisend);
+   \node (xaxislabel) at (2.6 * 15,-1.5) {\textsc{Sonority Rise}};
+
+    \end{tikzpicture} % TODO: draw arrow and mark 1.0, 1.5, 2.0, 2.5
+ \end{center}
+
+Note that the clusters RF and RD fall between RT and NT on this scale.  Therefore, we cannot clearly separate the clusters that undergo epenthesis
+from the ones that do not if we adopt {\sc Sonority Rise} as the relevant metric.
+
+\bigskip
 

### 2013-07-18 paper.tex
Finished Irish section

@@
 
+Carnie's (1994) analysis of these facts is in terms of a Minimal Distancing Constraint with various parameter settings, such as for which direction away from the nucleus it applies (to the right in the Irish case, to account for epenthesis applying to both codas and heterosyllabic clusters).
+His preliminary analysis has distance computed according to the following sonority scale:
+
+\ex. \label{carniesonorityscale} \a. 1 - Voiceless stops
+     \b. 2 - Voiced stops
+     \b. 3 - Voiceless fricatives
+     \b. 4 - Voiced fricatives
+     \b. 5 - Sonorants
+
+with a subsequent revision where sonority is computed in terms of the number of nodes that have to be specified to obtain the appropriate manner specification.
+This computation is somewhat complicated, so I will not reproduce it here.
+The result is that sonorant-fricative and sonorant-voiced stop clusters have a sonority distance of 0, since they are each specified for a single node in the feature geometry.
+Voiceless stops have no specified nodes, so sonorant-voiceless stop clusters have a sonority distance of 1, which is the minimal distance tolerated.
+
+A sonority scale that gives nasals and liquids identical sonority values seems unlikely given measurable differences in the phonetic correlates of sonority such as intensity between liquids and nasals \citep{parker.2002}.
+This is especially so when the obstruents are spread so widely on the sonority scale.
+I will therefore explore instead an alternative sonority distance-based analysis using Syllable Contact.
+
+\bigskip
+
+We quickly see that Syllable Contact on its own is insufficient as epenthesis in Irish also affects coda clusters. We will need to invoke Sonority Sequencing.
+
+%TODO : Syllable Contact and Sonority Sequencing should not be in smallcaps unless referred to as SyllCon and SonSeq.
+
+Attempting to apply Syllable Contact to the Irish case, we immediately encounter problems.
+Firstly, it is difficult to see why markedness triggers epenthesis only in sonorant-initial clusters, as Syllable Contact predicts that obstruent-initial clusters should be even more marked.
+
+Secondly, we would need to invoke a separate set of constraints on sonority sequencing in coda clusters, and assume that the ranking of the faithfulness constraint {\sc Dep} with respect to both sets of constraints is coincidentally identical.
+
+Suppose we define a single markedness constraint that favours all falling sonority clusters regardless of their position in the syllable, i.e.
+combining Syllable Contact and Sonority Sequencing.
+We require a finer-grained metric to measure how marked a particular cluster is.
+An obvious course of action is to use \citet{gouskova.2002}'s {\sc *Dis} metric, extending its use from the heterosyllabic environment alone to all positions.
+
+Using the defined sonority scale, we expect the following markedness hierarchy of sonorant-initial clusters.
+
+\begin{center}
+  \begin{tikzpicture}[shorten >=1pt,->,scale=0.5]
+     \tikzstyle{line} = [draw]%, -latex']
+
+        \node (NT) at (2 * 5, 0) {NT}; 
+        \node (ND) at (1.5 * 5, 0) {ND}; 
+        \node (NF) at (1 * 5, 0) {NF};
+        \node (NN) at (0 * 5, 0) {NN};
+        \node (NR) at (-1 * 5, 0) {NR};
+
+        \node (RT) at (3 * 5, 0) {RT};
+        \node (RD) at (2.5 * 5, 0) {RD}; 
+        \node (RF) at (2 * 5, 0.7) {RF}; 
+        \node (RN) at (1 * 5, 0.7) {RN};
+        \node (RR) at (0 * 5, 0.7) {RR};
+
+    \node (axisstart) at (-1.5 * 5,-1) {};
+    \node (axisend)   at (3.5 * 5,-1) {};
+    \draw (axisstart) -- (axisend);
+  \node (xaxislabel) at (3.5 * 5,-1.5) {\textsc{Dis}};
+
+    \end{tikzpicture} 
+ \end{center}
+
+Even ignoring the problem of the obstruent-initial clusters, we see that sonority distance
+alone does not get us the desired result. Instead, it incorrectly predicts that if NT and RT are not 
+broken up by epenthesis, then RF and RD should not either.
+
+\subsection{Interim summary}
+
+To summarise the findings of the Irish case study: a sonority contour faithfulness account explains
+the facts quite simply, because {\sc Sonority Angle} successfully achieves a linear separation of
+the NT and RT clusters from the remaining sonorant-initial clusters, explaining why they fail to undergo
+epenthesis. The {\sc Sonority Rise} metric does not have the same property. We have also seen that a markedness-based account would have to be much more complicated to explain the same facts.
+
 \section{Case study: Chaha} \label{chaha}

### 2013-07-22 paper.tex
Added intro to Chaha and some 2C data

@@
 
+Chaha is a Southern Semitic language spoken in central Ethiopia by about 440,000 people.  
+As is common with Semitic languages, it has many underlying consonant clusters, some of which are resolved by epenthesis of the high central vowel [\textipa{1}].
+Vowel epenthesis appears to preferentially target rising and level sonority clusters over falling ones.
+The data in this section mostly comes from Rose 2000, who also provides an analysis in terms of Syllable Contact.
+
+We will use the existing sonority scale given in \ref{standardsonorityscale}, with a small modification.
+Chaha has a bilabial approximant represented by [\textipa{B}] (more precisely, \textipa{\|`B}) \citep[15]{banksira.2000} that is not as sonorous as /r/, whose realisation is tap-like \citep[181]{taranto.2001}.
+The justification for /\textipa{B}/ being less sonorous than /r/ is largely empirical, based on the epenthetic behaviour of clusters containing this sonorant \citep{405}{rose.2000}, data for which will be presented later in this paper.
+I will specify its sonority as an intermediate 3.5, under the sonority of 4 for liquids in general.
+
+\ex. Sonority scale to be used in Chaha
+
+\begin{center}
+\begin{tabular}{ccccccccccccc}
+ V & $>$ & w j & $>$ & r & $>$ & \textipa{B} & $>$ & m n & $>$ & f s z x & $>$ & t t' k k' d g \\
+ vowels & & glides & & liquids & &   & & nasals & & fricatives & & stops \\
+    V   & &    G   & &    R    & & \textipa{B} & & N & & F & & T \\
+    6   & &    5   & &    4    & &    3.5      & & 3 & & 2 & & 1 \\
+\end{tabular}
+\end{center}
+\subsection{CC clusters}
+
+Underlying two-consonant clusters in Chaha are obligatorily epenthesised into if initial, never broken up by epenthesis in medial position, while final clusters are epenthesised into if they are of rising or level sonority, or the cluster consists of [r] followed by a nasal.
+
+\ex. No onset clusters in Chaha
+     \a. \textipa{k1r@tam} `he lifted up'
+
+\ex. Tautomorphemic medial two-consonant clusters are tolerated no matter what their sonority profile
+     \a. \textipa{s1rto} `cauterise ({\sc masc pl})!'
+     \b. \textipa{n1k'mo} `pick ({\sc masc pl})!'
+     \b. \textipa{at'met'} `solidified juice from [\textipa{@s@t}] plant'
+     \z. \citep[(1a,c,d)]{rose.2000}
+
+The presentation of the patterns of epenthesis in CC\# clusters is slightly complicated by variability between idiolects.  Epenthesis is possible in all level and rising sonority clusters.  
+Among these clusters, the ones for which epenthesis is optionally unavailable are the obstruent-obstruent clusters.  Most falling sonority clusters do not undergo epenthesis,
+except [r]-sonorant clusters, which can be broken up in certain idiolects. Voicing is irrelevant
+to whether clusters undergo epenthesis.
+
+The following table summarises the data.
+
+\ex. Table showing epenthesis patterns for clusters of varying sonority patterns:
+
+\begin{tabular}{c | c c c c c}
+ \backslashbox{C1}{C2}      & Stop & Fricative & Nasal & Liquid \\ \hline
+Stop   & \textbf{OPTIONAL}   & \textbf{OPTIONAL} & \textbf{\tickYes} & \textbf{\tickYes} \\
+       & \textipa{n1g(1)d} & \textipa{d1g(1)s} & \textipa{n1k1m} & \textipa{g1d1r} \\
+       & `touch!' & `give feast!' & `pick!' & `put to bed!' \\ \hline
+Fric-  & \textbf{\tickNo} & \textbf{OPTIONAL} & \textbf{\tickYes} & \textbf{\tickYes} \\
+ative  & \textipa{k1ft}   & \textipa{mes(1)x} &    & \textipa{s1f1r} \\
+       & `open!'  & `chew!' & & `measure!' & \\ \hline
+Nasal  & \textbf{\tickNo}     & \textbf{\tickNo}     & \textbf{\tickYes} & \textbf{\tickYes} \\
+       & \textipa{g1nd} & \textipa{t1mx} & \textipa{g@n1m}   &  \\
+       & `log (noun)'   & `scoop with finger!' & `take back loaned cow!' &  \\ \hline
+Liquid & \textbf{\tickNo}     & \textbf{\tickNo} & \textbf{OPTIONAL}      & \textbf{\tickYes} \\
+       & \textipa{f1rt} & \textipa{t1rx} & \textipa{k1r(1)m} & \textipa{s1B1r} \\
+       & `divide in half!' & `make incision!' & `insult!'    & `break!' \\  \hline
+\end{tabular}	
+\noindent (Data assembled from \citet[404--7]{rose.2000})
+
 \section{Issues} \label{issues}

### 2013-07-22 paper.tex
Added start of 3C section

@@
 Chaha has a bilabial approximant represented by [\textipa{B}] (more precisely, \textipa{\|`B}) \citep[15]{banksira.2000} that is not as sonorous as /r/, whose realisation is tap-like \citep[181]{taranto.2001}.
-The justification for /\textipa{B}/ being less sonorous than /r/ is largely empirical, based on the epenthetic behaviour of clusters containing this sonorant \citep{405}{rose.2000}, data for which will be presented later in this paper.
+The justification for /\textipa{B}/ being less sonorous than /r/ is largely empirical, based on the epenthetic behaviour of clusters containing this sonorant \citep[405]{rose.2000}, data for which will be presented later in this paper.
 I will specify its sonority as an intermediate 3.5, under the sonority of 4 for liquids in general.
@@
 \end{center}
-\subsection{CC clusters}
+
+\subsection{Data: CC clusters}
 
@@
 
+\bigskip
+
+  The variability therefore lies in (1) whether epenthesis between obstruents is possible (between stops, between a stop and a fricative, and between two fricatives), and (2) whether [r]-sonorant can be broken up by epenthesis or not.
+  The variable setting of these two options corresponds to four attested idiolects:
+
+  \ex. \label{idiolects} The four idiolects:
+       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
+           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
+       \b. \label{idiolectb} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
+           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
+       \c. \label{idiolectc} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
+           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
+       \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
+           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
+
+The evidence of the epenthetic behaviour of coda clusters accords with the {\sc Sonority Angle} prediction that RN should be the most likely to epenthesise out of the falling sonority clusters.
+
+\subsection{Data: CCC clusters}
+
+Triconsonantal clusters are always broken up as [CC\textipa{1}C] or [C\textipa{1}CC]. The sources
+of CCC clusters in Chaha are the 3rd singular masculine conjugation of the jussive form of
+triliteral verbs, which have the underlying form /j\textipa{@}-\underline{CCC}-o/, and
+the 3rd singular masculine conjugation of the passive/reflexive form of quadriliteral verbs,
+which have the underlying form /j-\underline{t-CC}aCaC/.
+
+As with coda clusters, there is considerable variability in epenthetic positioning between idiolects.
+In what follows, I assume that the primary forms presented in Section 4.3 of \citet{rose.2000} are preferred forms, and the secondary variants presented in Section 5 are less preferred.
+
 \section{Issues} \label{issues}

### 2013-07-24 paper.tex
Started on 3C section

@@
 
+The patterns of epenthesis are as follows.
+
+\bigskip
+
+If C\textsubscript{2}-C\textsubscript{3} rises by two or more sonority steps,
+the only possible output is [CC\textipa{1}C].
+
+\ex. \a. \textipa{j@gd1ro}, *\textipa{j@g1dro} `let them put to bed'
+%TODO : convert the rest to actual words
+%TODO : check why I claim this has no variation even though it's underlined
+
+If C\textsubscript{2}-C\textsubscript{3} is of level sonority or rises by
+a single sonority step, the primary form is [CC\textipa{1}C], but [C\textipa{1}CC]
+is also possible.
+
+\ex. \a. /sgd/ $\rightarrow$ [sg\iep d] preferred, [s\iep gd] possible
+     \b. /gdf/ $\rightarrow$ [gd\iep f] preferred, [g\iep df] possible
+
+If C\textsubscript{2} is /r/ and C\textsubscript{3} is a sonorant, the primary
+form is [C\textipa{1}CC], but [CC\textipa{1}C] is also possible.
+
+\ex. \a. /krm/ $\rightarrow$ [k'\iep rm] preferred, [k'r\iep m] also possible
+
+If C\textsubscript{1} is /r/ or /n/ and the verbal form is jussive, 
+always epenthesise as [CC\textipa{1}C]. This is due to a
+morphophonological constraint on Chaha jussives.
+
+Otherwise (if C\textsubscript{2}-C\textsubscript{3} is of falling sonority and 
+C\textsubscript{2} is not /r/), [C\textipa{1}CC] is the only possible outcome.
+\ex. \a. /mrg/ $\rightarrow$ m\iep rg, *mr\iep g
+     \b. TODO
+
+There is a single exception to the previous generalisation: Rose reports that /mst/
+epenthesises as [ms\textipa{1}t]. Another native speaker reports that
+         he epenthesises this as [m\textipa{1}st] (Degif Petros Banksira, p.c.)
+
 \section{Issues} \label{issues}

### 2013-09-06 paper.tex
comment
Added Chaha coda cluster section including comparison with other approaches

--- 2013-07-22 paper.tex
@@
 \author{Michelle A. Fullwood}
-\date{July 2013}
+\date{Generals Paper, MIT \\ September 2013}
 \begin{document}
@@
 
-Given a sonority scale where classes of consonants are mapped to a numerical sonority, we can now calculate
-the {\sc Sonority Angle} for any cluster, which can be thought of as the faithfulness cost of epenthesising
-between the two consonants.  Examples of the calculation are given below.
+Given a sonority scale where classes of consonants are mapped to a numerical sonority, we can now calculate the {\sc Sonority Angle} for any cluster, which can be thought of as the faithfulness cost of epenthesising between the two consonants.
+Examples of the calculation are given below.
 
@@
 Similarly, between the clusters that fall in sonority by two steps -- RF and NT -- we expect
-NT to be less likely to undergo epenthesis, since N is less sonorous than R. We expect NT and RT
-to be the clusters most resistant to epenthesis out of all the clusters. This will be crucial 
+NT to be less likely to undergo epenthesis, since N is less sonorous than R. We expect NT and RT to be the clusters most resistant to epenthesis out of all the clusters. This will be crucial 
 to our analysis of Irish sonority-driven epenthesis.
@@
 
-\subsection{Another dimension of sonority contour faithfulness}
+\subsection{Another dimension of sonority contour faithfulness} \label{depson}
 
@@
 
-\subsection{Data: CC clusters}
+\subsection{CC clusters}
+
+\subsubsection{Data}
 
@@
 The variability therefore lies in (1) whether epenthesis between obstruents is possible (between stops, between a stop and a fricative, and between two fricatives), and (2) whether [r]-sonorant can be broken up by epenthesis or not.
+
 The variable setting of these two options corresponds to four attested idiolects:
 
-  \ex. \label{idiolects} The four idiolects:
+  \ex. \label{idiolects} The four idiolects: % TODO: ref
        \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
            [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
-       \b. \label{idiolectb} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
+       \b. \label{idiolectb} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
+           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
+       \c. \label{idiolectc} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
            [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
-       \c. \label{idiolectc} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
-           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
        \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
@@
 
-The evidence of the epenthetic behaviour of coda clusters accords with the {\sc Sonority Angle} prediction that RN should be the most likely to epenthesise out of the falling sonority clusters.
+\subsubsection{Sonority Angle Analysis}
 
-\subsection{Data: CCC clusters}
+Under a sonority contour faithfulness analysis, epenthesis is triggered by a markedness constraint on the structural conditions of the cluster, not by the markedness of the underlying sonority contour profile itself.
+Undominated {\sc *ComplexOnset} accounts for the non-existence of initial clusters.
+{\sc *Coda} is ranked low, and therefore medial clusters are left intact.{\sc *ComplexCoda}, dominated by an {\sc Ident(SonAngle)} constraint, explains why some coda clusters are broken up by epenthesis while others are not.
 
-Triconsonantal clusters are always broken up as [CC\textipa{1}C] or [C\textipa{1}CC]. The sources
-of CCC clusters in Chaha are the 3rd singular masculine conjugation of the jussive form of
-triliteral verbs, which have the underlying form /j\textipa{@}-\underline{CCC}-o/, and
+In idiolect \ref{idiolecta}, all coda clusters with a {\sc Sonority Angle} smaller than 1.5 -- the rising and level sonority clusters -- are broken up by epenthesis, while those with a {\sc Sonority Angle} greater than 1.5 -- the falling sonority clusters -- are left intact.
+
+%TODO: diagram
+
+The constraint ranking for this idiolect is thus:
+
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc *ComplexCoda}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{k1tf}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\hline \hline a. & & \textipa{k1tf} & & $\ast$! \\
+\hline b. & \ding{43} & \textipa{k1t1f} & 0.59 & \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\hline \hline c. &  \ding{43} & \textipa{k1rm} & & $\ast$ \\
+\hline d. & & \textipa{k1r1m} & 1.89 $\ast$! & \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+This approach does make one incorrect prediction: it predicts that /\textipa{Bm}/ should not undergo epenthesis under this ranking, since /\textipa{B}N/ has a {\sc Sonority Angle} of 1.65.
+But it always does:
+
+\ex. /\textipa{s@B-m}/ $\rightarrow$ \textipa{s@B1m} `people-{\sc emph}'  % TODO: ref
+
+The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect. % TODO: ref: Greenberg cited in Rose
+I suggest that there might be an undominated markedness constraint against this cluster -- either OCP(labial) or another constraint based on articulatory or perceptual difficulty -- that outranks all relevant faithfulness constraints.
+
+\bigskip
+
+Proceeding to idiolect \ref{idiolectb}, we find that [r]-sonorant clusters are allowed word-finally.
+Because {\sc Sonority Angle} permits a linear separation of the [r]-sonorant clusters from the remainder of the falling sonority clusters, this is straightforward to explain
+by the movement of the cut-off line from 1.5 to 1.9.
+
+% TODO: diagram
+
+\ex. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\hline \hline a. &   & \textipa{k1rm} & & $\ast$! \\
+\hline b. & \ding{43} & \textipa{k1r1m} & 1.89 & \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Idiolects \ref{idiolectc} and \ref{idiolectd} are identical to \ref{idiolecta} and \ref{idiolectb} respectively, except that obstruent-obstruent clusters do not undergo epenthesis under any circumstances.
+This can be achieved by ranking {\sc Dep}(+son)
+above {\sc *ComplexCoda}.
+
+\ex. Ranking for idiolect \ref{idiolectc}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{s1gd}/} & {\sc Dep}(+son) & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{s1gd} & & & \cellcolor{lightgray}$\ast$ \\
+\hline b. & & \textipa{s1g1d} & $\ast$! & 1.37 & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+To summarise, coda epenthesis behaviour in Chaha can be explained by the ranking of a {\sc Ident(SonAngle)}$<$n constraint above the markedness constraint triggering epenthesis, {\sc *ComplexCoda}.
+The evidence of the epenthetic behaviour of Chaha coda clusters accords with the {\sc Sonority Angle} prediction that RN should be the most likely to epenthesise out of the falling sonority clusters.
+It also demonstrates the action of a faithfulness constraint against introducing a sonorant region between two obstruents, {\sc Dep}(+son), as defined in $\S$\ref{depson}.
+
+\ex. Rankings for the four idiolects:
+     \a. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}(+son)
+     \b. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}(+son)
+     \c. {\sc Ident(SonAngle)}$<$1.5, {\sc Dep}(+son) $\gg$ {\sc *ComplexCoda}
+     \c. {\sc Ident(SonAngle)}$<$1.9, {\sc Dep}(+son) $\gg$ {\sc *ComplexCoda}
+
+\subsubsection{Comparison to other approaches}
+
+{\sc Sonority Rise} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other, it is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}.
+This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters.
+
+% TODO: diagram
+
+\bigskip
+
+\citet{rose.2000} offers an explanation for these facts in terms of markedness of the sonority contours of the surface clusters.
+Medial clusters are subject to Syllable Contact, which bans rising sonority clusters across a syllable boundary, while coda clusters are subject to Sonority Sequencing.
+
+The fact that medial clusters are never broken up by epenthesis even when they violate Syllable Contact is due to a constraint against the configuration [V.C\textipa{1}.CV], {\sc *MedialLight}.
+This constraint is unnecessary under my analysis as the only constraint that would militate against medial clusters, {\sc *Coda}, is not active.
+
+In addition, Sonority Sequencing does not allow a divide of the [r]-sonorant clusters versus the remainder of the clusters, whether in Rose's categorical formulation of Sonority Sequencing or a family of {\sc *Dis} constraints.
+
+% TODO: diagram
+
+Therefore, Rose needs to invoke the following constraint to cause epenthesis in these clusters:
+
+\ex. {\sc *R-Sonorant}: no [r]-sonorant sequences \citep[(41)]{rose.2000}
+
+For those speakers that permit obstruent-obstruent clusters in defiance of Sonority Sequencing, Rose ranks Sonority Sequencing low, using the following constraint to trigger epenthesis in other clusters instead:
+
+\ex. {\sc *C-Son\#}: a word-final sonorant consonant must be preceded by a vowel or [r].
+
+Rose's approach thus requires the formulation of two constraints specifically targeting [r].
+The advantage of doing so is that it avoids the difficulty of forbidding [\textipa{Bm}] clusters which we encountered above.
+On the other hand, the sonority contour faithfulness approach can get away without specifically mentioning [r] at all, by virtue of the {\sc Sonority Angle} hierarchy being able to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.
+
+\subsection{CCC clusters}
+
+\subsubsection{Data and Analysis}
+
+Triconsonantal clusters are always broken up as [CC\textipa{1}C] or [C\textipa{1}CC].
+The sources of CCC clusters in Chaha are the 3rd singular masculine conjugation of the jussive form of triliteral verbs, which have the underlying form /j\textipa{@}-\underline{CCC}-o/, and
 the 3rd singular masculine conjugation of the passive/reflexive form of quadriliteral verbs,
@@
 
-As with coda clusters, there is considerable variability in epenthetic positioning between idiolects.
-In what follows, I assume that the primary forms presented in Section 4.3 of \citet{rose.2000} are preferred forms, and the secondary variants presented in Section 5 are less preferred.
+As with coda clusters, there is considerable inter- and intra-speaker variability in epenthetic positioning between idiolects.
+The following data is from the main idiolect discussed in Section 4.3 of \citep{rose.2000}.
+Underlined forms have alternate forms in other idiolects.
+
+In
 
@@
 
+% TODO
+
 \bibliographystyle{unified}

### 2013-09-10 paper.tex
Most of the text for the 3C case

@@
 \usepackage{rotating}    %for angled text
+\usepackage{wasysym}  % for frowny face
 
@@
 formulation of the OCP, which bans successive identical oral gestures.
-A cluster such as [nt] would consist of a single oral constriction gesture at the alveolar ridge, and would not constitute a violation of the OCP.
-Splitting it by epenthesis to form [n\textipa{@}t] would require a repeated identical constriction gesture, and therefore be a violation of the OCP.
+A cluster such as [nd] would consist of a single oral constriction gesture at the alveolar ridge, and would not constitute a violation of the OCP.
+Splitting it by epenthesis to form [n\textipa{@}d] would require a repeated identical constriction gesture, and therefore be a violation of the OCP.
 
@@
 The advantage of doing so is that it avoids the difficulty of forbidding [\textipa{Bm}] clusters which we encountered above.
-On the other hand, the sonority contour faithfulness approach can get away without specifically mentioning [r] at all, by virtue of the {\sc Sonority Angle} hierarchy being able to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.
+On the other hand, the sonority contour faithfulness approach can get away without specifically mentioning [r] at all, by virtue of the ability of the {\sc Sonority Angle} hierarchy to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.
 
 \subsection{CCC clusters}
-
-\subsubsection{Data and Analysis}
 
@@
 As with coda clusters, there is considerable inter- and intra-speaker variability in epenthetic positioning between idiolects.
-The following data is from the main idiolect discussed in Section 4.3 of \citep{rose.2000}.
+We begin with data from the main idiolect discussed in Section 4.3 of \citep{rose.2000}.
+
+\subsubsection{Data and Analysis}
+
+Triconsonantal clusters must be broken up via epenthesis, indicating that {\sc *CCC} $\gg$ {\sc Dep}.
+If epenthesis occurs either between C1-C2 or between C2-C3, {\sc *CCC} will be satisfied.
+We do not need a separate constraint to prevent double epenthesis occurring to produce *[C\textipa{1}C\textipa{1}C].
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/CCC/} & *CCC & {\sc Dep} \\[0.5ex]
+\hline \hline a. & & CCC & $\ast$! &  \\
+\hline b. & \ding{43} & CC\textipa{1}C & & $\ast$ \\
+\hline c. & \ding{43} & C\textipa{1}CC & & $\ast$ \\
+\hline d. & & C\textipa{1}C\textipa{1}C & & $\ast\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+This holds for all the idiolects. Within each idiolect, we need only explain the location of epenthesis.
+
+\bigskip
+
+In the default idiolect, epenthesis occurs between C2 and C3 to form [CC\textipa{1}C].
+Only when C1-C2 constitutes a sonority rise or plateau, and C2-C3 constitutes a sonority fall, does epenthesis occur between C1 and C2 to form [C\textipa{1}CC].
+Forms and their associated sonority angles are shown in the table below.
 Underlined forms have alternate forms in other idiolects.
 
-In
+% TODO: table
+
+In this idiolect, all sonority rises and plateaus --- that is, all clusters with a {\sc Sonority Angle} less than 1.5 --- are conflated together.
+Similarly, all clusters with a {\sc Sonority Angle} greater than 1.5 are conflated together, with the default preference being to epenthesise on the right.
+
+Borrowing a constraint from \citet{rose.2000}, I use {\sc Align-Left} as the markedness constraint that prefers [CC\textipa{1}C] over [C\textipa{1}CC].
+
+\ex. Align-Left: every consonant must be aligned with the left edge of some prosodic word. % TODO: cite
+
+\vspace{-1cm}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & & \textipa{j@kifto} & 2,4!,5 \\
+\hline b. & \ding{43} & \textipa{j@kfito} & 2,3,5 \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+The ranking {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}, with all other {\sc Ident(SonAngle)}$<$n constraints being ranked lower than markedness, is responsible for the epenthetic positioning behaviour of this idiolect, as illustrated in the following tableaux.
+
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}
+     \a. Fall-\{Rise, Plateau\}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@wz1fo} & 1.33 & \cellcolor{lightgray} \\
+\hline b. & & \textipa{j@wizfo} & 2.03 $\ast$! & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. \{Rise, Plateau\}-\{Rise, Plateau\}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@gd1fo} & 1.37 & \\
+\hline b. & & \textipa{j@g1dfo} & 0.59 & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \c. Fall-Fall
+\begin{center} \renewcommand*\arraystretch{1.2}%h%
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{jams1to} & 2.11 $\ast$ & \\
+\hline b. & & \textipa{jam1sto} & 2.03 $\ast$ & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \d. \{Rise, Plateau\}-Fall
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & & \textipa{j@kfito} & 2.11 $\ast$!  & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{j@kifto} & 0.59 & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
+
+In a second idiolect discussed in Section 5.2.2 of \citep{rose.2000}, clusters behave much as in the default, except that when C2 is [r] and C3 is sonorant, epenthesis occurs on the right instead.
+
+\ex. \a. \textipa{j@k'r1mo} `let them insult'
+     \b. \textipa{j@sr1Bo} `let them break'
+
+The explanation for the special behaviour of RN clusters among triconsonantal clusters in this idiolect is similar to that of RN clusters among coda clusters: the dividing line between the conflated clusters has simply shifted to the right, at 1.9, grouping RN clusters together with sonority rises and plateaus, versus all other falls.
+This is possible using the {\sc Sonority Angle} metric because RN clusters are expected to be the most susceptible to epenthesis of all the falling sonority clusters.
+
+% TODO: scale
+
+\ex. \a. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect 1:
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & & \textipa{j@krimo} & 1.89 $\ast$! &  \\
+\hline b. & \ding{43} & \textipa{j@kirmo} & 0.12 & $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}		 
+     \b. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect 2:
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@krimo} & 1.89 & \\
+\hline b. & & \textipa{j@kirmo} & 0.12 & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+As a consequence of this, however, we would incorrectly expect a cluster like /rmd/ to epenthesise on the left:
+
+\ex. \begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \frownie & \textipa{j@rmido} & 2.36 $\ast$! & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{j@rimdo} & 1.89 & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Looking across the clusters, we find that all /r/-initial and /n/-initial triconsonantal clusters epenthesise as [CC\textipa{1}C].
+This seems to be due to a morphophonological constraint, as Rose states that ``[t]here is an independent requirement that if the initial root consonant of a triliteral root is /r/, it must appear in a coda in the jussive, realised as [n], except where there is a nasal in the root.'' (412, fn.
+20).
+In addition, all [n]-initial roots are underlyingly /r/ \citep[22]{banksira.2000}, and the only possible sources of /r/ or [n]-initial triconsonantal clusters in the language are jussive forms, so there is no independent evidence of how these clusters would epenthesise in the absence of this requirement.
+
+Adopting the following undominated constraint in Chaha, therefore, guarantees the correct form for all /r/ and [n]-initial clusters, including /rmd/ in this instance.
+
+\ex. {\sc Jussive-R}: if the first consonant of the input root is /r/, its output correspondent must be in the coda in the jussive.
+
+\ex. {\sc Jussive-R} $\gg$ {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc Align-Left}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Jussive-R} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@rmido} & & \cellcolor{lightgray}2.36 $\ast$ & \cellcolor{lightgray} \\
+\hline b. & & \textipa{j@rimdo} & $\ast$! & \cellcolor{lightgray}1.89 & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+This ranking explains all the forms in the second idiolect.
+
+\bigskip
+
+In the third idiolect, discussed in Section 5.2 of \citep{rose.2000}, most clusters epenthesise as [C\textipa{1}CC]. This includes clusters
+
+\ex. TODO
+
+In other words, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C2-C3 constitutes a sonority rise or plateau, and C1-C2 constitutes a sonority fall.
+
+This calls for a different active markedness constraint than {\sc Align-Left}. Again borrowing from Rose, I utilise the following constraint:
+
+\ex. Anchor-L-Root: An element at the left edge of the root corresponds to an element at the left edge of a heavy syllable. \citep[(45)]{rose.2000}
+
+Armed with this constraint, we can cast this behaviour as the following ranking in {\sc Sonority Angle} terms:
+
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-L-Root}
+
+% TODO: tableaux
+
+There still remain two clusters whose alternative behaviour remains unexplained according to the rankings we have obtained so far.
+
+\ex. wizf, sigd % TODO
+
+These two datapoints can be explained by retaining the constraint ranking of idiolect 3, but moving the dividing line
+
+% TODO: Tableau
+
+This behaviour is equivalent to the following {\sc Sonority Angle}-based ranking:
+
+\ex. {\sc Ident(SonAngle)}$<$1.0 $\gg$ {\sc Anchor-L-Root}
+
+% TODO: tableau
+
+% TODO: summary
+
+Complete tables illustrating the behaviour of the four idiolects are given in Appendix A. % TODO
+
+\subsubsection{Comparison with alternative approaches}
+
+The analysis of the four idiolects above was possible because the lines at which faithfulness conflation occur in Chaha correspond to linear separations of the various sets of clusters:
+
+\ex. \a. Idiolect 1: (sonority rises and plateaus) vs (sonority falls)
+     \b. Idiolect 2: (sonority rises and plateaus and RN) vs (other sonority falls)
+     \c. Idiolect 3: (sonority rises and plateaus) vs (sonority falls)
+     \d. Idiolect 4: (sonority rises) vs (sonority plateaus and falls)
+
+% TODO: diagram showing the various cut-off points.
+
+The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects 1, 3 and 4, but notice that this is not possible for idiolect 2, because % TODO
+
+\bigskip
+
+\citet{rose.2000} presents a successful analysis of the same data in Chaha, from which I have liberally borrowed.
+Under her approach, it is Syllable Contact that triggers epenthesis.
+To this end, she employs two versions of Syllable Contact that achieve the grouping effect above.
+The first permits sonority falls, while the second, looser constraint, permits both sonority falls and plateaus.
+
+\ex. \a. {\sc SyllCon}: The first segment of the onset of a syllable must be lower in sonority 
+     \b. {\sc SyllCon(Loose}): The first segment of the onset of a syllable must not be of greater sonority than the last segment of the immediately preceding syllable.
+
+Variable placcement of these two constraints with respect to {\sc Align-Left} and {\sc Anchor-Left Root}, which themselves can be variably ranked, predict three of the four idiolects.
+
+\ex. Rose's constraint rankings for idiolects 1, 3 and 4.
+    \a. Idiolect 1: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
+        \begin{itemize}
+          \item [CC\textipa{1}C] unless C1-C2 violates {\sc SyllCon}
+                (is a sonority rise or plateau) and C2-C3 would not.
+        \end{itemize}
+     \b. Idiolect 3: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} 
+        \begin{itemize}
+          \item [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon}
+                (is a sonority rise or plateau) and C1-C2 would not.
+        \end{itemize}
+     \c. Idiolect 4: {\sc SyllCon(Loose)} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} $\gg$ {\sc SyllCon}
+        \begin{itemize}
+          \item [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon(Loose)} 
+                (is a sonority rise) and C1-C2 would not.
+        \end{itemize}
+
+Thus far, the logic has been very similar to the {\sc Sonority Angle} analysis.
+Explaining the special behaviour of RN clusters in idiolect 2, requires invoking the {\sc *R-Son} constraint used in the analysis of idiolect ??
+of coda clusters.
+
+\ex. Rose's constraint ranking for idiolect 2
+     \a. {\sc *R-Son} $\gg$ {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
+% TODO: sample tableau?
+
+In addition, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C1-C2 and C2-C3 constitute violations of {\sc SyllCon}.
+% comment on need for *CCC?
+
+Overall, therefore, the {\sc Sonority Angle}-based analysis is slightly more economical than the Syllable Contact-based analysis by Rose, by not requiring any additional machinery to account for the behaviour of RN clusters in idiolect 2.
+
+\section{CCCC clusters}
+
+In this last part of our case study of Chaha, we turn to the behaviour of quadriconsonantal clusters. These epenthesise as [CC\textipa{1}CC] or [C\textipa{1}CC\textipa{1}C]. 
+I will show that the rankings already obtained for CCC clusters predict almost exactly which of the CCCC clusters should display variation and in which direction.
+
+\subsection{Predictions of CCC rankings}
+
+The undominated nature of the constraint *CCC, which we used to trigger epenthesis among the triconsonantal clusters, also triggers epenthesis in quadriconsonantal clusters.
+Notice that using this as the markedness constraint predicts exactly the two outcomes that are directly observed.
+
+Given the general form of the ranking {\sc Ident(SonAngle)}$<n$ $\gg$ {\sc Align-Left},
+the expected behaviour of four-consonant clusters is as follows.
+
+% Show that with the rankings we obtained for the various idiolects in the previous section, we predict all and only the clusters observed among 4Cs.
+
+\subsection{Data}
+
+\subsection{Analysis}
+
+\subsection{Comparison with alternative approaches}
+
+\section{Summary: Chaha}
 

### 2013-09-11 paper.tex
CCC section almost complete except for diagrams

@@
 the facts quite simply, because {\sc Sonority Angle} successfully achieves a linear separation of
-the NT and RT clusters from the remaining sonorant-initial clusters, explaining why they fail to undergo
-epenthesis. The {\sc Sonority Rise} metric does not have the same property. We have also seen that a markedness-based account would have to be much more complicated to explain the same facts.
+the NT and RT clusters from the remaining sonorant-initial clusters, explaining why they fail to undergo epenthesis.
+The {\sc Sonority Rise} metric does not have the same property.
+We have also seen that a markedness-based account would have to be much more complicated to explain the same facts.
 
@@
 
-In idiolect \ref{idiolecta}, all coda clusters with a {\sc Sonority Angle} smaller than 1.5 -- the rising and level sonority clusters -- are broken up by epenthesis, while those with a {\sc Sonority Angle} greater than 1.5 -- the falling sonority clusters -- are left intact.
-
-%TODO: diagram
+In idiolect \ref{idiolecta}, all coda clusters of rising and level sonority -- that is, those with a {\sc Sonority Angle} smaller than 1.5 -- are broken up by epenthesis, while falling sonority clusters -- those with a {\sc Sonority Angle} greater than 1.5 -- are left intact.
 
@@
 
-% TODO: diagram
-
-\ex. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda}
+%\vspace{-3em}
+%\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchydividingline1.9}}
+
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc *ComplexCoda}
 
@@
 
-\bigskip
-
-In the default idiolect, epenthesis occurs between C2 and C3 to form [CC\textipa{1}C].
+There are four idiolects to be explained:
+
+\ex. \a. ``Default idiolect'', discussed in Section 4.3 of \citep{rose.2000}. \label{defaultCCCidiolect}
+           \a. [C\textipa{1}CC] iff C1-C2 is a fall and C2-C3 is a rise or plateau.
+           \b. [CC\textipa{1}C] otherwise.
+           \z.
+     \b. [CR\textipa{1}N] idiolect, discussed in Section 5.2.2 of \citep{rose.2000}. \label{CRNidiolect}
+           \a. [CC\textipa{1}C] if C2 is [r] and C3 is a sonorant.
+           \b. Otherwise as default.
+           \z.
+     \c. [C\textipa{1}CC] idiolect, discussed in Section 5.2.1 of \citep{rose.2000}. \label{C1CCidiolect}
+           \a. [CC\textipa{1}C] iff C2-C3 is a fall and C1-C2 is a rise or plateau.
+           \b. [C\textipa{1}CC] otherwise.
+           \z.
+     \d. [\textipa{w1zf}, \textipa{s1gd}] idiolect, discussed in Section 5.2.1 of \citep{rose.2000}. \label{wizfidiolect}
+          \a. In this idiolect alone, /wzf/ and /sgd/ epenthesise as [\textipa{w1zf}] and  [\textipa{s1gd}].
+
+\bigskip
+
+\noindent {\bf Default idiolect.} In the default idiolect \ref{defaultCCCidiolect}, epenthesis occurs between C2 and C3 to form [CC\textipa{1}C].
 Only when C1-C2 constitutes a sonority rise or plateau, and C2-C3 constitutes a sonority fall, does epenthesis occur between C1 and C2 to form [C\textipa{1}CC].
@@
 
-% TODO: table
-
-In this idiolect, all sonority rises and plateaus --- that is, all clusters with a {\sc Sonority Angle} less than 1.5 --- are conflated together.
-Similarly, all clusters with a {\sc Sonority Angle} greater than 1.5 are conflated together, with the default preference being to epenthesise on the right.
-
-Borrowing a constraint from \citet{rose.2000}, I use {\sc Align-Left} as the markedness constraint that prefers [CC\textipa{1}C] over [C\textipa{1}CC].
+\ex. Default idiolect
+
+\begin{tabular}{ccccc}
+	& Underlying form      & Surface form & {\sc SonAngle}(C1,C2) & {\sc SonAngle}(C2,C3) \\ \hline
+    \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
+	a. & \textipa{j@-rk't'-o} & \textipa{j@nk'1t'o} & 2.36 & 1.37 \\
+	b. & \textipa{j@-rks-o}   & \textipa{j@nk1so}   & 2.36 & 0.59 \\
+    c. & \textipa{j@-rk'm-o}  & \textipa{j@nk'1mo}  & 2.36 & 0.27 \\
+    d. & \textipa{j@-\underline{wzf}-o} & \textipa{j@wz1fo} & 2.03 & 1.33 \\
+	e. & \textipa{j@-mxr-o}   & \textipa{j@mx1ro}   & 2.03 & 0.22 \\
+    f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
+    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
+    \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
+    h. & \textipa{j@-\underline{gdf}-o} & \textipa{j@gd1fo} & 1.37 & 0.59 \\
+    i. & \textipa{j@-\underline{gdr}-o} & \textipa{j@gd1ro} & 1.37 & 0.12 \\
+    j. & \textipa{j@-\underline{kmr}-o} & \textipa{j@km1ro} & 0.27 & 0.46 \\
+    k. & \textipa{j@-\underline{sfr}-o} & \textipa{j@sf1ro} & 1.33 & 0.22 \\
+    l. & \textipa{j@-\underline{sBr}-o} & \textipa{j@sB1ro} & 0.34 & 0.73 \\ \hline
+    \multicolumn{5}{c}{Fall-Fall: [CC\textipa{1}C]} \\ \hline
+    m. & \textipa{j@-rfk-o} & \textipa{j@nf1ko} & 2.03 & 2.11 \\ 
+    n. & \textipa{j@-rmd-o} & \textipa{j@rm1do} & 1.89 & 2.36 \\ 
+    o. & \textipa{j-a-mst-o}& \textipa{jams1to} & 2.03 & 2.11 \\ \hline
+    \multicolumn{5}{c}{\{Rise,Plateau\}-Fall: [C\textipa{1}CC]} \\ \hline
+    p. & \textipa{j@-kft-o} & \textipa{j@k1fto} & 0.59 & 2.11 \\
+    q. & \textipa{j@-dmd-o} & \textipa{j@d1mdo} & 0.27 & 2.36 \\
+    r. & \textipa{j@-drs-o} & \textipa{j@d1rso} & 0.12 & 2.21 \\ 
+    s. & \textipa{j@-\underline{k'rm}-o} & \textipa{j@k'1rmo} & 0.12 & 1.89 \\ 
+    t. & \textipa{j@-\underline{srB}-o}  & \textipa{j@s1rBo}  & 0.22 & 1.57 \\
+    u. & \textipa{j@-frt-o} & \textipa{j@f1rto} & 0.22 & 2.36 \\
+    v. & \textipa{j@-sBx-o} & \textipa{j@s1Bxo} & 0.34 & 2.17 \\
+    w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
+    \multicolumn{5}{c}{Non-jussive forms} \\ \hline
+    x. & \textipa{j-t-Bt'@b@t'} & \textipa{j1t1Bt'@b@t'} & 0.18 & 2.38 \\
+    y. & \textipa{j-t-rs@n@s} & \textipa{j1t1rs@n@s} & 0.12 & 2.21 \\
+    z. & \textipa{j-t-kB@s@s} & \textipa{j1tk1B@s@s} & 1.37 & 0.12 \\
+    A. & \textipa{j-t-k't'@k'@t'} & \textipa{j1tk'1t'@k'@t'} & 1.37 & 1.37 \\
+\end{tabular}
+
+\bigskip
+
+The default preference in this idiolect is to epenthesise on the right, between C2 and C3.
+I encode this preference with a markedness constraint borrowed from \citep{rose.2000}'s analysis:
 
@@
 
+The only time that {\sc Align-Left} is overruled is when breaking up the C2-C3 cluster would be too ``expensive'' in faithfulness terms --- when the cluster consists of a sonority fall --- and breaking up the C1-C2 cluster is comparatively cheap, that is, when C1-C2 is a sonority rise or plateau.
+In {\sc Sonority Angle} terms, {\sc Align-Left} is overruled only when breaking the C2-C3 cluster would entail creating a {\sc Sonority Angle} greater than 1.5, when the alternative of breaking the C1-C2 cluster would create a {\sc Sonority Angle} smaller than 1.5.
+
 The ranking {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}, with all other {\sc Ident(SonAngle)}$<$n constraints being ranked lower than markedness, is responsible for the epenthetic positioning behaviour of this idiolect, as illustrated in the following tableaux.
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & \ding{43} & \textipa{j@gd1fo} & 1.37 & \\
-\hline b. & & \textipa{j@g1dfo} & 0.59 & $\ast$! \\
+\hline \hline c. & \ding{43} & \textipa{j@gd1fo} & 1.37 & \\
+\hline d. & & \textipa{j@g1dfo} & 0.59 & $\ast$! \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & \ding{43} & \textipa{jams1to} & 2.11 $\ast$ & \\
-\hline b. & & \textipa{jam1sto} & 2.03 $\ast$ & $\ast$! \\
+\hline \hline e. & \ding{43} & \textipa{jams1to} & 2.11 $\ast$ & \\
+\hline f. & & \textipa{jam1sto} & 2.03 $\ast$ & $\ast$! \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & & \textipa{j@kfito} & 2.11 $\ast$!  & \cellcolor{lightgray} \\
-\hline b. & \ding{43} & \textipa{j@kifto} & 0.59 & \cellcolor{lightgray}$\ast$ \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-\bigskip
-
-In a second idiolect discussed in Section 5.2.2 of \citep{rose.2000}, clusters behave much as in the default, except that when C2 is [r] and C3 is sonorant, epenthesis occurs on the right instead.
+\hline \hline g. & & \textipa{j@kfito} & 2.11 $\ast$!  & \cellcolor{lightgray} \\
+\hline h. & \ding{43} & \textipa{j@kifto} & 0.59 & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
+
+\noindent {\bf Remark on conflation.} Notice that all distinctions among the set of rising and level sonority clusters on the one hand, and the distinctions among the set of falling sonority clusters, are conflated.
+For instance, consider the cluster /mst/.
+{\sc SonAngle}(m,s), at 2.03, is smaller than {\sc SonAngle}(s,t), at 2.11, yet epenthesis occurs on the right, creating the larger {\sc Sonority Angle}.
+This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(SonAngle)}$<$1.5.
+This is possible because I have adopted the position that the {\sc Ident(SonAngle)}$<n$ constraints can be freely ranked.
+
+Adopting the converse strategy --- that {\sc Ident(SonAngle)}$<n$ constraints have a universal ranking --- would not predict [\textipa{ms1t}]. Instead we would have the following situation:
+
+\ex. Universal ranking cannot derive [\textipa{j@ms1to}]
+
+\vspace{-3em}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-mst-o}/} & {\sc Ident(SonAngle)}$<$2.1 & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a.  &\frownie & \textipa{j@ms1to} & 2.11 $\ast$! & \cellcolor{lightgray}2.11 $\ast$ & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{j@m1sto} & 2.03 & \cellcolor{lightgray}2.03 $\ast$ & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
+
+\noindent {\bf [CR\textipa{1}N] idiolect.} In a second idiolect \ref{CRNidiolect} (c.f.
+Section 5.2.2 of \citep{rose.2000}), clusters behave much as in the default, except that when C2 is [r] and C3 is sonorant, epenthesis occurs on the right instead.
 
@@
 
-\ex. \a. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect 1:
+\ex. \a. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect \ref{defaultCCCidiolect}:
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}		 
-     \b. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect 2:
+     \b. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect \ref{CRNidiolect}:
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
-In the third idiolect, discussed in Section 5.2 of \citep{rose.2000}, most clusters epenthesise as [C\textipa{1}CC]. This includes clusters
-
-\ex. TODO
-
-In other words, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C2-C3 constitutes a sonority rise or plateau, and C1-C2 constitutes a sonority fall.
+\noindent {\bf [C\textipa{1}CC] idiolect.} In the third idiolect \ref{C1CCidiolect} (c.f. Section 5.2 of of \citep{rose.2000}), most clusters epenthesise as [C\textipa{1}CC]. This includes clusters
+
+\ex. Default idiolect
+
+\begin{tabular}{ccccc}
+	& Underlying form      & Surface form & {\sc SonAngle}(C1,C2) & {\sc SonAngle}(C2,C3) \\ \hline
+    \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
+	a. & \textipa{j@-rk't'-o} & \textipa{j@nk'1t'o} & 2.36 & 1.37 \\
+	b. & \textipa{j@-rks-o}   & \textipa{j@nk1so}   & 2.36 & 0.59 \\
+    c. & \textipa{j@-rk'm-o}  & \textipa{j@nk'1mo}  & 2.36 & 0.27 \\
+    d. & \textipa{j@-\underline{wzf}-o} & \textipa{j@wz1fo} & 2.03 & 1.33 \\
+	e. & \textipa{j@-mxr-o}   & \textipa{j@mx1ro}   & 2.03 & 0.22 \\
+    f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
+    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
+    \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [C\textipa{1}CC]} \\ \hline
+    h. & \textipa{j@-\underline{gdf}-o} & \textipa{j@g1dfo} & 1.37 & 0.59 \\
+    i. & \textipa{j@-\underline{gdr}-o} & \textipa{j@g1dro} & 1.37 & 0.12 \\
+    j. & \textipa{j@-\underline{kmr}-o} & \textipa{j@k1mro} & 0.27 & 0.46 \\
+    k. & \textipa{j@-\underline{sfr}-o} & \textipa{j@s1fro} & 1.33 & 0.22 \\
+    l. & \textipa{j@-\underline{sBr}-o} & \textipa{j@s1Bro} & 0.34 & 0.73 \\ \hline
+    \multicolumn{5}{c}{Fall-Fall: [CC\textipa{1}C]} \\ \hline
+    m. & \textipa{j@-rfk-o} & \textipa{j@nf1ko} & 2.03 & 2.11 \\ 
+    n. & \textipa{j@-rmd-o} & \textipa{j@rm1do} & 1.89 & 2.36 \\ 
+    o. & \textipa{j-a-mst-o}& \textipa{jams1to} & 2.03 & 2.11 \\ \hline
+    \multicolumn{5}{c}{\{Rise,Plateau\}-Fall: [C\textipa{1}CC]} \\ \hline
+    p. & \textipa{j@-kft-o} & \textipa{j@k1fto} & 0.59 & 2.11 \\
+    q. & \textipa{j@-dmd-o} & \textipa{j@d1mdo} & 0.27 & 2.36 \\
+    r. & \textipa{j@-drs-o} & \textipa{j@d1rso} & 0.12 & 2.21 \\ 
+    s. & \textipa{j@-\underline{k'rm}-o} & \textipa{j@k'1rmo} & 0.12 & 1.89 \\ 
+    t. & \textipa{j@-\underline{srB}-o}  & \textipa{j@s1rBo}  & 0.22 & 1.57 \\
+    u. & \textipa{j@-frt-o} & \textipa{j@f1rto} & 0.22 & 2.36 \\
+    v. & \textipa{j@-sBx-o} & \textipa{j@s1Bxo} & 0.34 & 2.17 \\
+    w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
+\end{tabular}
+
+\bigskip
+
+In this idiolect, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C2-C3 constitutes a sonority rise or plateau, and C1-C2 constitutes a sonority fall.
 
@@
 
-\ex. Anchor-L-Root: An element at the left edge of the root corresponds to an element at the left edge of a heavy syllable. \citep[(45)]{rose.2000}
+\ex. Anchor-Left Root: An element at the left edge of the root corresponds to an element at the left edge of a heavy syllable. \citep[(45)]{rose.2000}
 
@@
 
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-L-Root}
-
-% TODO: tableaux
-
-There still remain two clusters whose alternative behaviour remains unexplained according to the rankings we have obtained so far.
-
-\ex. wizf, sigd % TODO
-
-These two datapoints can be explained by retaining the constraint ranking of idiolect 3, but moving the dividing line
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-Left Root} \label{CCiCidiolectranking}
+     \a. Fall-\{Rise, Plateau\}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@wz1fo} & 1.33 & \cellcolor{lightgray}$\ast$ \\
+\hline b. & & \textipa{j@wizfo} & 2.03 $\ast$! & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. \{Rise, Plateau\}-\{Rise, Plateau\}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\hline \hline c. & & \textipa{j@gd1fo} & 1.37 & $\ast$! \\
+\hline d. & \ding{43}  & \textipa{j@g1dfo} & 0.59 &  \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \c. Fall-Fall
+\begin{center} \renewcommand*\arraystretch{1.2}%h%
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\hline \hline e. & & \textipa{jams1to} & 2.11 $\ast$! & \\
+\hline f. & \ding{43} & \textipa{jam1sto} & 2.03 $\ast$ & $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \d. \{Rise, Plateau\}-Fall
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\hline \hline g. & & \textipa{j@kf1to} & 2.11 $\ast$!  & \cellcolor{lightgray}$\ast$ \\
+\hline h. & \ding{43} & \textipa{j@k1fto} & 0.59 & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
+
+This ranking predicts that fall-fall clusters should epenthesise on the left.
+Items (m) and (n) are accounted for as they are subject to the {\sc Jussive-R} constraint, but the /mst/ cluster in (o) is predicted to surface as [m\textipa{1}st], whereas Rose marks it as being epenthesised as [ms\textipa{1}t] without variation.
+On the other hand, one of Rose's constraint rankings produces this form.
+Moreover, Degif Petros Banksira (p.c.), a native speaker of Chaha, confirms that he produces the form [jam\textipa{1}sto].
+Therefore this prediction actually proves correct.
+
+\bigskip
+
+\noindent {\bf [\textipa{w1zf}, \textipa{s1gd} idiolect.]} There still remain two clusters whose alternative behaviour remains unexplained according to the rankings we have obtained so far.
+
+\ex. \a. /\textipa{j@-wzf-o}/ can surface as [\textipa{j@-w1zf-o}], but this is not predicted by any ranking so far, including \ref{CCiCidiolectranking}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Root} \\[0.5ex]
+\hline \hline a. & \frownie & \textipa{j@w1zfo} & 2.03 $\ast$! & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{j@wz1fo} & 1.32 & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. /\textipa{j@-sgd-o}/ can surface as [\textipa{j@-s1gd-o}], but this is not predicted by any ranking so far, including \ref{CCiCidiolectranking}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-sgd-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Root} \\[0.5ex]
+\hline \hline c. & \frownie & \textipa{j@s1gdo} & 2.11 $\ast$! & \cellcolor{lightgray} \\
+\hline d. & \ding{43} & \textipa{j@sg1do} & 1.37 & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+These two datapoints can be explained by retaining the constraint ranking of idiolect 3, but moving the dividing line to 1.0, between sonority rises on the one hand, and sonority plateaus and falls on the other.
 
@@
 \ex. {\sc Ident(SonAngle)}$<$1.0 $\gg$ {\sc Anchor-L-Root}
+     \a. \begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.0 & {\sc Anchor-L Root} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@w1zfo} & 2.03 $\ast$ & \\
+\hline b. & & \textipa{j@wz1fo} & 1.32 $\ast$ & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. \begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-sgd-o}/} & {\sc Ident(SonAngle)}$<$1.0 & {\sc Anchor-L Root} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{j@s1gdo} & 2.11 $\ast$ & \\
+\hline b. & & \textipa{j@sg1do} & 1.37 $\ast$ & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
 
@@
 
-\ex. \a. Idiolect 1: (sonority rises and plateaus) vs (sonority falls)
-     \b. Idiolect 2: (sonority rises and plateaus and RN) vs (other sonority falls)
-     \c. Idiolect 3: (sonority rises and plateaus) vs (sonority falls)
-     \d. Idiolect 4: (sonority rises) vs (sonority plateaus and falls)
-
-% TODO: diagram showing the various cut-off points.
-
-The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects 1, 3 and 4, but notice that this is not possible for idiolect 2, because % TODO
+\ex. \a. Idiolect \ref{defaultCCCidiolect} (sonority rises and plateaus) vs (sonority falls)
+     \b. Idiolect \ref{CRNidiolect}: (sonority rises and plateaus and RN) vs (other sonority falls)
+     \c. Idiolect \ref{C1CCidiolect}: (sonority rises and plateaus) vs (sonority falls)
+     \d. Idiolect \ref{wizfidiolect}: (sonority rises) vs (sonority plateaus and falls)
+
+% TODO: SonAngle diagram showing the various cut-off points.
+
+The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects 1, 3 and 4, but notice that this is not possible for idiolect \ref{CRNidiolect}, because {\sc Sonority Rise} cannot achieve a linear separation of the sonority rises, plateaus and RN from the remainder of the falling sonority clusters.
+
+% TODO: SonRise diagram
 
@@
 
-Variable placcement of these two constraints with respect to {\sc Align-Left} and {\sc Anchor-Left Root}, which themselves can be variably ranked, predict three of the four idiolects.
-
-\ex. Rose's constraint rankings for idiolects 1, 3 and 4.
-    \a. Idiolect 1: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
-        \begin{itemize}
-          \item [CC\textipa{1}C] unless C1-C2 violates {\sc SyllCon}
+Variable placement of these two constraints with respect to {\sc Align-Left} and {\sc Anchor-Left Root}, which themselves can be variably ranked, predict three of the four idiolects.
+
+\ex. Rose's constraint rankings for idiolects \ref{defaultCCCidiolect}, \ref{C1CCidiolect} and \ref{wizfidiolect}.
+    \a. Idiolect \ref{defaultCCCidiolect}: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
+          \a. [CC\textipa{1}C] unless C1-C2 violates {\sc SyllCon}
                (is a sonority rise or plateau) and C2-C3 would not.
-        \end{itemize}
-     \b. Idiolect 3: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} 
-        \begin{itemize}
-          \item [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon}
+          \z.
+     \b. Idiolect \ref{C1CCidiolect}: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} 
+          \a. \item [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon}
                 (is a sonority rise or plateau) and C1-C2 would not.
-        \end{itemize}
-     \c. Idiolect 4: {\sc SyllCon(Loose)} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} $\gg$ {\sc SyllCon}
-        \begin{itemize}
-          \item [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon(Loose)} 
+          \z.
+     \c. Idiolect \ref{wizfidiolect}: {\sc SyllCon(Loose)} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} $\gg$ {\sc SyllCon}
+          \a. [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon(Loose)} 
                 (is a sonority rise) and C1-C2 would not.
-        \end{itemize}
+          \z.
 
 Thus far, the logic has been very similar to the {\sc Sonority Angle} analysis.
-Explaining the special behaviour of RN clusters in idiolect 2, requires invoking the {\sc *R-Son} constraint used in the analysis of idiolect ??
-of coda clusters.
-
-\ex. Rose's constraint ranking for idiolect 2
+Explaining the special behaviour of RN clusters in the [CR\textipa{1}N] idiolect \ref{CRNidiolect}, requires invoking the {\sc *R-Son} constraint used in the analysis of idiolects \ref{idiolectb} and \ref{idiolectd} of the coda clusters.
+
+\ex. Rose's constraint ranking for the [CR\textipa{1}N] idiolect \ref{CRNidiolect}
      \a. {\sc *R-Son} $\gg$ {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
-% TODO: sample tableau?
-
-In addition, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C1-C2 and C2-C3 constitute violations of {\sc SyllCon}.
+
+In addition to these, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must again be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C1-C2 and C2-C3 constitute violations of {\sc SyllCon}.
+
 % comment on need for *CCC?
-
-Overall, therefore, the {\sc Sonority Angle}-based analysis is slightly more economical than the Syllable Contact-based analysis by Rose, by not requiring any additional machinery to account for the behaviour of RN clusters in idiolect 2.
 

### 2013-09-11 paper.tex
Intro to 4C

@@
 
-As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<n$, defined similarly to {\sc Ident(SonAngle)}$<n$.
+As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<n$, defined similarly to {\sc Ident(SonAngle)}$<$n.
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & & \textipa{j@kifto} & 2,4!,5 \\
-\hline b. & \ding{43} & \textipa{j@kfito} & 2,3,5 \\
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-\textnormal{CCC}-o}/} & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & & \textipa{j@\textnormal{C}i\textnormal{CC}o} & 2,4!,5 \\
+\hline b. & \ding{43} & \textipa{j@\textnormal{CC}i\textnormal{C}o} & 2,3,5 \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(SonAngle)}$<$1.5.
-This is possible because I have adopted the position that the {\sc Ident(SonAngle)}$<n$ constraints can be freely ranked.
-
-Adopting the converse strategy --- that {\sc Ident(SonAngle)}$<n$ constraints have a universal ranking --- would not predict [\textipa{ms1t}]. Instead we would have the following situation:
+This is possible because I have adopted the position that the {\sc Ident(SonAngle)}$<$n constraints can be freely ranked.
+
+Adopting the converse strategy --- that {\sc Ident(SonAngle)}$<$n constraints have a universal ranking --- would not predict [\textipa{ms1t}]. Instead we would have the following situation:
 
@@
 
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{j@}-CCC-\textipa{o}/} & {\sc Anchor-Left Rt} \\[0.5ex]
+\hline \hline a. & & \textipa{j@.\textnormal{C}1\textnormal{C}.\textnormal{C}o} &  \\
+\hline b. & \ding{43} & \textipa{j@\textnormal{C}.\textnormal{C}1.\textnormal{C}o} & $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
 Armed with this constraint, we can cast this behaviour as the following ranking in {\sc Sonority Angle} terms:
@@
 
-% TODO: Tableau
-
 This behaviour is equivalent to the following {\sc Sonority Angle}-based ranking:
@@
 
-% TODO: tableau
-
-% TODO: summary
-
-Complete tables illustrating the behaviour of the four idiolects are given in Appendix A. % TODO
+In summary, we were able to explain all four CCC idiolects of Chaha by ranking different {\sc Ident(SonAngle)}$<$n constraints higher than either {\sc Align-Left} or {\sc Anchor-Left Root}.
 
@@
 
-In this last part of our case study of Chaha, we turn to the behaviour of quadriconsonantal clusters. These epenthesise as [CC\textipa{1}CC] or [C\textipa{1}CC\textipa{1}C]. 
-I will show that the rankings already obtained for CCC clusters predict almost exactly which of the CCCC clusters should display variation and in which direction.
+In this last part of our case study of Chaha, we turn to the behaviour of quadriconsonantal clusters.
+The only such clusters come from the imperative/jussive CCC stem followed by the consonant-initial suffix -\textipa{n@}.
+The underlying form is /\textipa{n-CCC-n@}/.
+They surface either as [\textipa{n1\underline{\textnormal{CC}1\textnormal{C}n}@}] or [\textipa{n1\underline{\textnormal{C}1\textnormal{CC}1n}@}].
+
+In this section, I will demonstrate that the rankings already obtained for CCC clusters predict almost exactly which of the CCCC clusters should display variation and in which direction.
 
@@
 The undominated nature of the constraint *CCC, which we used to trigger epenthesis among the triconsonantal clusters, also triggers epenthesis in quadriconsonantal clusters.
-Notice that using this as the markedness constraint predicts exactly the two outcomes that are directly observed.
-
-Given the general form of the ranking {\sc Ident(SonAngle)}$<n$ $\gg$ {\sc Align-Left},
-the expected behaviour of four-consonant clusters is as follows.
+This excludes possible solutions such as *[C\textipa{1}CCC] and *[CCC\textipa{1}C], as these still incur a violation of *CCC.
+
+Solutions such as [C\textipa{1}C\textipa{1}CC] and [CC\textipa{1}C\textipa{1}C] are also excluded, as these incur unnecessary violations of {\sc Ident(SonAngle)} and {\sc Dep}.
+If the middle two consonants C2 and C3 are split up by an epenthetic vowel, there is no further need for epenthesis as *CCC is already satisfied by [CC\textipa{1}CC].
+
+Therefore, the only two possible solutions under my approach are [CC\textipa{1}CC] and [C\textipa{1}CC\textipa{1}C].
+Which one is chosen depends on the sonority profile of the clusters, and which of {\sc Align-Left} and {\sc Anchor-Left Root} is dominant.
+
+\ex. {\sc Align-Left} favours [CC\textipa{1}CC], but {\sc Anchor-Left Rt} favours [C\textipa{1}CC\textipa{1}C].
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & Align-Left & Anchor-Left Root \\[0.5ex]
+\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$ \\
+\hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+There are some clusters whose epenthetic behaviour is subject to other considerations.
+The constraint {\sc Jussive-R} still applies to these forms, for example, which ensures that the following forms epenthesise as [CC\textipa{1}CC]:
+
+\ex. \a. \textipa{n1-\underline{nk'1m-n}@}
+     \b. \textipa{n1-\underline{nf1k-n}@}
+     \c. \textipa{n1-\underline{rm1d-n}@}
+     \z. \citep[(33a,34a,34b)]{rose.2000}
+
+In addition, Chaha prohibits intramorphemic geminates, which enforces the following forms:
+
+\ex. \a. \textipa{n1-\underline{k'f1fn}@}
+     \b. \textipa{n1-\underline{sd1dn}@}
+     \z. \citep[(37a,b)]{rose.2000}
+
+I will not consider such clusters further.
+
+\bigskip
+
+Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C2,C3) exceeds n and {\sc SonAngle}(C1,C2) and {\sc SonAngle}(C3,C4) are both smaller than n.
+Illustrative tableaux are shown below for n=1.5:
+
+\ex. TODO tableaux
+
+Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C].
+This preference is overridden when at least one of {\sc SonAngle}(C1,C2) and {\sc SonAngle}(C3,C4) are greater than n and {\sc SonAngle}(C2,C3) is less than n.
+
+\ex. TODO tableaux
 
@@
 
-\subsection{Data}
-
-\subsection{Analysis}
+The following table shows the actual surface forms observed for each of the underlying clusters, as well as the predictions of the four idiolectal rankings.
 

### 2013-09-13 paper.tex
More or less finished Chaha, added stringency info and Bangla analysis to mechanisms section

@@
 \usepackage{rotating}  %for angled text
-\usepackage{wasysym}  % for frowny face
+\usepackage{wasysym}   %for frowny face
 
@@
 This faithfulness-based approach raises the question of how the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] should be computed in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
+
 Fleischhacker's analysis rested on empirical determinations of sonority contour faithfulness, and did not attempt to determine such a relation.
-
 \citet{steriade.2006} proposed that input and output sonority contours should match in terms of whether they are rising or falling, and to what degree, but did not suggest a concrete mathematical relation.
@@
 
-In this paper, I suggest an alternative metric, {\sc Sonority Angle}, namely the magnitude of the angle made by the vectors C\textsubscript{1}-C\textsubscript{2} and C\textsubscript{1}-V, and explore the ramifications of this choice.
-
-{\sc Sonority Angle} makes the same broad predictions as {\sc Sonority Rise} -- that clusters of rising sonority, having a relatively small angle between the underlying sonority contour /C\textsubscript{1}-C\textsubscript{2}/ and the overt sonority contour [C\textsubscript{1}-V], are perceptually more similar to their epenthetic output, and therefore more likely to undergo epenthesis, than clusters of falling sonority.
+In this paper, I suggest that any such metric should bear two properties.
+The first is that suggested by previous analyses, that the more positive the gradient of the sonority contour from C1 to C2, the smaller the faithfulness cost and hence the more likely epenthesis is to occur.
+The second is that for a given sonority distance between C1 and C2, the more sonorous C1 and C2 are, the more likely epenthesis is to occur.
+
+To make things concrete, I suggest a metric that possesses these two properties, which I term {\sc Sonority Angle}.
+This is the magnitude of the angle made by the vectors C\textsubscript{1}-C\textsubscript{2} and C\textsubscript{1}-V.
+I then explore the ramifications of this choice.
+
+{\sc Sonority Angle} makes the same broad predictions as {\sc Sonority Rise} --- that clusters of rising sonority, having a relatively small angle between the underlying sonority contour /C\textsubscript{1}-C\textsubscript{2}/ and the overt sonority contour [C\textsubscript{1}-V], are perceptually more similar to their epenthetic output, and therefore more likely to undergo epenthesis, than clusters of falling sonority.
 Crucially, however, the exact hierarchy of susceptibility of individual clusters to epenthesis is predicted to be different.
@@
 Syllable Contact forms the basis for the main existing analysis of Chaha epenthesis by \citet{rose.2000}.
-I show that the faithfulness-based analysis, powered by the metric of {\sc Sonority Angle}, is more economical.
-In the case of Irish, Syllable Contact makes incorrect predictions regarding the data.
+I show that the faithfulness-based analysis, powered by the metric of {\sc Sonority Angle}, is slightly more economical in addressing the data.
+Furthermore, in the case of Irish, Syllable Contact makes incorrect predictions regarding the data.
 
@@
 and show that the sonority contour faithfulness approach explains these facts, with {\sc Sonority Angle} as the metric for comparing sonority contours.
-I compare it to {\sc Sonority Rise} and show that the former is the more successful analysis, and that overall, the approach just outlined is more economical than the
-Syllable Contact-based approach of \citet{rose.2000}.
-
-Section \ref{issues} looks at various issues regarding {\sc Sonority Angle}, such as its robustness.
-Section \ref{conclusion} concludes.
+I compare it to {\sc Sonority Rise} and show that the former is the more successful analysis, and that overall, the approach just outlined is more economical than the  Syllable Contact-based approach of \citet{rose.2000}.
+
+Section \ref{issues} looks at various issues regarding {\sc Sonority Angle}, such as its robustness. Section \ref{conclusion} concludes.
 
@@
 The second generalisation is that the more sonorous the C\textsubscript{1}, the more likely
-epenthesis is to occur. This time, fix C\textsubscript{2} and lower the sonority of C\textsubscript{1}.
+epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at -2, but vary their distance from V: %TODO : check if it should be -2 or +2
 
@@
 					  % left diagram
-                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
-                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+                      \draw (5,1) -- (0,3) -- (5,6) ; % 
+                      \node at (1.8, 3.2) {$\theta$}; % 
                       \node[left] at  (0,3) {C$_1$}; 
@@
 					  % right diagram
-                      \draw (20,1) -- (15,1) -- (20,6) ; % falling sonority
-                      \node at (17, 1.9) {$\theta$}; % theta label for falling sonority
-                      \node[left] at (15,1) {C$_1$}; 
-                      \node[right] at (20,1) {C$_2$};
+                      \draw (20,3) -- (15,5) -- (20,6) ; % rising sonority
+                      \node at (18, 4.8) {$\theta$}; % theta label for falling sonority
+                      \node[left] at (15,5) {C$_1$}; 
+                      \node[right] at (20,3) {C$_2$};
                       \node[right] at (20,6) {V};
@@
 
-While the difference is less clear visually, the second angle is larger.
+When C1 (and, by extension, C2) is of higher sonority, as on the right, the V-C1-C2 angle is clearlysmaller.
 The first term in the formula confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.
@@
 
-These faithfulness constraints have a universal ranking, with the least stringent the highest-ranked.
-
-   \ex. ... \newline
-            $\gg$ \textsc{Ident(SonAngle)}$<$1.5 \newline
-            $\gg$ \textsc{Ident(SonAngle)}$<$1.0 \newline
-            $\gg$ \textsc{Ident(SonAngle)}$<$0.5 \newline
-            $\gg$ ...
-
+This family of faithfulness constraints forms a stringency hierarchy.
+Any cluster that would, upon epenthesis, violate \textsc{Ident(SonAngle)}$<$n would also violate {\sc Ident(SonAngle)}$<$m where m$>$n.
 The resulting hierarchy of clusters, ranked according to their resistance to epenthesis as defined
@@
 \noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressed}}
+
+The prediction is that when a markedness constraint targets a set of clusters for epenthesis, if a certain cluster undergoes epenthesis, then all clusters to the left of it on the hierarchy --- those with a smaller {\sc Sonority Angle} --- should also undergo epenthesis.
 
@@
 in sonority.
-Furthermore, out of these three clusters, theone with the most sonorous C\textsubscript{1}, RN, has the smallest {\sc Sonority Angle}.
-We thus predict that out of the falling sonority clusters,
-RN is the most likely to be broken up by epenthesis. The case study on Chaha will demonstrate that this
-is the case.
+Furthermore, out of these three clusters, the one with the most sonorous C\textsubscript{1}, RN, has the smallest {\sc Sonority Angle}.
+We thus predict that out of the falling sonority clusters, RN is the most likely to be broken up by epenthesis.
+The case study on Chaha will demonstrate that this is the case.
 
@@
 
+\subsection{Stringency and faithfulness conflation}
+
+There are two possible ways to rank the family of {\sc Ident(SonAngle)}$<$n constraints.
+One is to fix them in a universal ranking \citep{prince.smolensky.1993}, with least stringent the highest-ranked:
+
+\ex. Universal ranking: \\
+     {\sc Ident(SonAngle)}$<$2.0 $\gg$ {\sc Ident(SonAngle)}$<$1.5 $\gg$ ...
+
+It is also possible to allow them to be freely ranked \citep[and others]{de.lacy.2004}, so that a more stringent constraint may outrank a less stringent one:
+
+\ex. Possible free ranking:
+     {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Ident(SonAngle)}$<$2.0 $\gg$ ...
+
+Depending on what constraints intervene, this may result in conflation of certain areas of the hierarchy, so that any distinctions between {\sc Sonority Angles} between 1.5 and 2.0 may be conflated.
+
+\bigskip
+
+In this paper, for ease of analysis, I will assume that all {\sc Ident(SonAngle)}$<$n constraints are ranked low by default, but that individual {\sc Ident(SonAngle)}$<$n constraints can be promoted to dominate a markedness constraint $\mathcal{M}$ against clusters or another faithfulness constraint $\mathcal{F}$, blocking epenthesis for all clusters with a {\sc Sonority Angle} greater than $n$, with the result that either the cluster remains intact, or a competing solution to epenthesis emerges.
+
+An example of {\sc Ident(SonAngle)}$<$n blocking epenthesis is given in the sample tableaux below.
+
+\ex. Ident(SonAngle)$<$1.5 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}
+     \a. Allows epenthesis in rising and level clusters such as stop-fricative TF:
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} & {\sc Dep} \\[0.5ex]
+\hline \hline a. & & TF & & $\ast$! & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & T\textipa{@}F & 0.59 & & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. Prevents epenthesis in falling clusters such as FT:
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} & {\sc Dep} \\[0.5ex]
+\hline \hline c. & \ding{43} & FT & &\cellcolor{lightgray} $\ast$ & \cellcolor{lightgray} \\
+\hline d. & & F\textipa{@}T & 2.11 $\ast$! &\cellcolor{lightgray} & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+We will see more examples of this in the analysis of Irish epenthesis as well as Chaha coda cluster epenthesis.
+
+\bigskip
+
+I will illustrate the use of {\sc Ident(SonAngle)}$<$n to block epenthesis in favour of other cluster resolution strategies with an example from the loanword phonology of the Dhaka dialect of Bangla, discussed and analysed in \citep{karim.2011}.
+Standard Bangla keeps coda clusters in words borrowed from English, but these are simplified in the Dhaka dialect in a variety of ways, including both epenthesis and deletion of one of the consonants in the cluster.
+
+\ex. \a. RN clusters are broken up via copy epenthesis \label{banglaRN}
+         \a. \textipa{hOrn} $\rightarrow$ \textipa{hOrOn} `horn'
+         \b. \textipa{p\textsuperscript{h}Orm} $\rightarrow$ \textipa{p\textsuperscript{h}OrOm} `form'
+         \c. \textipa{fIlm} $\rightarrow$ \textipa{fIlIm} `film'
+         \z.
+     \b. RT clusters resolved by deletion of [r] \label{banglaRT}
+         \a. \textipa{park} $\rightarrow$ \textipa{pak} `park'
+         \b. \textipa{\textrtailt Orc} $\rightarrow$ \textipa{\textrtailt Oc} `torch'
+         \c. \textipa{narb\textsuperscript{h}} $\rightarrow$ \textipa{nab\textsuperscript{h}} `nerve'
+         \z.
+     \citep[(4,5)]{karim.2011}
+
+From the examples in \ref{banglaRN}, we see that {\sc Max}(r) $\gg$ {\sc Dep} in general, making epenthesis the preferred way of dealing with the cluster.
+
+\ex. {\sc *ComplexCoda} $\gg$ {\sc Max}(r) $\gg$ {\sc Dep}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{hOrn}/} & {\sc *ComplexCoda} & {\sc Max}(r) & {\sc Dep} \\[0.5ex]
+\hline \hline a. & & \textipa{hOrn} & $\ast$! & & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{hOrOn} & & & \cellcolor{lightgray}$\ast$ \\
+\hline c. & & \textipa{hOn} & & $\ast$! & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+However, if we retain this ranking, we incorrectly expect RT clusters to be broken up by epenthesis rather than delete the [r].
+This can be resolved by ranking {\sc Ident(SonAngle)}$<$2.3, say, above {\sc Max}(r).
+This then blocks epenthesis in RT clusters, which have a {\sc Sonority Angle} of 2.35:
+
+\ex. {\sc *ComplexCoda}, {\sc Ident(SonAngle)}$<$2.3  $\gg$ {\sc Max}(r) $\gg$ {\sc Dep}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{park}/} & {\sc *ComplexCoda} & {\sc Ident(SonAngle)}$<$2.3 & {\sc Max}(r) & {\sc Dep} \\[0.5ex]
+\hline \hline a. & & \textipa{park} & $\ast$! & & \cellcolor{lightgray} & \cellcolor{lightgray} \\
+\hline b. & & \textipa{parak} & & $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray}$\ast$ \\
+\hline c. & \ding{43} & \textipa{pak} & & & \cellcolor{lightgray}$\ast$ & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Since RN clusters have a smaller {\sc Sonority Angle} of 1.9, their behaviour does not change with this ranking.
+
+While other analyses could possibly account for this data (see one such in \citep{karim.2011}), we see that simply ranking {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{F}$ allows us to account for it quite straightforwardly.
+
+\bigskip
+
+Thus far, we have not made any particular use of free ranking.
+While ranking {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{M}$ does conflate all clusters with a {\sc Sonority Angle} above $n$, as well as all clusters with a {\sc Sonority Angle} below $n$, preserving only the distinction between {\sc Sonority Angles} greater and less than $n$, this could be accomplished using a universal ranking of the {\sc Ident(SonAngle)}$<$n constraints as well, as illustrated in the following example:
+
+\ex. The {\sc Ident(SonAngle)}$<$n with the smallest $n$ that outranks {\sc *ComplexCoda} determines the cut-off point.
+
+\vspace{-3em}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Id(SA)}$<$2.0 & {\sc Id(SA)}$<$1.5 & {\sc *CompCoda} & {\sc Id(SA)}$<$1.0 & {\sc Id(SA)}$<$0.5 \\[0.5ex]
+\hline \hline a. & & TF & & & $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & T\textipa{@}F & 0.59 & 0.59 & & \cellcolor{lightgray}0.59 & \cellcolor{lightgray}0.59 $\ast$ \\
+\hline \end{tabular}} %\renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
+%\begin{center} \renewcommand*\arraystretch{1.2}
+%\scalebox{1}[1]
+{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Id(SA)}$<$2.5 & {\sc Id(SA)}$<$1.5 & {\sc *CompCoda} & {\sc Id(SA)}$<$1.0 & {\sc Id(SA)}$<$0.5 \\[0.5ex]
+\hline \hline c. & \ding{43}& FT & & & \cellcolor{lightgray} $\ast$ & \cellcolor{lightgray} & \cellcolor{lightgray} \\
+\hline d. &  & F\textipa{@}T & 2.11 & 2.11 $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} 2.11 $\ast$ & \cellcolor{lightgray}2.11 $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Where free ranking comes into play is when two output candidates break up different clusters.
+We will see examples of this in the analysis of Chaha three- and four-consonant clusters.
+I will give a schematic example here to illustrate the phenomenon.
+
+Suppose a triconsonantal cluster /CCC/ has to be broken up either as [C\textipa{@}CC] or [CC\textipa{@}C], and further that [C\textipa{@}CC] violates some additional markedness constraint $\mathcal{M}$.
+Which {\sc Ident(SonAngle)}$<$n constraint outranks $\mathcal{M}$ will then determine the positioning of the epenthetic vowel.
+
+\ex. {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{M}$
+     \a. Scenario 1: {\sc SonAngle}(C1-C2), {\sc SonAngle}(C2,C3)$<$n \\
+         Since neither violates {\sc Ident(SonAngle)}$<$n, $\mathcal{M}$ determines output.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n & $\mathcal{M}$ \\[0.5ex]
+\hline \hline a. & \ding{43} & C1C2\textipa{@}C3 & $<$n & \\
+\hline b. & & C1\textipa{@}C2C3 & $<$n & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+      \b. Scenario 2: {\sc SonAngle}(C1-C2)$>$n, {\sc SonAngle}(C2,C3)$<$n \\
+          C1\textipa{@}C2C3 harmonically bound by C1C2\textipa{@}C3 candidate.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline c. & \ding{43} &  C1C2\textipa{@}C3  & $<$n & \cellcolor{lightgray} \\
+\hline d. & & C1\textipa{@}C2C3 & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \c. Scenario 3: {\sc SonAngle}(C1-C2)$<$n, {\sc SonAngle}(C2,C3)$>$n \\
+         {\sc Ident(SonAngle)}$<$n determines output, overruling $\mathcal{M}$.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline e. & &  C1C2\textipa{@}C3 & $>$n $\ast$!  & \cellcolor{lightgray} \\
+\hline f. & \ding{43} & C1\textipa{@}C2C3& $>$n & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \d. Scenario 4: {\sc SonAngle}(C1-C2), {\sc SonAngle}(C2-C3) $>$ n \\
+         Since both candidates violate {\sc Ident(SonAngle)}$<$n, $\mathcal{M}$ determines output.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline g. & &  C1C2\textipa{@}C3 & $>$n $\ast$  & \\
+\hline h. & \ding{43} & C1\textipa{@}C2C3 & $>$n $\ast$ & $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Because we have assumed that all other {\sc Ident(SonAngle)}$<$n constraints rank low, certainly below $\mathcal{M}$, the degree to which candidates (g) and (h) violate {\sc Ident(SonAngle)}$<$n is irrelevant --- the distinction between clusters with {\sc Sonority Angles} above $n$ has been conflated.
+Even if {\sc Sonority Angle}(C2,C3) exceeds {\sc Sonority Angle}(C1,C2), the outcome is determined by the markedness constraint $\mathcal{M}$.
+
+Contrast this with the universal ranking, under which this distinction would be relevant. Numbers are given for clarity.
+
+\ex. Scenario: {\sc SonAngle}(C2-C3) $>$ {\sc SonAngle}(C1-C2) $>$ n \\
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Ident(SonAngle)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline a. & \ding{43} &  C1C2\textipa{@}C3 & 2.0 $\ast$!  & 2.0 $\ast$ &  \\
+\hline b.  & & C1\textipa{@}C2C3 & 1.7  & 1.7 $\ast$ & $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Under a universal ranking of {\sc Ident(SonAngle)}$<$n constraints, [C1C2\textipa{@}C3] would win in this scenario.
+In an equivalent scenario under free-ranking, where {\sc Ident(SonAngle)}$<$1.5 is the least stringent constraint to outrank $\mathcal{M}$, which in turn outranks all more stringent {\sc Ident(SonAngle)}$<$n constraints, the [C1C2\textipa{@}C3] candidate would win instead.
+There would be conflation of all clusters with {\sc Sonority Angles} below $n$, but distinctions between clusters with {\sc Sonority Angles} would still be relevant.
+
+The example of Chaha will show that free-ranking is necessary, as conflation is observed on both sides of $n$, where {\sc Ident(SonAngle)}$<$n is the most stringent constraint to outrank $\mathcal{M}$.
+
 \subsection{Sonority Rise}
 
-I will contrast {\sc Sonority Angle} with an alternative metric of sonority contour faithfulness proposed by \citet{flemming.2008}, {\sc Sonority Rise}, which takes the ratio of the underlying sonority contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V].
+I now turn to an alternative metric of sonority contour faithfulness proposed by \citet{flemming.2008}, {\sc Sonority Rise}, which takes the ratio of the underlying sonority contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] and subtracts that from 1.
 
@@
 
-{\sc Sonority Rise} also gives rise to a hierarchy of susceptbility of clusters.
+{\sc Sonority Rise} also gives rise to a hierarchy of susceptibility of clusters.
 
@@
 
-Though in many ways similar to the {\sc Sonority Angle} hierarchy, it makes several crucially different predictions.
-For example, it does not share the prediction of {\sc Sonority Angle} that RN is the most likely of the falling sonority clusters to epenthesise -- rather, if RN undergoes epenthesis then we expect FT and NF to do the same.
-Furthermore, it predicts that if NT and RT fail to undergo epenthesis due to the high faithfulness cost of interrupting these clusters, then RF should also fail to undergo epenthesis.
+Observe that of the two desiderata for such a metric, {\sc Sonority Rise} fulfills the first but not the second.
+Consider the falling sonority clusters.
+RN, NF and FT, which all have a sonority distance of -1, have a smaller {\sc Sonority Rise} than NT and RF, with a sonority distance of -2, followed by RT with a sonority distance of -3.
+%TODO: check if these should be + or -
+
+However, of the three, RN has the largest {\sc Sonority Rise}, and therefore is expected to be more resistant to epenthesis than NF and FT.
+If RN undergoes epenthesis, therefore, we predict FT and NF to do the same.
+
+Another prediction is that if NT and RT fail to undergo epenthesis due to the high faithfulness cost of interrupting these clusters, then RF should also fail to undergo epenthesis.
 Both of these predictions are contrary to the evidence of Irish and Chaha.
@@
 
-\ex. Universal ranking cannot derive [\textipa{j@ms1to}]
+\ex. Universal ranking cannot derive [\textipa{jams1to}]
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-mst-o}/} & {\sc Ident(SonAngle)}$<$2.1 & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a.  &\frownie & \textipa{j@ms1to} & 2.11 $\ast$! & \cellcolor{lightgray}2.11 $\ast$ & \cellcolor{lightgray} \\
-\hline b. & \ding{43} & \textipa{j@m1sto} & 2.03 & \cellcolor{lightgray}2.03 $\ast$ & \cellcolor{lightgray}$\ast$ \\
+\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$2.1 & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a.  &\frownie & \textipa{jams1to} & 2.11 $\ast$! & \cellcolor{lightgray}2.11 $\ast$ & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{jam1sto} & 2.03 & \cellcolor{lightgray}2.03 $\ast$ & \cellcolor{lightgray}$\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Rose also uses the {\sc Jussive-R} constraint in her analysis of quadriconsonantal clusters.
 
@@
 
-\ex. TODO tableaux
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}
+     \a. Case 1: {\sc Sonority Angle}(C2,C3)$<$1.5
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-gdf-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{n1gd1fn@} & 0.59 & \\
+\hline b. & & \textipa{n1g1df1n@} & 1.37, 0.54 & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. Case 2: {\sc Sonority Angle}(C2,C3)$>=$1.5 but so is one of {\sc Sonority Angle}(C1,C2) or {\sc Sonority Angle}(C3,C4)
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{n1sr1Bn@} & 1.57 $\ast$ &  \\
+\hline b. & & \textipa{n1s1rB1n@} & 0.22, 1.65$\ast$ & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+      \c. Case 3: {\sc Sonority Angle}(C2,C3)$>=$1.5 and both {\sc Sonority Angle}(C1,C2) and {\sc Sonority Angle}(C3,C4)$<$1.5
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-dmd-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. &  & \textipa{n1dm1dn@} & 2.3 $\ast$!   & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{n1d1md1n@} & 0.27, 0.27 & \cellcolor{lightgray} $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
 
@@
 
-\ex. TODO tableaux
+\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-Left Rt}
+     \a. Case 1: Both {\sc Sonority Angle}(C1,C2) and {\sc Sonority Angle}(C3,C4)$<$1.5
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-gdf-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
+\hline \hline a. &  & \textipa{n1gd1fn@} & 0.59 & $\ast$!\\
+\hline b. & \ding{43} & \textipa{n1g1df1n@} & 1.37, 0.54 &  \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \b. Case 2: {\sc Sonority Angle}(C1,C2) or {\sc Sonority Angle}(C3,C4) $>=$1.5, but so is {\sc Sonority Angle}(C2,C3)
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
+\hline \hline a. &  & \textipa{n1sr1Bn@} & 1.57 $\ast$ & $\ast$! \\
+\hline b. & \ding{43} & \textipa{n1s1rB1n@} & 0.22, 1.65$\ast$ &  \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \c. Case 3: {\sc Sonority Angle}(C1,C2) or {\sc Sonority Angle}(C3,C4) $>=$1.5, and {\sc Sonority Angle}(C2,C3)$<$1.5
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{n-sdB-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{n1sd1Bn@} & 0.18 & \cellcolor{lightgray} $\ast$ \\
+\hline b. & & \textipa{n1s1dB1n@} & 2.11 $\ast$!, 1.65 $\ast$ & \cellcolor{lightgray} \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
 
@@
 
-\subsection{Comparison with alternative approaches}
+\ex. Table of CCCC clusters, observed outcomes and predictions made by the constraint rankings proposed for the four idiolects in Section ???
+
+\begin{center}
+\begin{tabular}{|l|ccc|c|cccc|} \hline
+         & \multicolumn{3}{c|}{{\sc SonAngles}} &  & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
+ Cluster & C1,C2 & C2,C3 & C3,C4 & Observed outcomes & 1 & 2 & 3 & 4 \\ \hline % TODO: name idiolects
+ a. \textipa{sdBn} & 2.11 & 0.18 & 1.66 & \textipa{sd1Bn} & \multicolumn{4}{c|}{\textipa{sd1Bn}} \\ 
+ b. \textipa{wzfn} & 2.03 & 1.33 & 0.54 & \textipa{wz1fn}, \textipa{w1zf1n} & \multicolumn{3}{c}{\textipa{wz1fn}} & \cellcolor{lightgray}  \textipa{w1zf1n} \\
+ c. \textipa{gdfn} & 1.37 & 0.59 & 0.54 & \textipa{gd1fn}, \textipa{g1df1n} & \multicolumn{2}{c}{\textipa{gd1fn}} & \cellcolor{lightgray}  \textipa{g1df1n} &  \textipa{gd1fn} \\
+ d. \textipa{mstn} & 2.03 & 2.11 & 0.27 & \textipa{m1st1n} & \multicolumn{2}{c}{*\textipa{ms1tn}} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{m1st1n}} \\
+ e. \textipa{dmdn} & 0.27 & 2.36 & 0.27 & \textipa{d1md1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{d1md1n}} \\
+ f. \textipa{drsn} & 0.12 & 2.21 & 0.54 & \textipa{d1rs1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{d1rs1n}} \\
+ g. \textipa{sBxn} & 0.34 & 2.17 & 0.54 & \textipa{s1Bx1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{s1Bx1n}} \\
+ h. \textipa{kftn} & 0.59 & 2.11 & 0.27 & \textipa{k1ft1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{k1ft1n}} \\
+ i. \textipa{ktfn} & 1.37 & 0.59 & 0.54 & \textipa{kt1fn}, \textipa{k1tf1n} & \multicolumn{2}{c}{\textipa{kt1fn}} & \cellcolor{lightgray}  \textipa{k1tf1n} &  \textipa{kt1fn} \\
+ j. \textipa{sgdn} & 2.11 & 1.37 & 0.27 & \textipa{sg1dn}, \textipa{s1gd1n} & \multicolumn{3}{c}{\textipa{sg1dn}} & \cellcolor{lightgray}  \textipa{s1gd1n} \\
+ k. \textipa{srBn} & 0.22 & 1.57 & 1.65 & \textipa{sr1Bn}, \textipa{s1rB1n} & \multicolumn{2}{c}{\textipa{sr1Bn}} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{s1rB1n}} \\
+ l.
+\textipa{krmn} & 0.12 & 1.89 & 1.25 & \textipa{kr1mn}, \textipa{k1rm1n} & \cellcolor{lightgray}  \textipa{k1rm1n} & \textipa{kr1mn} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{k1rm1n}} \\ \hline
+ \end{tabular}
+\end{center}
+
+There is only one incorrect prediction, namely that /mstn/ should surface as [\textipa{ms1tn}] in idiolects \ref{defaultCCCidiolect} and \ref{CRNidiolect}, but Rose indicates that there is no variation.
+It is possible that this is simply a form that does undergo variation but the predicted [\textipa{ms1tn}] variant has not been observed in Rose's corpus.
+
+Apart from the case of /mstn/, we see that the predictions of the rankings derived for the /CCC/ case are quite successful: clusters predicted to show variation do show variation, while for those predicted to surface only as one of [CC\textipa{1}CC] and [C\textipa{1}CC\textipa{1}C], the predicted form is indeed the only one observed.
 
 \section{Summary: Chaha}
+
+In this case study, I presented an alternative analysis of Chaha epenthetic positioning to \citet{rose.2000}'s Syllable Contact-based analysis, in which sonority profiles affected epenthesis via the mechanism of sonority-based faithfulness constraints {\sc Ident(SonAngle)}$<$n rather than sonority-based markedness constraints such as Syllable Contact and Sonority Sequencing.
+The fact that general constraints on syllable structure such as *CCC and {\sc *ComplexCoda} drove epenthesis eliminated the need for constraints forbidding too much epenthesis, as Rose does in the form of the constraint {\sc *MedialLight}.
+
+The prediction of {\sc Sonority Angle} that RN clusters should be the most susceptible of all the falling sonority clusters to epenthesis was borne out in the Chaha data, both in CC\# and CCC clusters.
+This fact made it possible for us to do without Rose's {\sc *R-Son} constraint, although at the expense of requiring a constraint against [\textipa{Bm}] clusters.
+Invoking another faithfulness constraint, {\sc Dep}(+son), in the analysis of CC\# clusters allowed us to eliminate the use of Rose's {\sc *C-Son} constraint, which also needed to make special reference to [r].
+
+% faithfulness conflation
+
+In the final tally, therefore, % TODO
 

### 2013-09-13 paper.tex
Added Chaha summary

@@
 
-\section{CCCC clusters}
+\subsection{CCCC clusters}
 
@@
 
-\subsection{Predictions of CCC rankings}
+\subsubsection{Predictions of CCC rankings}
 
@@
 
-\section{Summary: Chaha}
+\subsection{Summary: Chaha}
 
@@
 
-In the final tally, therefore, % TODO
+In the final tally, the {\sc Sonority Angle}-based approach fares worse on one datapoint and uses approximately the same number of constraints, but manages to accomplish most of the work of the analysis with the only crucial ranking being the placement of a single {\sc Ident(SonAngle)}$<$n constraint with respect to a relevant $\mathcal{M}$ constraint, while in Rose's analysis this work is spread over a number of different sonority-related constraints.
 

### 2013-09-17 paper.tex
Added quite a bit of the issues section and a conclusion

@@
 
-\subsubsection{Data and Analysis}
+\subsubsection{Data and Analysis} \label{CCCanalysis}
 
@@
 
-% Show that with the rankings we obtained for the various idiolects in the previous section, we predict all and only the clusters observed among 4Cs.
-
 The following table shows the actual surface forms observed for each of the underlying clusters, as well as the predictions of the four idiolectal rankings.
 
-\ex. Table of CCCC clusters, observed outcomes and predictions made by the constraint rankings proposed for the four idiolects in Section ???
+\ex. Table of CCCC clusters, observed outcomes and predictions made by the constraint rankings proposed for the four idiolects in $\S$\ref{CCCanalysis}.
 
@@
 
-% faithfulness conflation
+% faithfulness conflation?
 
@@
 
-\section{Issues} \label{issues}
+\section{Discussion} \label{issues}
+
+In this paper, I proposed two desiderata for a metric of sonority contour distance, and suggested {\sc Sonority Angle} as a concrete metric that fit these criteria.
+In this section, I examine the weaknesses of {\sc Sonority Angle} as a metric, as well as possible extensions.
+
+\subsection{Robustness of the metric}
+
+\noindent {\bf Changes in C1.} In the discussion of Chaha triconsonantal clusters in  $\S$\ref{CCCanalysis}, I glossed over how the metric should be computed if C1 changes.
+This was an issue in clusters such as /rfk/, which emerge as [nf\textipa{1}k] due to morphophonological processes.
+Ultimately, this was not an issue because the behaviour of all such clusters was independently determined by {\sc Jussive-R}, but this raises the question of how {\sc Sonority Angle} should be computed if C1 changes.
+Currently, it is undefined, as it is unclear how to measure the angle between C1-C2=RF and C1-V=NV:
+
+%TODO : draw diagram showing what happens with the different C1's
+\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % left diagram
+                      \draw (5,2) -- (0,4);
+                      \draw (0,3) -- (5,6) ; % rising sonority
+                      \node[left] at  (0,4) {r}; 
+                      \node[left] at  (0,3) {n}; 
+                      \node[right] at (5,2) {f};
+                      \node[right] at (5,6) {\textipa{1}};
+     \end{tikzpicture}
+
+It is of course possible to define the angle as whatever is made by the intersection of the two vectors, but there is insufficient data to support this interpretation.
+Alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C1C2/ and the surface contour [C1V] does not depend on the two C1's being the same.
+
+\bigskip
+
+\noindent {\bf Horizontal distance.} In this paper, I assumed that the horizontal distance between C1 and C2, and C1 and V, is the same, and arbitrarily fixed at 1, in calculating {\sc Sonority Angle}.
+This is an arbitrary choice, and potentially an important one, as when the horizontal distance gets large, changes occur in the cluster hierarchy:
+
+\ex. TODO: stick in what happens if horizontal distance is 100 and the sonority scale remains the same
+
+Since this horizontal distance is along the dimension of time, the assumption that the two distances is the same is also likely incorrect.
+If we choose a different horizontal distance for C1-C2 versus C1-V, the cluster hierarchy would also be likely to change.
+
+\bigskip
+
+\noindent {\bf Arbitrariness of the sonority scale.} A third issue faced by any sonority metric is the arbitrariness of the vertical, sonority scale used in this paper.
+The scale adopted, which is a relatively standard scale, is rather phonological in nature, placing each sonority class at a distance of 1 from the next, and ignoring all differences between consonants within each class.
+From a phonetic standpoint, this seems unlikely.
+Observe, for example, the values obtained by \citet{parker.2002} for ???, the metric that Parker found to be the most correlated with phonological sonority:
+
+\ex. TODO: Parker sonority scale
+
+Plugging this scale into the {\sc Sonority Angle} metric, we obtain %TODO
+
+\bigskip
+
+Ultimately, the most practical course of action may be to simply attempt to experimentally determine sonority contour distances, and perhaps then fit them to a metric.
+To date, only a few sonority contour distances have been experimentally determined, for example between rising (TR) and falling (sT) clusters \citep{fleischhacker.2002}, but not finer-grained distances such as between the various falling sonority clusters.
+I leave this to future work.
+
+\bigskip
+
+\noindent {\bf Why these vectors?} In the sonority contour faithfulness approach, the relevant comparison is between C1-C2 and C1-V.
+But why these two vectors?
+In particular, why not C1-C2 versus V-C2?
+
+\ex. Left: {\sc Sonority Angle} as currently defined; right: another possible definition as the angle C1-C2-V.
+
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % left diagram
+                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
+                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+                      \node[left] at  (0,3) {C$_1$}; 
+                      \node[right] at (5,1) {C$_2$};
+                      \node[right] at (5,6) {V};
+					  % right diagram
+                      \draw (15,3) -- (20,1) -- (15,6) ; % falling sonority
+                      \node at (17.5, 2.75) {$\theta$}; % theta label for falling sonority
+                      \node[left] at (15,3) {C$_1$}; 
+                      \node[right] at (20,1) {C$_2$};
+                      \node[right] at (13,6) {V};
+\end{tikzpicture} 
+\end{center}
+
+The answer, currently, is based purely on empirical grounds: if we assume this comparison to be the relevant one, then we expect falling sonority contours to be more susceptible to epenthesis, which contradicts the cross-linguistic evidence.
+It would seem that there is something quite fundamental about the comparison being centred around the rightward context, or release, of C1, which may perhaps arise out of phonological processing.
+
+\subsection{Extensions of the metric}
+
+So far, I have employed the {\sc Sonority Angle} metric purely in the analysis of epenthetic processes. However, there are other possible applications.
+
+\bigskip
+
+\noindent {\bf Syncope.} We can straightforwardly adapt the sonority contour faithfulness account to analyse syncope, as pointed out by \citet{flemming.2008}.
+Interestingly, this makes different predictions from an account based on Syllable Contact, unlike the case of epenthesis where sonority contour faithfulness and Syllable Contact make similar predictions.
+
+According to Syllable Contact, syncope should be blocked when it would create a marked, rising sonority, cluster.
+We expect syncope to preferentially create falling sonority clusters.
+Under a sonority contour faithfulness account, however, we expect clusters to be created when they are similar in sonority profile to the underlying C1-V contour -- that is, rising sonority clusters should be preferentially created.
+
+\citet{flemming.2008} cites two cases of sonority-sensitive syncope in English and Dutch in which rising sonority clusters are preferentially created.
+Illustrative examples from English are given below:
+
+\ex. \a. Syncope allowed when rising sonority cluster is created
+     \a. \textipa{Ev@ri} $\sim$ \textipa{Evri} `every'
+     \b. \textipa{mEm@ri} $\sim$ \textipa{mEmri} `memory'
+     \z.
+     \b. Syncope disallowed when level or falling sonority cluster would be created
+     \a. \textipa{pIk@tIN} $\sim$ \textipa{pIktIN} `picketing'
+     \b. \textipa{k@p\ae s@ti} $\sim$ \textipa{k@p\ae sti} `capacity'
+     \z.
+     \citep{hooper.1978}, cited in \citep{flemming.2008}
+
+On the other hand, syncope in Hebrew (and others?) is said to work according to the principles of Syllable Contact:
+
+\ex. TODO: Hebrew etc examples
+
+More work needs to be done to reconcile these two.
+
+\bigskip
+
+\noindent{\bf Consonant deletion.} The current formulation of {\sc Ident(SonAngle)}$<$n constraints restricts its application to when the consonants of a C1-C2 and C1-V-C2 sequence stand in correspondence.
+However, another formulation is possible, in which sonority contours are a property of C1 rather than a property of the whole contour.\footnote{Thanks to Adam Albright for this suggestion.}
+
+\ex. TODO: formulate this
+
+A possible application of this looser definition of {\sc Sonority Angle} lies in the deletion of consonants in complex onsets.
+
+% pa - pla 
+% Hawaiian loanword?
+% Sanskrit reduplication
 
@@
 
-% TODO
-
-\bibliographystyle{unified}
+In this paper, I argued for sonority contour faithfulness being the right way to analyse sonority-driven epenthesis, giving case studies in Irish and Chaha as examples.
+I additionally proposed that sonority contour distance should be computed by a metric that obeys two desiderata, % TODO
+
+Using {\sc Sonority Angle} as a concrete example of a metric that obeys these two desiderata, I showed that  a sonority contour faithfulness account based on {\sc Sonority Angle} worked better than a cluster markedness-based account of sonority-driven epenthesis in Irish.
+Firstly, the faithfulness-based analysis did not need separate constraints for heterosyllabic and coda clusters like Syllable Contact and Sonority Sequencing, which more economically accounted for the ``coincidence'' that the same clusters were allowed and disallowed in both syllabic contexts.
+Secondly, the markedness-based approach in Irish could not account for why obstruent-initial heterosyllabic and coda clusters are tolerated in Irish even though these should be more marked than sonorant-initial clusters under the two sonority-based markedness constraints.
+
+In addition, compared to the {\sc *Dis} metric \citep{gouskova.2002} for measuring sonority distance in Syllable Contact and Sonority Sequencing, and the alternative sonority contour faithfulness metric {\sc Sonority Rise} \citep{flemming.2008}, {\sc Sonority Angle} made the correct predictions that nasal-voiceless stop and liquid-voiceless stop clusters should be the hardest to epenthesise into in Irish, and the prediction that liquid-nasal clusters should be the most susceptible to epenthesis out of the falling sonority clusters in Chaha.
+
+{\sc Sonority Angle} was offered here as a concrete instance of the class of metrics that conform to the two desiderata.
+In $\S$\ref{issues}, I discussed several issues regarding the assumptions that need to be incorporated into its formulation.
+More perceptual experiments and cross-linguistic investigation of sonority-driven epenthesis needs to be done to pin down the specifics of the metric.
+In addition, I discussed two other sonority-based phenomena that may shed additional light on the true nature of sonority contour faithfulness.
+
+\bibliographystyle{apalike}
 \bibliography{sonangle}

### 2013-09-18 paper.tex
Added syncope section

@@
 
-So far, I have employed the {\sc Sonority Angle} metric purely in the analysis of epenthetic processes. However, there are other possible applications.
+So far, I have employed the {\sc Sonority Angle} metric purely in the analysis of sonority-driven epenthesis. However, there are other possible applications.
 
@@
      \z.
-     \b. Syncope disallowed when level or falling sonority cluster would be created
+     \b. Syncope disallowed when level or falling sonority cluster would have been created
      \a. \textipa{pIk@tIN} $\sim$ \textipa{pIktIN} `picketing'
@@
      \z.
-     \citep{hooper.1978}, cited in \citep{flemming.2008}
-
-On the other hand, syncope in Hebrew (and others?) is said to work according to the principles of Syllable Contact:
-
-\ex. TODO: Hebrew etc examples
-
-More work needs to be done to reconcile these two.
+     (Data from \citep{hooper.1978}, cited in \citep{flemming.2008})
+
+On the other hand, syncope in Hebrew \citep{landau.1997}, Lushootseed \citep{urbanczyk.1996} and Mantuan \citep{miglio.1998} are said to work according to the principles of Syllable Contact:
+
+\ex. \a. Syncope allowed when falling sonority cluster is created
+     \ag. \v{s}om\'er-et + ot\'o $\rightarrow$ \v{s}om\'eretot\`o (no deletion) / \v{s}om\'ertot\`o \\
+          keep-3SgFem + it \\
+     \bg. kib\'el + ot\'ax $\rightarrow$ kilb\'eltax \\
+          accept.3SgMasc + you \\
+     \z.
+     \b. Syncope disallowed when rising sonority cluster would have been created
+     \ag. hev\'e-tem + ot\'o $\rightarrow$ hev\'etemot\`o (no deletion) / *hev\'etmot\`o \\
+          bring-2pl + it \\
+     \bg. xa\v{s}av + al\'av $\rightarrow$ *xa\v{s}\'avlav \\
+          think.3SgMasc + about.him \\
+     \z.
+     (Data from \citep{landau.1997})
+
+More work needs to be done to reconcile these two types of sonority-driven syncope.
 

### 2013-09-18 paper.tex
Added horizontal distance discussion

@@
 
-\noindent {\bf Horizontal distance.} In this paper, I assumed that the horizontal distance between C1 and C2, and C1 and V, is the same, and arbitrarily fixed at 1, in calculating {\sc Sonority Angle}.
-This is an arbitrary choice, and potentially an important one, as when the horizontal distance gets large, changes occur in the cluster hierarchy:
-
-\ex. TODO: stick in what happens if horizontal distance is 100 and the sonority scale remains the same
-
-Since this horizontal distance is along the dimension of time, the assumption that the two distances is the same is also likely incorrect.
-If we choose a different horizontal distance for C1-C2 versus C1-V, the cluster hierarchy would also be likely to change.
+\noindent {\bf Horizontal distance.} In this paper, I assumed that the horizontal distance between C1 and C2, and C1 and V, is the same, and arbitrarily fixed at 1 unit, in calculating {\sc Sonority Angle}.
+This is an arbitrary choice, and potentially an important one, as when the horizontal distance gets large, changes occur in the cluster hierarchy, some of which violate the first desideratum for a sonority angle metric:
+
+\ex. {\sc Sonority Angle} hierarchy for a horizontal distance of 100 units.
+
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \node (RT) at (0.04998833883*300,1.5)   {RT};
+  \node (NT) at (0.04998833883*300,1.0)  {NT};
+  \node (FT) at (0.04897835381*300,0.5)  {FT}; %0.04997835381
+  \node (TT) at (0.0479583957219*300,0)     {TT}; %0.0499583957219
+  \node (RF) at (0.0399946679463*300,1.5)     {RF};
+  \node (NF) at (0.038906715435*300,1.0)  {NF}; %0.0399906715435
+  \node (TF) at (0.0379587290353*300,0.5)   {TF}; %0.0399587290353
+  \node (FF) at (0.0379587290353*300,0)   {FF};%0.0399587290353
+  \node (RN) at (0.0299970006598*300,1.5)   {RN};
+  \node (NN) at (0.0289910048569*300,1.0)   {NN}; %0.0299910048569
+  \node (FN) at (0.0279790204366*300,0.5)  {FN}; %0.0299790204366
+  \node (TN) at (0.0269610617488*300,0)   {TN}; %0.0299610617488
+  \node (RR) at (0.0199973339732*300,1.5)  {RR}; %
+  \node (NR) at (0.0189913381702*300,1.0)  {NR}; %0.0199913381702
+  \node (FR) at (0.0179813531501*300,0.5)   {FR};%0.0199813531501
+  \node (TR) at (0.0169673908651*300,0)   {TR}; %0.0199673908651
+  % axis
+  \node (axisstart) at (0.0,-0.5) {};
+  \node (axisend)   at (0.06*300,-0.5) {};
+  \draw (axisstart) -- (axisend);
+  \node  (0point) at (0.0,0) {};
+  \node (xaxislabel) at (0.06*300,-0.8) {\textsc{SonAngle}};
+\end{tikzpicture}
+
+Notice that we cannot achieve a clean separation of the rising versus level versus falling sonority clusters, as before.
+Compare this with {\sc Sonority Rise} which, being dimensionless (since it is the ratio of two vectors in the same plane), does not have to take into account such units.
+
+Additionally, since this horizontal distance is along the dimension of time, the assumption that the two horizontal distance for C1-C2 is the same as that for C1-V is likely incorrect.
+If we choose different values for these two horizontal distances, the cluster hierarchy would also be likely to change.
+This would also be a consideration to take into account when computing {\sc Sonority Rise}.
 

### 2013-09-18 paper.tex
Cleared a TODO about direction of sonority distance

@@
 The second generalisation is that the more sonorous the C\textsubscript{1}, the more likely
-epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at -2, but vary their distance from V: %TODO : check if it should be -2 or +2
+epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at 2, but vary their distance from V:
 
@@
 In this paper, I proposed two desiderata for a metric of sonority contour distance, and suggested {\sc Sonority Angle} as a concrete metric that fit these criteria.
-In this section, I examine the weaknesses of {\sc Sonority Angle} as a metric, as well as possible extensions.
+In this section, I examine first a general question regarding sonority contour faithfulness, then discuss weaknesses of {\sc Sonority Angle} as a metric, as well as possible extensions of this metric to domains beyond sonority-driven epenthesis.
+
+\section{Disregarding V-C2}
+
+In the sonority contour faithfulness approach, the relevant comparison is between C1-C2 and C1-V. But why these two vectors? In particular, why not C1-C2 versus V-C2?
+
+\ex. Left: {\sc Sonority Angle} as currently defined; right: another possible definition as the angle C1-C2-V.
+
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % left diagram
+                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
+                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+                      \node[left] at  (0,3) {C$_1$}; 
+                      \node[right] at (5,1) {C$_2$};
+                      \node[right] at (5,6) {V};
+					  % right diagram
+                      \draw (15,3) -- (20,1) -- (15,6) ; % falling sonority
+                      \node at (17.5, 2.75) {$\theta$}; % theta label for falling sonority
+                      \node[left] at (15,3) {C$_1$}; 
+                      \node[right] at (20,1) {C$_2$};
+                      \node[right] at (13,6) {V};
+\end{tikzpicture} 
+\end{center}
+
+The answer, currently, is based purely on empirical grounds: if we assume this comparison to be the relevant one, then we expect falling sonority contours to be more susceptible to epenthesis, which contradicts the cross-linguistic evidence.
+It would seem that there is something quite fundamental about the comparison being centred around the rightward context, or release, of C1, which may perhaps arise out of phonological processing.
 
@@
 
-%TODO : draw diagram showing what happens with the different C1's
 \ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
@@
 
-\noindent {\bf Why these vectors?} In the sonority contour faithfulness approach, the relevant comparison is between C1-C2 and C1-V.
-But why these two vectors?
-In particular, why not C1-C2 versus V-C2?
-
-\ex. Left: {\sc Sonority Angle} as currently defined; right: another possible definition as the angle C1-C2-V.
-
-\begin{center}
-\begin{tikzpicture} [shorten >=1pt,scale=0.33]
-                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
-                      \node at (-3, 7.0) {Sonority}; % axis label
-					 % left diagram
-                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
-                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
-                      \node[left] at  (0,3) {C$_1$}; 
-                      \node[right] at (5,1) {C$_2$};
-                      \node[right] at (5,6) {V};
-					  % right diagram
-                      \draw (15,3) -- (20,1) -- (15,6) ; % falling sonority
-                      \node at (17.5, 2.75) {$\theta$}; % theta label for falling sonority
-                      \node[left] at (15,3) {C$_1$}; 
-                      \node[right] at (20,1) {C$_2$};
-                      \node[right] at (13,6) {V};
-\end{tikzpicture} 
-\end{center}
-
-The answer, currently, is based purely on empirical grounds: if we assume this comparison to be the relevant one, then we expect falling sonority contours to be more susceptible to epenthesis, which contradicts the cross-linguistic evidence.
-It would seem that there is something quite fundamental about the comparison being centred around the rightward context, or release, of C1, which may perhaps arise out of phonological processing.
-
 \subsection{Extensions of the metric}

### 2013-09-18 paper.tex
Added some missing citations

@@
 \ex. \textsc{Ident(SonAngle)}$<n$: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
-stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$. % TODO: change to it being a property of C1?
+stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$.
 
@@
 Consider the falling sonority clusters.
-RN, NF and FT, which all have a sonority distance of -1, have a smaller {\sc Sonority Rise} than NT and RF, with a sonority distance of -2, followed by RT with a sonority distance of -3.
-%TODO: check if these should be + or -
+RN, NF and FT, which all have a sonority distance of -1, have a smaller {\sc Sonority Rise} than NT and RF, with a sonority distance of 2, followed by RT with a sonority distance of 3.
 
@@
     \draw (axisstart) -- (axisend);
-   \node (xaxislabel) at (2.6 * 15,-2.5) {\textsc{Sonority Angle}};
+   \node (xaxislabel) at (2.4 * 15,-2.4) {\textsc{Sonority Angle}};
 
@@
 
-  \node (2pointlabel) at (2.43 * 15,-1.5) {2.3};
-
-    \end{tikzpicture} %TODO : draw arrow and mark 1.0, 1.5, 2.0, 2.5
+  \path [line] (2 * 15, -1.3) -- (2 * 15, -0.7) -- cycle;
+  \path [line] (1 * 15, -1.3) -- (1 * 15, -0.7) -- cycle;
+  \node (1mark) at (1 * 15, -1.7) {1};
+  \node (2mark) at (2 * 15, -1.7) {2};
+
+  \node (2pointlabel) at (2.43 * 15,-1.7) {2.3};
+
+    \end{tikzpicture}
 
@@
 
-    \end{tikzpicture} % TODO: draw arrow and mark 1.0, 1.5, 2.0, 2.5
+    \end{tikzpicture} 
  \end{center}
@@
 We quickly see that Syllable Contact on its own is insufficient as epenthesis in Irish also affects coda clusters. We will need to invoke Sonority Sequencing.
-
-%TODO : Syllable Contact and Sonority Sequencing should not be in smallcaps unless referred to as SyllCon and SonSeq.
 
@@
 
-  \ex. \label{idiolects} The four idiolects: % TODO: ref
+  \ex. \label{idiolects} The four idiolects: \citep[(43)]{rose.2000}
        \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
@@
 
-\ex. /\textipa{s@B-m}/ $\rightarrow$ \textipa{s@B1m} `people-{\sc emph}'  % TODO: ref
-
-The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect. % TODO: ref: Greenberg cited in Rose
+\ex. /\textipa{s@B-m}/ $\rightarrow$ \textipa{s@B1m} `people-{\sc emph}'  \citep[fn. 16]{rose.2000}
+
+The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect \citep[cited in \citep{rose.2000}]{greenberg.1950}.
 I suggest that there might be an undominated markedness constraint against this cluster -- either OCP(labial) or another constraint based on articulatory or perceptual difficulty -- that outranks all relevant faithfulness constraints.
@@
 
-\ex. Align-Left: every consonant must be aligned with the left edge of some prosodic word. % TODO: cite
+\ex. Align-Left: every consonant must be aligned with the left edge of some prosodic word. \citep[(21)]{rose.2000}
 

### 2013-09-18 paper.tex
Added NT example in Irish
Added a couple of diagrams

@@
 
+\vspace{-3em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
      \b. /korp/  $\rightarrow$ [korp], *[kor\textipa{@p}] \\
-         {\it corp} `body' %TODO : get some NT data in here!
+         {\it corp} `body' 
+     \b. /\textipa{baNk}/ $\rightarrow$ [\textipa{baNk}], *[\textipa{baN@k}] \\
+         {\it banc} `bank'
      \z.
-     \citep[(39a,b,c)]{carnie.1994}
+     \citep[(39a,b,c,26c)]{carnie.1994}
 
@@
 \ex. No onset clusters in Chaha
-     \a. \textipa{k1r@tam} `he lifted up'
+     \a. \textipa{k1r@tam} `he lifted up' \citep[398]{rose.2000}
 
@@
 
-\subsubsection{Sonority Angle Analysis}
+\subsubsection{Analysis}
 
@@
 In idiolect \ref{idiolecta}, all coda clusters of rising and level sonority -- that is, those with a {\sc Sonority Angle} smaller than 1.5 -- are broken up by epenthesis, while falling sonority clusters -- those with a {\sc Sonority Angle} greater than 1.5 -- are left intact.
+
+\ex. All clusters with a {\sc Sonority Angle} to the left of the dividing line undergo epenthesis while those to the right resist it, with one exception.
+
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
+  \tikzstyle{line} = [draw, -latex']
+
+	\node (TR) at (0.124354994547*8, 1) {TR};
+	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
+	\node (FR) at (0.218668945874*8, 1) {FR};
+	\node (TN) at (0.266252049151*8, 1.5) {TN};
+	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
+	\node (NR) at (0.463647609001*8, 1) {NR};
+	\node (FN) at (0.540419500271*8, 0.5) {FN};
+	\node (TF) at (0.588002603548*8, 1) {TF};
+	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
+	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
+	\node (RR) at (1.10714871779*8, 1) {RR};
+	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
+	\node (NN) at (1.2490457724*8, 1) {NN};
+	\node (FF) at (1.32581766367*8, 1.5) {FF};
+	\node (TT) at (1.37340076695*8, 1) {TT};
+	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
+	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
+	\node (RN) at (1.89254688119*8, 1) {RN};
+	\node (NF) at (2.0344439358*8, 1) {NF};
+%	\node (GF) at (2.0344439358*8, 1.5) {GF};
+	\node (FT) at (2.11121582707*8, 0.5) {FT};
+	\node (bF) at (2.17308367293*8, 1) {bF};
+	\node (RF) at (2.21429743559*8, 1.5) {RF};
+	\node (RT) at (2.35619449019*8, 1) {RT};
+	\node (NT) at (2.35619449019*8, 0.5) {NT};
+	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
+  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
+  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
+  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
+  % axis
+  \node (axisstart) at (-0.23,0) {};
+  \node (axisend)   at (2.7*8,0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
+  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
+  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
+  \node (0pointlabel) at (0.0,-0.5) {0};
+  \node (1pointlabel) at (1.0*8,-0.5) {1};
+  \node (2pointlabel) at (2.0*8,-0.5) {2};
+  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
+  % dividing line
+  \node (dividinglinestart) at (1.5 * 8,2) {};
+  \node (dividinglineend)   at (1.5 * 8,-0.3) {};
+  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
+  \node (dividingpointlabel) at (1.5*8, -0.5) {1.5};
+\end{tikzpicture}
+}
 
@@
 {\sc Sonority Rise} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other, it is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}.
-This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters.
-
-% TODO: diagram
+This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters: if RN undergoes epenthesis, we expect that FT and NF should also, but FT never does.
+
+\bigskip
+
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{line} = [draw, -latex']
+  \node (RT) at (2.5*8, 0)  {RT};
+  \node (NT) at (1.67*8,0)  {NT};
+  \node (FT) at (1.25*8,0)  {FT};
+  \node (TT) at (1*8,-0.5)     {TT};
+  \node (RF) at (2*8,0)     {RF};
+  \node (NF) at (1.33*8,-0.5)  {NF};
+  \node (FF) at (1*8,0)   {FF};
+  \node (TF) at (0.8*8,-0.5)   {TF};
+  \node (RN) at (1.5*8,0)   {RN};
+  \node (NN) at (1*8,0.5)     {NN};
+  \node (FN) at (0.75*8,0)  {FN};
+  \node (TN) at (0.6*8,0)   {TN};
+  \node (RR) at (1*8,1.0)  {RR};
+  \node (NR) at (0.67*8,-0.5)  {NR};
+  \node (FR) at (0.5*8,0)   {FR};
+  \node (TR) at (0.4*8,0)   {TR};
+  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
+  \node (level) at (1*8,2) {\underline{Level sonority}};
+  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
+  % axis
+  \node (axisstart) at (-0.23,-1.0) {};
+  \node (axisend)   at (2.7*8,-1.0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
+  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
+  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
+  \node (0pointlabel) at (0.0,-1.5) {0};
+  \node (1pointlabel) at (1.0*8,-1.5) {1};
+  \node (2pointlabel) at (2.0*8,-1.5) {2};
+  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
+\end{tikzpicture}
+}
 

### 2013-09-18 paper.tex
Fixed analysis of idiolect b and added diagram
Added all remaining diagrams

@@
 
-%\vspace{-3em}
-%\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchydividingline1.9}}
-
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc *ComplexCoda}
-
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\bigskip
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
+  \tikzstyle{line} = [draw, -latex']
+
+	\node (TR) at (0.124354994547*8, 1) {TR};
+	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
+	\node (FR) at (0.218668945874*8, 1) {FR};
+	\node (TN) at (0.266252049151*8, 1.5) {TN};
+	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
+	\node (NR) at (0.463647609001*8, 1) {NR};
+	\node (FN) at (0.540419500271*8, 0.5) {FN};
+	\node (TF) at (0.588002603548*8, 1) {TF};
+	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
+	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
+	\node (RR) at (1.10714871779*8, 1) {RR};
+	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
+	\node (NN) at (1.2490457724*8, 1) {NN};
+	\node (FF) at (1.32581766367*8, 1.5) {FF};
+	\node (TT) at (1.37340076695*8, 1) {TT};
+	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
+	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
+	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
+	\node (NF) at (2.0344439358*8, 1) {NF};
+%	\node (GF) at (2.0344439358*8, 1.5) {GF};
+	\node (FT) at (2.11121582707*8, 0.5) {FT};
+	\node (bF) at (2.17308367293*8, 1) {bF};
+	\node (RF) at (2.21429743559*8, 1.5) {RF};
+	\node (RT) at (2.35619449019*8, 1) {RT};
+	\node (NT) at (2.35619449019*8, 0.5) {NT};
+	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
+  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
+  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
+  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
+  % axis
+  \node (axisstart) at (-0.23,0) {};
+  \node (axisend)   at (2.7*8,0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
+  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
+  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
+  \node (0pointlabel) at (0.0,-0.5) {0};
+  \node (1pointlabel) at (1.0*8,-0.5) {1};
+  \node (2pointlabel) at (2.0*8,-0.5) {2};
+  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
+  % dividing line
+  \node (dividinglinestart) at (1.9 * 8,2) {};
+  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
+  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
+  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
+\end{tikzpicture}
+}
+
+\ex. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc *ComplexCoda} \\[0.5ex]
 \hline \hline a. &   & \textipa{k1rm} & & $\ast$! \\
@@
 \bigskip
-
 \resizebox{\linewidth}{!}{
@@
 
-% TODO: diagram
+\bigskip
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{vertex}=[circle]
+  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
+  \tikzstyle{line} = [draw, -latex']
+  \node (RT) at (3*3,2.0)   {RT};
+  \node (NT) at (2*3,1.5)  {NT};
+  \node (FT) at (1*3,1.0)  {FT};
+  \node (TT) at (0*3,0.5)     {TT};
+  \node (RF) at (2*3,2.0)     {RF};
+  \node (NF) at (1*3,1.5)  {NF};
+  \node (FF) at (0*3,1.0)   {FF};
+  \node (TF) at (-1*3,0.5)   {TF};
+  \node (RN) at (1*3,2.0)   {RN};
+  \node (NN) at (0*3,1.5)   {NN};
+  \node (FN) at (-1*3,1)  {FN};
+  \node (TN) at (-2*3,0.5)   {TN};
+  \node (RR) at (0*3,2.0)  {RR};
+  \node (NR) at (-1*3,1.5)  {NR};
+  \node (FR) at (-2*3,1.0)   {FR};
+  \node (TR) at (-3*3,0.5)   {TR};
+  % headers
+  \node (rising) at (2*3,2.6) {\underline{Falling sonority}};
+  \node (level) at (0*3,2.6) {\underline{Level sonority}};
+  \node (falling) at (-2*3,2.6) {\underline{Rising sonority}};
+  % axis
+  \node (axisstart) at (-3.5*3,-0) {};
+  \node (axisend)   at (3.5*3,-0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0, 0.2) -- (0, -0.2) -- cycle;
+  \draw (1*3, 0.2) -- (1*3, -0.2) -- cycle;
+  \draw (2*3, 0.2) -- (2*3, -0.2) -- cycle;
+  \draw (3*3, 0.2) -- (3*3, -0.2) -- cycle;
+  \draw (-1*3, 0.2) -- (-1*3, -0.2) -- cycle;
+  \draw (-2*3, 0.2) -- (-2*3, -0.2) -- cycle;
+  \draw (-3*3, 0.2) -- (-3*3, -0.2) -- cycle;
+  \node (0pointlabel) at (0.0,-0.5) {0};
+  \node (1pointlabel) at (1.0*3,-0.5) {1};
+  \node (2pointlabel) at (2.0*3,-0.5) {2};
+  \node (3pointlabel) at (3.0*3,-0.5) {3};
+  \node (-1pointlabel) at (-1.0*3,-0.5) {-1};
+  \node (-2pointlabel) at (-2.0*3,-0.5) {-2};
+  \node (-3pointlabel) at (-3.0*3,-0.5) {-3};
+  \node (xaxislabel) at (3.5*3,-0.5) {\textsc{Dis}};
+\end{tikzpicture}
+}
 
@@
 
-% TODO: scale
-
 \ex. \a. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect \ref{defaultCCCidiolect}:
@@
 
-% TODO: SonAngle diagram showing the various cut-off points.
-
-The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects 1, 3 and 4, but notice that this is not possible for idiolect \ref{CRNidiolect}, because {\sc Sonority Rise} cannot achieve a linear separation of the sonority rises, plateaus and RN from the remainder of the falling sonority clusters.
-
-% TODO: SonRise diagram
-
+\bigskip
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
+  \tikzstyle{line} = [draw, -latex']
+
+	\node (TR) at (0.124354994547*8, 1) {TR};
+	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
+	\node (FR) at (0.218668945874*8, 1) {FR};
+	\node (TN) at (0.266252049151*8, 1.5) {TN};
+	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
+	\node (NR) at (0.463647609001*8, 1) {NR};
+	\node (FN) at (0.540419500271*8, 0.5) {FN};
+	\node (TF) at (0.588002603548*8, 1) {TF};
+	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
+	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
+	\node (RR) at (1.10714871779*8, 1) {RR};
+	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
+	\node (NN) at (1.2490457724*8, 1) {NN};
+	\node (FF) at (1.32581766367*8, 1.5) {FF};
+	\node (TT) at (1.37340076695*8, 1) {TT};
+	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
+	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
+	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
+	\node (NF) at (2.0344439358*8, 1) {NF};
+%	\node (GF) at (2.0344439358*8, 1.5) {GF};
+	\node (FT) at (2.11121582707*8, 0.5) {FT};
+	\node (bF) at (2.17308367293*8, 1) {bF};
+	\node (RF) at (2.21429743559*8, 1.5) {RF};
+	\node (RT) at (2.35619449019*8, 1) {RT};
+	\node (NT) at (2.35619449019*8, 0.5) {NT};
+	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
+  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
+  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
+  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
+  % axis
+  \node (axisstart) at (-0.23,0) {};
+  \node (axisend)   at (2.7*8,0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
+  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
+  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
+  \node (0pointlabel) at (0.0,-0.5) {0};
+  \node (1pointlabel) at (1.0*8,-0.5) {1};
+  \node (2pointlabel) at (2.0*8,-0.5) {2};
+  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
+  % dividing line
+  \node (dividinglinestart) at (1.9 * 8,2) {};
+  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
+  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
+  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
+  \node (dividingpointlabel2) at (1.9*8, -1.0) {\ref{CRNidiolect}};
+  % another dividing line
+  \node (dividingline2start) at (1.5 * 8,2) {};
+  \node (dividingline2end)   at (1.5 * 8,-0.3) {};
+  \path [line,dashed] (dividingline2start) -- (dividingline2end) -- cycle;
+  \node (dividingpoint2label) at (1.5*8, -0.5) {1.5};
+  \node (dividingpoint2label2) at (1.5*8, -1.0) {\ref{defaultCCCidiolect} \& \ref{C1CCidiolect}};
+  % third dividing line
+  \node (dividingline3start) at (1.0 * 8,2) {};
+  \node (dividingline3end)   at (1.0 * 8,-0.3) {};
+  \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;
+  \node (dividingpoint3label2) at (1.0*8, -1.0) {\ref{wizfidiolect}};
+\end{tikzpicture}
+}
+
+\bigskip
+The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects \ref{defaultCCCidiolect}, \ref{C1CCidiolect} and \ref{wizfidiolect}, but notice that this is not possible for idiolect \ref{CRNidiolect}, because {\sc Sonority Rise} cannot achieve a linear separation of the sonority rises, plateaus and RN from the remainder of the falling sonority clusters.
+
+\bigskip
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{line} = [draw, -latex']
+  \node (RT) at (2.5*8, 0)  {RT};
+  \node (NT) at (1.67*8,0)  {NT};
+  \node (FT) at (1.25*8,0)  {FT};
+  \node (TT) at (1*8,-0.5)     {TT};
+  \node (RF) at (2*8,0)     {RF};
+  \node (NF) at (1.33*8,-0.5)  {NF};
+  \node (FF) at (1*8,0)   {FF};
+  \node (TF) at (0.8*8,-0.5)   {TF};
+  \node (RN) at (1.5*8,0)   {RN};
+  \node (NN) at (1*8,0.5)     {NN};
+  \node (FN) at (0.75*8,0)  {FN};
+  \node (TN) at (0.6*8,0)   {TN};
+  \node (RR) at (1*8,1.0)  {RR};
+  \node (NR) at (0.67*8,-0.5)  {NR};
+  \node (FR) at (0.5*8,0)   {FR};
+  \node (TR) at (0.4*8,0)   {TR};
+  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
+  \node (level) at (1*8,2) {\underline{Level sonority}};
+  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
+  % axis
+  \node (axisstart) at (-0.23,-1.0) {};
+  \node (axisend)   at (2.7*8,-1.0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
+  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
+  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
+  \node (0pointlabel) at (0.0,-1.5) {0};
+  \node (1pointlabel) at (1.0*8,-1.5) {1};
+  \node (2pointlabel) at (2.0*8,-1.5) {2};
+  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
+\end{tikzpicture}
+}
 \bigskip
@@
 \begin{tabular}{|l|ccc|c|cccc|} \hline
-         & \multicolumn{3}{c|}{{\sc SonAngles}} &  & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
- Cluster & C1,C2 & C2,C3 & C3,C4 & Observed outcomes & 1 & 2 & 3 & 4 \\ \hline % TODO: name idiolects
+         & \multicolumn{3}{c|}{{\sc SonAngles}} & Observed & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
+ Cluster & C1,C2 & C2,C3 & C3,C4 &  outcomes & \ref{defaultCCCidiolect} & \ref{CRNidiolect} & \ref{C1CCidiolect} & \ref{wizfidiolect} \\ \hline 
  a. \textipa{sdBn} & 2.11 & 0.18 & 1.66 & \textipa{sd1Bn} & \multicolumn{4}{c|}{\textipa{sd1Bn}} \\ 
@@
 
-\section{Disregarding V-C2}
+\subsection{Disregarding V-C2}
 

### 2013-09-18 paper.tex
Finished discussion section (except for consonant deletion), fixed lots of small errors

@@
 
-\newcommand*\circled[1]{%
-  \tikz[baseline=(C.base)]\node[draw,circle,inner sep=0.5pt](C) {#1};\!
-}
-
 \makeatletter
@@
 This raises the question of how to compute the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
-In this paper, I propose that the appropriate metric is {\sc Sonority Angle}, the angle formed by the contours C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V, and apply it in analyzing two case studies of sonority-driven epenthesis, Chaha and Irish.
+In this paper, I propose two desiderata for such a metric, and propose a metric that fits these considerations --- {\sc Sonority Angle}, the angle formed by the contours C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V.
+I apply it in analyzing two case studies of sonority-driven epenthesis, Chaha and Irish.
 A comparison is made to another possible metric,
-{\sc Sonority Rise} \citep{flemming.2008}, the ratio of the gradients of the two contours, as well as to Syllable Contact, which represents an alternative, markedness-based approach to the problem of sonority-driven epenthesis.
+{\sc Sonority Rise} \citep{flemming.2008}, the ratio of the gradients of the two contours, as well as to Syllable Contact and Sonority Sequencing, which represent an alternative, markedness-based approach to the problem of sonority-driven epenthesis.
 \end{abstract}
@@
 In this paper, I suggest that any such metric should bear two properties.
-The first is that suggested by previous analyses, that the more positive the gradient of the sonority contour from C1 to C2, the smaller the faithfulness cost and hence the more likely epenthesis is to occur.
-The second is that for a given sonority distance between C1 and C2, the more sonorous C1 and C2 are, the more likely epenthesis is to occur.
+The first is that suggested by previous analyses, that the more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost and hence the more likely epenthesis is to occur.
+The second is that for a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the more likely epenthesis is to occur.
 
 To make things concrete, I suggest a metric that possesses these two properties, which I term {\sc Sonority Angle}.
-This is the magnitude of the angle made by the vectors C\textsubscript{1}-C\textsubscript{2} and C\textsubscript{1}-V.
+This is the magnitude of the angle made by the vectors C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V.
 I then explore the ramifications of this choice.
 
-{\sc Sonority Angle} makes the same broad predictions as {\sc Sonority Rise} --- that clusters of rising sonority, having a relatively small angle between the underlying sonority contour /C\textsubscript{1}-C\textsubscript{2}/ and the overt sonority contour [C\textsubscript{1}-V], are perceptually more similar to their epenthetic output, and therefore more likely to undergo epenthesis, than clusters of falling sonority.
+{\sc Sonority Angle} makes the same broad predictions as {\sc Sonority Rise} --- that clusters of rising sonority, having a relatively small angle between the underlying sonority contour /C\textsubscript{1}C\textsubscript{2}/ and the overt sonority contour [C\textsubscript{1}V], are perceptually more similar to their epenthetic output, and therefore more likely to undergo epenthesis, than clusters of falling sonority.
 Crucially, however, the exact hierarchy of susceptibility of individual clusters to epenthesis is predicted to be different.
@@
 sonority-driven epenthesis. I introduce the proposed {\sc Sonority Angle} metric as well as the competing {\sc Sonority Rise} metric \citep{flemming.2008}, 
-then lay out the alternative markedness-based approach to sonority-driven epenthesis, namely {\sc Syllable Contact}.
+then lay out the alternative markedness-based approach to sonority-driven epenthesis, namely Syllable Contact.
 
@@
 In order to determine what faithfulness constraints exist in {\sc Con} and what their rankings should be, therefore, we need to know the metrics of perceptual distance that are relevant to each change.
-In the case of vowel epenthesis, the perceptual distance to be measured is between two sonority contours, /C1-C2/ and [C\textsubscript{1}-V-C\textsubscript{2}].
+In the case of vowel epenthesis, the perceptual distance to be measured is between two sonority contours, /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}].
 
@@
 
-When C1 (and, by extension, C2) is of higher sonority, as on the right, the V-C1-C2 angle is clearlysmaller.
+When C\textsubscript{1} (and, by extension, C\textsubscript{2}) is of higher sonority, as on the right, the VC\textsubscript{1}C\textsubscript{2} angle is clearlysmaller.
 The first term in the formula confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.
@@
 
-\ex. \textsc{Ident(SonAngle)}$<n$: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
+\ex. \textsc{Ident(SonAngle)}$<$n: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
 stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$.
@@
 \ex. {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{M}$
-     \a. Scenario 1: {\sc SonAngle}(C1-C2), {\sc SonAngle}(C2,C3)$<$n \\
+     \a. Scenario 1: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
          Since neither violates {\sc Ident(SonAngle)}$<$n, $\mathcal{M}$ determines output.
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n & $\mathcal{M}$ \\[0.5ex]
-\hline \hline a. & \ding{43} & C1C2\textipa{@}C3 & $<$n & \\
-\hline b. & & C1\textipa{@}C2C3 & $<$n & $\ast$! \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-      \b. Scenario 2: {\sc SonAngle}(C1-C2)$>$n, {\sc SonAngle}(C2,C3)$<$n \\
-          C1\textipa{@}C2C3 harmonically bound by C1C2\textipa{@}C3 candidate.
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
-\hline \hline c. & \ding{43} &  C1C2\textipa{@}C3  & $<$n & \cellcolor{lightgray} \\
-\hline d. & & C1\textipa{@}C2C3 & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \c. Scenario 3: {\sc SonAngle}(C1-C2)$<$n, {\sc SonAngle}(C2,C3)$>$n \\
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n & $\mathcal{M}$ \\[0.5ex]
+\hline \hline a. & \ding{43} & C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $<$n & \\
+\hline b. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $<$n & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+      \b. Scenario 2: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
+          C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline c. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}  & $<$n & \cellcolor{lightgray} \\
+\hline d. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
          {\sc Ident(SonAngle)}$<$n determines output, overruling $\mathcal{M}$.
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
-\hline \hline e. & &  C1C2\textipa{@}C3 & $>$n $\ast$!  & \cellcolor{lightgray} \\
-\hline f. & \ding{43} & C1\textipa{@}C2C3& $>$n & \cellcolor{lightgray}$\ast$ \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \d. Scenario 4: {\sc SonAngle}(C1-C2), {\sc SonAngle}(C2-C3) $>$ n \\
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline e. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$!  & \cellcolor{lightgray} \\
+\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $>$n & \cellcolor{lightgray}$\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ n \\
          Since both candidates violate {\sc Ident(SonAngle)}$<$n, $\mathcal{M}$ determines output.
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
-\hline \hline g. & &  C1C2\textipa{@}C3 & $>$n $\ast$  & \\
-\hline h. & \ding{43} & C1\textipa{@}C2C3 & $>$n $\ast$ & $\ast$ \\
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline g. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$  & \\
+\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 Because we have assumed that all other {\sc Ident(SonAngle)}$<$n constraints rank low, certainly below $\mathcal{M}$, the degree to which candidates (g) and (h) violate {\sc Ident(SonAngle)}$<$n is irrelevant --- the distinction between clusters with {\sc Sonority Angles} above $n$ has been conflated.
-Even if {\sc Sonority Angle}(C2,C3) exceeds {\sc Sonority Angle}(C1,C2), the outcome is determined by the markedness constraint $\mathcal{M}$.
+Even if {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3}) exceeds {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}), the outcome is determined by the markedness constraint $\mathcal{M}$.
 
@@
 
-\ex. Scenario: {\sc SonAngle}(C2-C3) $>$ {\sc SonAngle}(C1-C2) $>$ n \\
+\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C1C2C3/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Ident(SonAngle)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
-\hline \hline a. & \ding{43} &  C1C2\textipa{@}C3 & 2.0 $\ast$!  & 2.0 $\ast$ &  \\
-\hline b.  & & C1\textipa{@}C2C3 & 1.7  & 1.7 $\ast$ & $\ast$ \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-Under a universal ranking of {\sc Ident(SonAngle)}$<$n constraints, [C1C2\textipa{@}C3] would win in this scenario.
-In an equivalent scenario under free-ranking, where {\sc Ident(SonAngle)}$<$1.5 is the least stringent constraint to outrank $\mathcal{M}$, which in turn outranks all more stringent {\sc Ident(SonAngle)}$<$n constraints, the [C1C2\textipa{@}C3] candidate would win instead.
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Ident(SonAngle)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
+\hline \hline a. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} &  2.0 $\ast$!  & \cellcolor{lightgray} 2.0 $\ast$ & \cellcolor{lightgray} \\
+\hline b.  & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} &  1.7  & \cellcolor{lightgray} 1.7 $\ast$ & \cellcolor{lightgray} $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Under a universal ranking of {\sc Ident(SonAngle)}$<$n constraints, [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] would win in this scenario.
+In an equivalent scenario under free-ranking, where {\sc Ident(SonAngle)}$<$1.5 is the least stringent constraint to outrank $\mathcal{M}$, which in turn outranks all more stringent {\sc Ident(SonAngle)}$<$n constraints, the [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] candidate would win instead.
 There would be conflation of all clusters with {\sc Sonority Angles} below $n$, but distinctions between clusters with {\sc Sonority Angles} would still be relevant.
@@
 
-As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<n$, defined similarly to {\sc Ident(SonAngle)}$<$n.
+As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<$n, defined similarly to {\sc Ident(SonAngle)}$<$n.
 
@@
 
-I will formalise this restriction with the constraint {\sc Dep(+sonorant)}.
+I will formalise this restriction with the constraint {\sc Dep}(+sonorant).
 The epenthesis of a vowel between two obstruents, which bear the feature [$-$sonorant], necessitates the insertion of a new [+sonorant] feature, whereas when a vowel is epenthesised adjacent to a sonorant, the sonorant's [+sonorant] feature spreads and is shared between the vowel and the sonorant.
@@
 This constraint will be used in the analysis of Chaha complex coda epenthesis, which in some idiolects
-cannot occur between obstruents, while in others, it can. My proposal will be that in the former, {\sc Dep(+sonorant)} is higher-ranked, thus blocking epenthesis.
+cannot occur between obstruents, while in others, it can. My proposal will be that in the former, {\sc Dep}(+sonorant) is higher-ranked, thus blocking epenthesis.
 
@@
 Therefore, when sonority-driven epenthesis occurs in onsets or codas, other sonority-based markedness constraints must be employed.
-One such is {\sc Sonority Sequencing} \citep{selkirk.1984}, which states that sonority must be strictly increasing in the onset and strictly decreasing in the coda.
+One such is  Sonority Sequencing \citep{selkirk.1984}, which states that sonority must be strictly increasing in the onset and strictly decreasing in the coda.
 \citep{rose.2000} uses two variants of this constraint, one strict and one non-strict, in her analysis of Chaha.
@@
 Lastly, we come to the sonority-driven aspect of the analysis.  
-Epenthesis is allowed when C1 is ``followed by a voiced stop, fricative, nasal or liquid, but not when it is followed by a voiceless stop.'' \citep{carnie.1994}
+Epenthesis is allowed when C\textsubscript{1} is ``followed by a voiced stop, fricative, nasal or liquid, but not when it is followed by a voiceless stop.'' \citep{carnie.1994}
 
@@
 \begin{tabular}{c | c c c c c}
- \backslashbox{C1}{C2}      & Stop & Fricative & Nasal & Liquid \\ \hline
+ \backslashbox{C\textsubscript{1}}{C\textsubscript{2}}      & Stop & Fricative & Nasal & Liquid \\ \hline
 Stop   & \textbf{OPTIONAL}   & \textbf{OPTIONAL} & \textbf{\tickYes} & \textbf{\tickYes} \\
@@
 Triconsonantal clusters must be broken up via epenthesis, indicating that {\sc *CCC} $\gg$ {\sc Dep}.
-If epenthesis occurs either between C1-C2 or between C2-C3, {\sc *CCC} will be satisfied.
+If epenthesis occurs either between C\textsubscript{1}C\textsubscript{2} or between C\textsubscript{2}-C\textsubscript{3}, {\sc *CCC} will be satisfied.
 We do not need a separate constraint to prevent double epenthesis occurring to produce *[C\textipa{1}C\textipa{1}C].
@@
 \ex. \a. ``Default idiolect'', discussed in Section 4.3 of \citep{rose.2000}. \label{defaultCCCidiolect}
-           \a. [C\textipa{1}CC] iff C1-C2 is a fall and C2-C3 is a rise or plateau.
+           \a. [C\textipa{1}CC] iff C\textsubscript{1}C\textsubscript{2} is a fall and C\textsubscript{2}-C\textsubscript{3} is a rise or plateau.
            \b. [CC\textipa{1}C] otherwise.
@@
      \b. [CR\textipa{1}N] idiolect, discussed in Section 5.2.2 of \citep{rose.2000}. \label{CRNidiolect}
-           \a. [CC\textipa{1}C] if C2 is [r] and C3 is a sonorant.
+           \a. [CC\textipa{1}C] if C\textsubscript{2} is [r] and C\textsubscript{3} is a sonorant.
            \b. Otherwise as default.
@@
      \c. [C\textipa{1}CC] idiolect, discussed in Section 5.2.1 of \citep{rose.2000}. \label{C1CCidiolect}
-           \a. [CC\textipa{1}C] iff C2-C3 is a fall and C1-C2 is a rise or plateau.
+           \a. [CC\textipa{1}C] iff C\textsubscript{2}-C\textsubscript{3} is a fall and C\textsubscript{1}C\textsubscript{2} is a rise or plateau.
            \b. [C\textipa{1}CC] otherwise.
@@
 
-\noindent {\bf Default idiolect.} In the default idiolect \ref{defaultCCCidiolect}, epenthesis occurs between C2 and C3 to form [CC\textipa{1}C].
-Only when C1-C2 constitutes a sonority rise or plateau, and C2-C3 constitutes a sonority fall, does epenthesis occur between C1 and C2 to form [C\textipa{1}CC].
+\noindent {\bf Default idiolect.} In the default idiolect \ref{defaultCCCidiolect}, epenthesis occurs between C\textsubscript{2} and C\textsubscript{3} to form [CC\textipa{1}C].
+Only when C\textsubscript{1}C\textsubscript{2} constitutes a sonority rise or plateau, and C\textsubscript{2}-C\textsubscript{3} constitutes a sonority fall, does epenthesis occur between C\textsubscript{1} and C\textsubscript{2} to form [C\textipa{1}CC].
 Forms and their associated sonority angles are shown in the table below.
@@
 \begin{tabular}{ccccc}
-	& Underlying form      & Surface form & {\sc SonAngle}(C1,C2) & {\sc SonAngle}(C2,C3) \\ \hline
+	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
     \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
@@
 
-The default preference in this idiolect is to epenthesise on the right, between C2 and C3.
+The default preference in this idiolect is to epenthesise on the right, between C\textsubscript{2} and C\textsubscript{3}.
 I encode this preference with a markedness constraint borrowed from \citep{rose.2000}'s analysis:
@@
 
-The only time that {\sc Align-Left} is overruled is when breaking up the C2-C3 cluster would be too ``expensive'' in faithfulness terms --- when the cluster consists of a sonority fall --- and breaking up the C1-C2 cluster is comparatively cheap, that is, when C1-C2 is a sonority rise or plateau.
-In {\sc Sonority Angle} terms, {\sc Align-Left} is overruled only when breaking the C2-C3 cluster would entail creating a {\sc Sonority Angle} greater than 1.5, when the alternative of breaking the C1-C2 cluster would create a {\sc Sonority Angle} smaller than 1.5.
+The only time that {\sc Align-Left} is overruled is when breaking up the C\textsubscript{2}-C\textsubscript{3} cluster would be too ``expensive'' in faithfulness terms --- when the cluster consists of a sonority fall --- and breaking up the C\textsubscript{1}C\textsubscript{2} cluster is comparatively cheap, that is, when C\textsubscript{1}C\textsubscript{2} is a sonority rise or plateau.
+In {\sc Sonority Angle} terms, {\sc Align-Left} is overruled only when breaking the C\textsubscript{2}-C\textsubscript{3} cluster would entail creating a {\sc Sonority Angle} greater than 1.5, when the alternative of breaking the C\textsubscript{1}C\textsubscript{2} cluster would create a {\sc Sonority Angle} smaller than 1.5.
 
@@
 \noindent {\bf [CR\textipa{1}N] idiolect.} In a second idiolect \ref{CRNidiolect} (c.f.
-Section 5.2.2 of \citep{rose.2000}), clusters behave much as in the default, except that when C2 is [r] and C3 is sonorant, epenthesis occurs on the right instead.
+Section 5.2.2 of \citep{rose.2000}), clusters behave much as in the default, except that when C\textsubscript{2} is [r] and C\textsubscript{3} is sonorant, epenthesis occurs on the right instead.
 
@@
 
-\ex. \a. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect \ref{defaultCCCidiolect}:
+\ex. \a. Behaviour of clusters with C\textsubscript{2}=/r/ and C\textsubscript{3}=sonorant under idiolect \ref{defaultCCCidiolect}:
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}		 
-     \b. Behaviour of clusters with C2=/r/ and C3=sonorant under idiolect \ref{CRNidiolect}:
+     \b. Behaviour of clusters with C\textsubscript{2}=/r/ and C\textsubscript{3}=sonorant under idiolect \ref{CRNidiolect}:
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
-In this idiolect, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C2-C3 constitutes a sonority rise or plateau, and C1-C2 constitutes a sonority fall.
+In this idiolect, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C\textsubscript{2}-C\textsubscript{3} constitutes a sonority rise or plateau, and C\textsubscript{1}C\textsubscript{2} constitutes a sonority fall.
 
@@
 
-\subsubsection{Comparison with alternative approaches}
+\subsubsection{Comparison to other approaches}
 
@@
     \a. Idiolect \ref{defaultCCCidiolect}: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
-          \a. [CC\textipa{1}C] unless C1-C2 violates {\sc SyllCon}
-               (is a sonority rise or plateau) and C2-C3 would not.
+          \a. [CC\textipa{1}C] unless C\textsubscript{1}C\textsubscript{2} violates {\sc SyllCon}
+               (is a sonority rise or plateau) and C\textsubscript{2}-C\textsubscript{3} would not.
           \z.
      \b. Idiolect \ref{C1CCidiolect}: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} 
-          \a. \item [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon}
-                (is a sonority rise or plateau) and C1-C2 would not.
+          \a. \item [C\textipa{1}CC] unless C\textsubscript{2}-C\textsubscript{3} violates {\sc SyllCon}
+                (is a sonority rise or plateau) and C\textsubscript{1}C\textsubscript{2} would not.
           \z.
      \c. Idiolect \ref{wizfidiolect}: {\sc SyllCon(Loose)} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} $\gg$ {\sc SyllCon}
-          \a. [C\textipa{1}CC] unless C2-C3 violates {\sc SyllCon(Loose)} 
-                (is a sonority rise) and C1-C2 would not.
+          \a. [C\textipa{1}CC] unless C\textsubscript{2}-C\textsubscript{3} violates {\sc SyllCon(Loose)} 
+                (is a sonority rise) and C\textsubscript{1}C\textsubscript{2} would not.
           \z.
@@
 
-In addition to these, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must again be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C1-C2 and C2-C3 constitute violations of {\sc SyllCon}.
+In addition to these, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must again be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C\textsubscript{1}C\textsubscript{2} and C\textsubscript{2}-C\textsubscript{3} constitute violations of {\sc SyllCon}.
 
@@
 Solutions such as [C\textipa{1}C\textipa{1}CC] and [CC\textipa{1}C\textipa{1}C] are also excluded, as these incur unnecessary violations of {\sc Ident(SonAngle)} and {\sc Dep}.
-If the middle two consonants C2 and C3 are split up by an epenthetic vowel, there is no further need for epenthesis as *CCC is already satisfied by [CC\textipa{1}CC].
+If the middle two consonants C\textsubscript{2} and C\textsubscript{3} are split up by an epenthetic vowel, there is no further need for epenthesis as *CCC is already satisfied by [CC\textipa{1}CC].
 
@@
 
-Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C2,C3) exceeds n and {\sc SonAngle}(C1,C2) and {\sc SonAngle}(C3,C4) are both smaller than n.
+Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n.
 Illustrative tableaux are shown below for n=1.5:
@@
 \ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}
-     \a. Case 1: {\sc Sonority Angle}(C2,C3)$<$1.5
+     \a. Case 1: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$<$1.5
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \b. Case 2: {\sc Sonority Angle}(C2,C3)$>=$1.5 but so is one of {\sc Sonority Angle}(C1,C2) or {\sc Sonority Angle}(C3,C4)
+     \b.
+Case 2: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$>=$1.5 but so is one of {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) or {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-      \c. Case 3: {\sc Sonority Angle}(C2,C3)$>=$1.5 and both {\sc Sonority Angle}(C1,C2) and {\sc Sonority Angle}(C3,C4)$<$1.5
+      \c.
+Case 3: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$>=$1.5 and both {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) and {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})$<$1.5
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C].
-This preference is overridden when at least one of {\sc SonAngle}(C1,C2) and {\sc SonAngle}(C3,C4) are greater than n and {\sc SonAngle}(C2,C3) is less than n.
+This preference is overridden when at least one of {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are greater than n and {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) is less than n.
 
 \ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-Left Rt}
-     \a. Case 1: Both {\sc Sonority Angle}(C1,C2) and {\sc Sonority Angle}(C3,C4)$<$1.5
+     \a. Case 1: Both {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) and {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})$<$1.5
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \b. Case 2: {\sc Sonority Angle}(C1,C2) or {\sc Sonority Angle}(C3,C4) $>=$1.5, but so is {\sc Sonority Angle}(C2,C3)
+     \b.
+Case 2: {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) or {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4}) $>=$1.5, but so is {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \c. Case 3: {\sc Sonority Angle}(C1,C2) or {\sc Sonority Angle}(C3,C4) $>=$1.5, and {\sc Sonority Angle}(C2,C3)$<$1.5
+     \c.
+Case 3: {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) or {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4}) $>=$1.5, and {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$<$1.5
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
          & \multicolumn{3}{c|}{{\sc SonAngles}} & Observed & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
- Cluster & C1,C2 & C2,C3 & C3,C4 &  outcomes & \ref{defaultCCCidiolect} & \ref{CRNidiolect} & \ref{C1CCidiolect} & \ref{wizfidiolect} \\ \hline 
+ Cluster & C\textsubscript{1},C\textsubscript{2} & C\textsubscript{2},C\textsubscript{3} & C\textsubscript{3},C\textsubscript{4} &  outcomes & \ref{defaultCCCidiolect} & \ref{CRNidiolect} & \ref{C1CCidiolect} & \ref{wizfidiolect} \\ \hline
  a. \textipa{sdBn} & 2.11 & 0.18 & 1.66 & \textipa{sd1Bn} & \multicolumn{4}{c|}{\textipa{sd1Bn}} \\ 
@@
 
-\subsection{Summary: Chaha}
+\subsection{Interim summary}
 
@@
 
-\subsection{Disregarding V-C2}
-
-In the sonority contour faithfulness approach, the relevant comparison is between C1-C2 and C1-V. But why these two vectors? In particular, why not C1-C2 versus V-C2?
-
-\ex. Left: {\sc Sonority Angle} as currently defined; right: another possible definition as the angle C1-C2-V.
+\subsection{Disregarding VC\textsubscript{2}}
+
+In the sonority contour faithfulness approach, the relevant comparison is between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V.
+But why these two vectors?
+In particular, why not C\textsubscript{1}C\textsubscript{2} versus VC\textsubscript{2}?
+
+\ex. Left: {\sc Sonority Angle} as currently defined; right: another possible definition as the angle C\textsubscript{1}C\textsubscript{2}-V.
 
@@
 The answer, currently, is based purely on empirical grounds: if we assume this comparison to be the relevant one, then we expect falling sonority contours to be more susceptible to epenthesis, which contradicts the cross-linguistic evidence.
-It would seem that there is something quite fundamental about the comparison being centred around the rightward context, or release, of C1, which may perhaps arise out of phonological processing.
+It would seem that there is something quite fundamental about the comparison being centred around the rightward context, or release, of C\textsubscript{1}, which may perhaps arise out of phonological processing.
 
@@
 
-\noindent {\bf Changes in C1.} In the discussion of Chaha triconsonantal clusters in  $\S$\ref{CCCanalysis}, I glossed over how the metric should be computed if C1 changes.
+\noindent {\bf Changes in C\textsubscript{1}.} In the discussion of Chaha triconsonantal clusters in  $\S$\ref{CCCanalysis}, I glossed over how the metric should be computed if C\textsubscript{1} changes.
 This was an issue in clusters such as /rfk/, which emerge as [nf\textipa{1}k] due to morphophonological processes.
-Ultimately, this was not an issue because the behaviour of all such clusters was independently determined by {\sc Jussive-R}, but this raises the question of how {\sc Sonority Angle} should be computed if C1 changes.
-Currently, it is undefined, as it is unclear how to measure the angle between C1-C2=RF and C1-V=NV:
+Ultimately, this was not an issue because the behaviour of all such clusters was independently determined by {\sc Jussive-R}, but this raises the question of how {\sc Sonority Angle} should be computed if C\textsubscript{1} changes.
+Currently, it is undefined, as it is unclear how to measure the angle between C\textsubscript{1}C\textsubscript{2}=RF and C\textsubscript{1}V=NV:
 
@@
 It is of course possible to define the angle as whatever is made by the intersection of the two vectors, but there is insufficient data to support this interpretation.
-Alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C1C2/ and the surface contour [C1V] does not depend on the two C1's being the same.
-
-\bigskip
-
-\noindent {\bf Horizontal distance.} In this paper, I assumed that the horizontal distance between C1 and C2, and C1 and V, is the same, and arbitrarily fixed at 1 unit, in calculating {\sc Sonority Angle}.
+Alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.
+
+\bigskip
+
+\noindent {\bf Horizontal distance.} In this paper, I assumed that the horizontal distance between C\textsubscript{1} and C\textsubscript{2}, and C\textsubscript{1} and V, is the same, and arbitrarily fixed at 1 unit, in calculating {\sc Sonority Angle}.
 This is an arbitrary choice, and potentially an important one, as when the horizontal distance gets large, changes occur in the cluster hierarchy, some of which violate the first desideratum for a sonority angle metric:
@@
 
-Additionally, since this horizontal distance is along the dimension of time, the assumption that the two horizontal distance for C1-C2 is the same as that for C1-V is likely incorrect.
+Additionally, since this horizontal distance is along the dimension of time, the assumption that the two horizontal distance for C\textsubscript{1}C\textsubscript{2} is the same as that for C\textsubscript{1}V is likely incorrect.
 If we choose different values for these two horizontal distances, the cluster hierarchy would also be likely to change.
@@
 From a phonetic standpoint, this seems unlikely.
-Observe, for example, the values obtained by \citet{parker.2002} for ???, the metric that Parker found to be the most correlated with phonological sonority:
-
-\ex. TODO: Parker sonority scale
-
-Plugging this scale into the {\sc Sonority Angle} metric, we obtain %TODO
-
-\bigskip
-
-Ultimately, the most practical course of action may be to simply attempt to experimentally determine sonority contour distances, and perhaps then fit them to a metric.
+
+Perhaps the closest thing we have to a phonetic sonority scale comes from \citet{parker.2002}, who measured various acoustic correlates of sonority and showed that phonological sonority correlates to a very high degree with intensity ({\it r} = .97--.99).
+
+\ex. Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}
+
+\begin{center}
+\begin{tabular}{cc}
+ Segments & Mean \\ \hline
+ \textipa{i I u U} & 10.65 \\
+ \textipa{e E 2 o O} & 10.21 \\
+ \textipa{\ae  a} & 9.62 \\
+ \textipa{@} &  5.73 \\
+ \textipa{y w} & 3.92 \\
+ \textipa{r} & 2.53 \\
+ \textipa{l} & 2.51 \\
+ \textipa{m n} & -4.16 \\
+ \textipa{h} & -6.05 \\
+ \textipa{v D z Z} & -6.30 \\
+ \textipa{P} & -11.10 \\
+ \textipa{f T s S} & -11.96 \\
+ \textipa{b d g dZ} & -12.41 \\
+ \textipa{p t k tS} & -13.75 \\  
+\end{tabular}	
+\end{center}
+
+Plugging these numbers into the {\sc Sonority Angle} metric and using an average of the values of the vowel and averaging together voiced and voiceless members of the same class, we obtain the following hierarchy of clusters:
+
+\ex. {\sc Sonority Angle} cluster hierarchy obtained using Parker's intensity data for English males, averaging [$\pm$voice] values for obstruent classes.
+
+\bigskip
+\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
+  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
+  \tikzstyle{line} = [draw, -latex']
+
+\node (TR) at (0.0170349973202*8, 0.5) {TR};
+	\node (FR) at (0.0279543293301*8, 1) {FR};
+	\node (TN) at (0.0646614923105*8, 1.5) {TN};
+	\node (NR) at (0.0678017301617*8, 2.0) {NR};
+	\node (FN) at (0.140883408022*8, 0.5) {FN};
+	\node (TF) at (0.200974864302*8, 1.0) {TF};
+	\node (RR) at (1.39622474153*8, 2) {RR};
+	\node (NN) at (1.49000093511*8, 1.5) {NN};
+	\node (FF) at (1.5131236339*8, 1) {FF};
+	\node (TT) at (1.52381634628*8, 0.5) {TT};
+	\node (RN) at (2.81842394648*8, 2) {RN};
+	\node (FT) at (2.83596511588*8, 1.5) {FT};
+	\node (NF) at (2.86224116099*8, 1) {NF};
+	\node (RF) at (2.8813940461*8, 0.5) {RF};
+	\node (RT) at (2.90300609049*8, 1.5) {RT};
+	\node (NT) at (2.94915578908*8, 1) {NT};
+
+  \node (rising) at (0.3*8,3) {\underline{Rising sonority}};
+  \node (level) at (1.5*8,3) {\underline{Level sonority}};
+  \node (falling) at (2.2*8,3) {\underline{Falling sonority}};
+  % axis
+  \node (axisstart) at (-0.23,0) {};
+  \node (axisend)   at (3.2*8,0) {};
+  \draw (axisstart) -- (axisend);
+  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
+  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
+  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
+  \node (0pointlabel) at (0.0,-0.5) {0};
+  \node (1pointlabel) at (1.0*8,-0.5) {1};
+  \node (2pointlabel) at (2.0*8,-0.5) {2};
+  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
+\end{tikzpicture}
+}
+
+Using this scale, we obtain the desired empirical results of this paper based on the evidence of Irish and Chaha, that RN is the most epenthesisable of all the falling sonority clusters and tha RT and NT are the clusters most resistant to epenthesis.
+However, this does not conform to the general principle that for a given sonority distance, the more sonorous the consonants, the more likely a cluster is to undergo epenthesis --- we have NF being harder to epenthesise into than FT, here.
+
+Moreover, this result is obtained by averaging stops and fricatives to ignore voicing.
+If we leave voicing intact, then these results disappear: fricative-voiceless stops are the most likely to undergo epenthesis of the falling sonority clusters, more so than liquid--nasal clusters, and if RT and NT fail to undergo epenthesis, we expect voiced fricative--voiced stop, nasal--voiceless fricative, and nasal--voiced stop clusters to also resist epenthesis.
+Both of these are contrary to the empirical results of this paper.
+
+\bigskip
+
+Ultimately, the most practical course of action may be to simply attempt to experimentally determine sonority contour distances through a perceptual experiment, then fit them to a metric based on a suitable sonority scale.
 To date, only a few sonority contour distances have been experimentally determined, for example between rising (TR) and falling (sT) clusters \citep{fleischhacker.2002}, but not finer-grained distances such as between the various falling sonority clusters.
@@
 
-\bigskip
-
 \subsection{Extensions of the metric}
@@
 We expect syncope to preferentially create falling sonority clusters.
-Under a sonority contour faithfulness account, however, we expect clusters to be created when they are similar in sonority profile to the underlying C1-V contour -- that is, rising sonority clusters should be preferentially created.
+Under a sonority contour faithfulness account, however, we expect clusters to be created when they are similar in sonority profile to the underlying C\textsubscript{1}V contour -- that is, rising sonority clusters should be preferentially created.
 
@@
 
-\noindent{\bf Consonant deletion.} The current formulation of {\sc Ident(SonAngle)}$<$n constraints restricts its application to when the consonants of a C1-C2 and C1-V-C2 sequence stand in correspondence.
-However, another formulation is possible, in which sonority contours are a property of C1 rather than a property of the whole contour.\footnote{Thanks to Adam Albright for this suggestion.}
+\noindent{\bf Consonant deletion.} The current formulation of {\sc Ident(SonAngle)}$<$n constraints restricts its application to when the consonants of a C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} sequence stand in correspondence.
+However, another formulation is possible, in which sonority contours are a property of C\textsubscript{1} rather than a property of the whole contour.\footnote{Thanks to Adam Albright for this suggestion.}
+
+\bigskip
+
+\noindent [This section remains to be written]
 
@@
 
-A possible application of this looser definition of {\sc Sonority Angle} lies in the deletion of consonants in complex onsets.
-
-% pa - pla 
-% Hawaiian loanword?
-% Sanskrit reduplication
+A possible application of this looser definition of {\sc Sonority Angle} lies in the deletion of consonants in complex onsets. (pa vs pla) - loanwords, Sanskrit reduplication
 

### 2013-09-30 paper.tex
Added angle to basic SonAngle diagram using tkz-euclide
Used package fixltx2e to add textsubscript rather than defining manually - this was raising complaints
Improved second diagram

@@
 \usetikzlibrary{matrix,arrows}
+\usepackage{tkz-euclide}
+\usetkzobj{all}
 \usepackage{slashbox}	
@@
 
-\makeatletter
-\newcommand\textsubscript[1]{\@textsubscript{\selectfont#1}}
-\def\@textsubscript#1{{\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
+\usepackage{fixltx2e}
+
+%\makeatletter
+%\newcommand\textsubscript[1]{\@textsubscript{\selectfont#1}}
+%\def\@textsubscript#1{{\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
 \newcommand{\iep}{\textipa{1}}
@@
 
-\ex. \label{sonangle_picture} \begin{tikzpicture} [shorten >=1pt,scale=0.33]
+\ex. Visual representation of {\sc Sonority Angle} \label{sonangle_picture}
+
+\vspace{-3em}
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
                       \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
@@
                       \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
-                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+%                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
                       \node[left] at (0,3) {C$_1$}; 
@@
     \coordinate (C) at (5,6);
+\tkzMarkAngle[size=1.5cm](B,A,C)
+\tkzLabelAngle[pos=2](B,A,C){$\theta$}
 \end{tikzpicture} 
+\end{center}
 
@@
 
-Let us verify that {\sc Sonority Angle} does indeed reflect the two generalisations we wish to make:
-first, that the smaller the sonority distance between C\textsubscript{1} and C\textsubscript{2},
-the smaller the sonority angle.
-Imagine fixing C\textsubscript{1} as in \ref{sonangle_picture} and raising the sonority of C\textsubscript{2}. Intuitively, this decreases the {\sc Sonority Angle}, comparing the two below.
-
-\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
-                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
-                      \node at (-3, 7.0) {Sonority}; % axis label
+Let us verify that {\sc Sonority Angle} does indeed reflect the two generalisations we wish to make: first, that the smaller the sonority distance between C\textsubscript{1} and C\textsubscript{2}, the smaller the sonority angle.
+
+\ex. Illustration: keeping C\textsubscript{1} fixed, raising the sonority of C\textsubscript{2} decreases the {\sc Sonority Angle}.
+
+\vspace{-5em}
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,12) -- (-3, 0.5) ; % axis
+                      \node at (-3, 13.0) {Sonority}; % axis label
 					 % left diagram
-                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
-                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
-                      \node[left] at  (0,3) {C$_1$}; 
-                      \node[right] at (5,1) {C$_2$};
-                      \node[right] at (5,6) {V};
-					  % right diagram
-                      \draw (20,4) -- (15,3) -- (20,6) ; % falling sonority
-                      \node at (17.5, 4.0) {$\theta$}; % theta label for falling sonority
-                      \node[left] at (15,3) {C$_1$}; 
-                      \node[right] at (20,4) {C$_2$};
-                      \node[right] at (20,6) {V};
+    \coordinate (A) at (0,6); % pivot - C1
+    \coordinate (B) at (15,2); % C2
+    \coordinate (C) at (15,12); % V
+    \draw (B) -- (A) -- (C);
+	\tkzMarkAngle[size=3cm](B,A,C);
+	\tkzLabelAngle[pos=4](B,A,C){$\theta_1$};
+    \coordinate (D) at (15,8); % another C2
+    \draw (D) -- (A);
+	\tkzMarkAngle[size=6cm](D,A,C);
+	\tkzLabelAngle[pos=8](D,A,C){$\theta_2$};
+
+    \node[left] at  (A) {N}; 
+    \node[right] at (B) {T};
+    \node[right] at (C) {V};
+    \node[right] at (D) {R};
+
+    \draw [->,dotted] (B) -- (D);
 \end{tikzpicture} 
+\end{center}
 

### 2013-09-30 paper.tex
Improved third diagram

@@
 
-\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
-                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
-                      \node at (-3, 7.0) {Sonority}; % axis label
+\newpage
+
+\ex. Illustration: keeping C\textsubscript{1} -- C\textsubscript{2} fixed at 1, raising the sonority in cluster decreases the {\sc Sonority Angle}.
+
+\vspace{-5em}
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,12) -- (-3, 0.5) ; % axis
+                      \node at (-3, 13.0) {Sonority}; % axis label
 					 % left diagram
-                      \draw (5,1) -- (0,3) -- (5,6) ; % 
-                      \node at (1.8, 3.2) {$\theta$}; % 
-                      \node[left] at  (0,3) {C$_1$}; 
-                      \node[right] at (5,1) {C$_2$};
-                      \node[right] at (5,6) {V};
-					  % right diagram
-                      \draw (20,3) -- (15,5) -- (20,6) ; % rising sonority
-                      \node at (18, 4.8) {$\theta$}; % theta label for falling sonority
-                      \node[left] at (15,5) {C$_1$}; 
-                      \node[right] at (20,3) {C$_2$};
-                      \node[right] at (20,6) {V};
+    \coordinate (A) at (0,4); % pivot - C1 - F * 3
+    \coordinate (B) at (15,2); % C2 - T * 3
+    \coordinate (C) at (15,12); % V
+    \draw (B) -- (A) -- (C);
+	\tkzMarkAngle[size=2.5cm](B,A,C);
+	\tkzLabelAngle[pos=4](B,A,C){$\theta_1$};
+    \coordinate (D) at (15,6); % another C2 - N * 3
+    \coordinate (E) at (0,8); % another C1 - R * 3
+    \draw (D) -- (E) -- (C);
+	\tkzMarkAngle[size=2.5cm](D,E,C);
+	\tkzLabelAngle[pos=4](D,E,C){$\theta_2$};
+
+    \node[left] at  (A) {F}; 
+    \node[right] at (B) {T};
+    \node[right] at (C) {V};
+    \node[right] at (D) {N};
+    \node[left] at (E) {R};   
+    \draw [->,dotted] (B) -- (D);
+    \draw [->,dotted] (A) -- (E);
 \end{tikzpicture} 
-
-When C\textsubscript{1} (and, by extension, C\textsubscript{2}) is of higher sonority, as on the right, the VC\textsubscript{1}C\textsubscript{2} angle is clearlysmaller.
-The first term in the formula confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.
+\end{center}
+
+The first term in formula \ref{sonangle_formula} confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.
 

### 2013-09-30 paper.tex
Added SonAngle numbers to SonAngle hierarchy diagram

@@
 
-Fleischhacker's analysis rested on empirical determinations of sonority contour faithfulness, and did not attempt to determine such a relation.
+Fleischhacker's analysis rested on empirical determinations of sonority contour faithfulness of specific clusters such as stop-liquid (TR) clusters and fricative-stop (FT) clusters, and did not attempt to determine a formula for arbitrary values of C\textsubscript{1}, C\textsubscript{2}.
 \citet{steriade.2006} proposed that input and output sonority contours should match in terms of whether they are rising or falling, and to what degree, but did not suggest a concrete mathematical relation.
@@
 
-In this paper, I suggest that any such metric should bear two properties.
-The first is that suggested by previous analyses, that the more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost and hence the more likely epenthesis is to occur.
-The second is that for a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the more likely epenthesis is to occur.
+In this paper, I suggest that any such metric should bear two properties. The first is suggested by previous analyses, while the second is original to this paper.
+
+\ex. Desiderata for a sonority contour similarity metric \label{desiderata}
+     \a. The more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost.
+     \b. For a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the smaller the faithfulness cost.
 
@@
 Syllable Contact forms the basis for the main existing analysis of Chaha epenthesis by \citet{rose.2000}.
-I show that the faithfulness-based analysis, powered by the metric of {\sc Sonority Angle}, is slightly more economical in addressing the data.
+I show that the faithfulness-based analysis, powered by the metric of {\sc Sonority Angle}, is equally capable of explaining the Chaha facts.
 Furthermore, in the case of Irish, Syllable Contact makes incorrect predictions regarding the data.
@@
 
-The observation with which we started was that the more steeply rising the sonority profile of a consonant cluster, the more likely the cluster to undergo epenthesis.
+The first desideratum with which we started was that the more steeply rising the sonority profile of a consonant cluster, the more likely the cluster to undergo epenthesis.
 Thus the absolute difference in sonority between C\textsubscript{1} and C\textsubscript{2} must be factored into the metric.
@@
 
-These two factors are neatly captured by the metric {\sc Sonority Angle}, which is defined as the angle between the underlying C\textsubscript{1}C\textsubscript{2} sonority contour and the surface C\textsubscript{1}V contour:
+These two criteria are fulfilled by the metric {\sc Sonority Angle}, which is defined as the angle between the underlying C\textsubscript{1}C\textsubscript{2} sonority contour and the surface C\textsubscript{1}V contour:
 
@@
 
-\vspace{-5em}
+\vspace{-9em}
 \begin{center}
@@
 
+\bigskip
+
 Given a sonority scale where classes of consonants are mapped to a numerical sonority, we can now calculate the {\sc Sonority Angle} for any cluster, which can be thought of as the faithfulness cost of epenthesising between the two consonants.
@@
 
-We formalise the idea of the faithfulness cost by defining a family of \textsc{Ident} constraints that penalise outputs that incur faithfulness costs of greater than a certain $n$.
+I formalise the idea of faithfulness cost by defining a family of \textsc{Ident} constraints that penalise outputs that incur faithfulness costs of greater than a certain $n$, following \citep{flemming.2008}.
 
@@
 
-This family of faithfulness constraints forms a stringency hierarchy.
-Any cluster that would, upon epenthesis, violate \textsc{Ident(SonAngle)}$<$n would also violate {\sc Ident(SonAngle)}$<$m where m$>$n.
+This family of faithfulness constraints forms a stringency hierarchy. Any cluster that would violate \textsc{Ident(SonAngle)}$<$n, would also violate {\sc Ident(SonAngle)}$<$m, where m$>$n.
+
 The resulting hierarchy of clusters, ranked according to their resistance to epenthesis as defined
@@
 Notice that out of the falling sonority clusters, those that decrease in sonority by a single step
--- namely RN, NF and FT -- have smaller {\sc Sonority Angles} than the ones that have a greater fall
+--- namely RN, NF and FT --- have smaller {\sc Sonority Angles} than the ones that have a greater fall
 in sonority.

### 2013-09-30 paper.tex
Changed SonAngle abbrev to Son$\measuredangle$ and miscellaneous edits

@@
 \usepackage{wasysym}   %for frowny face
+\usepackage{amssymb} % for angle symbol
 
@@
 
-In this paper, I adopt (with, later, minor modifications) the following standard scale:
+In this paper, I adopt (with, later, minor modifications) the following standard scale \citep[(10)]{flemming.2008}:
 
@@
 
-I formalise the idea of faithfulness cost by defining a family of \textsc{Ident} constraints that penalise outputs that incur faithfulness costs of greater than a certain $n$, following \citep{flemming.2008}.
-
-\ex. \textsc{Ident(SonAngle)}$<$n: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
-stand in correspondence, and the sonority angle between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$.
-
-This family of faithfulness constraints forms a stringency hierarchy. Any cluster that would violate \textsc{Ident(SonAngle)}$<$n, would also violate {\sc Ident(SonAngle)}$<$m, where m$>$n.
+I formalise the idea of faithfulness cost by defining a family of \textsc{Ident} constraints that penalise outputs that incur faithfulness costs of greater than a certain $n$, following \cite{flemming.2008}.
+
+\ex. \textsc{Ident(Son$\measuredangle$)}$<$n: Assign a violation mark if the consonants in two strings C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} 
+stand in correspondence, and the {\sc Sonority Angle} between C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}V is greater than $n$.
+
+This family of faithfulness constraints forms a stringency hierarchy.
+Any cluster that would violate \textsc{Ident(Son$\measuredangle$)}$<$n, would also violate {\sc Ident(Son$\measuredangle$)}$<$m, where m$>$n.
 
@@
 
-Similarly, between the clusters that fall in sonority by two steps -- RF and NT -- we expect
-NT to be less likely to undergo epenthesis, since N is less sonorous than R. We expect NT and RT to be the clusters most resistant to epenthesis out of all the clusters. This will be crucial 
-to our analysis of Irish sonority-driven epenthesis.
+Similarly, between the clusters that fall in sonority by two steps --- RF and NT --- we expect
+NT to be less likely to undergo epenthesis, since N is less sonorous than R.
+
+Among falling clusters that share the same C\textsubscript{2}, there is a tension between wanting a small sonority distance and wanting C\textsubscript{1} to have as high a sonority as possible.
+RT and NT resolve this in different ways, ending up with the same {\sc Sonority Angle}, which is the largest out of the all the clusters.
+We thus expect NT and RT to be the clusters most resistant to epenthesis out of all the clusters.
+This will be crucial to our analysis of Irish sonority-driven epenthesis.
 
@@
 
-There are two possible ways to rank the family of {\sc Ident(SonAngle)}$<$n constraints.
+There are two possible ways to rank the family of {\sc Ident(Son$\measuredangle$)}$<$n constraints.
 One is to fix them in a universal ranking \citep{prince.smolensky.1993}, with least stringent the highest-ranked:
@@
 \ex. Universal ranking: \\
-     {\sc Ident(SonAngle)}$<$2.0 $\gg$ {\sc Ident(SonAngle)}$<$1.5 $\gg$ ...
+     {\sc Ident(Son$\measuredangle$)}$<$2.0 $\gg$ {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ ...
 
@@
 \ex. Possible free ranking:
-     {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Ident(SonAngle)}$<$2.0 $\gg$ ...
-
-Depending on what constraints intervene, this may result in conflation of certain areas of the hierarchy, so that any distinctions between {\sc Sonority Angles} between 1.5 and 2.0 may be conflated.
-
-\bigskip
-
-In this paper, for ease of analysis, I will assume that all {\sc Ident(SonAngle)}$<$n constraints are ranked low by default, but that individual {\sc Ident(SonAngle)}$<$n constraints can be promoted to dominate a markedness constraint $\mathcal{M}$ against clusters or another faithfulness constraint $\mathcal{F}$, blocking epenthesis for all clusters with a {\sc Sonority Angle} greater than $n$, with the result that either the cluster remains intact, or a competing solution to epenthesis emerges.
-
-An example of {\sc Ident(SonAngle)}$<$n blocking epenthesis is given in the sample tableaux below.
+     {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Ident(Son$\measuredangle$)}$<$2.0 $\gg$ ...
+
+Depending on what constraints intervene, this may result in conflation of certain areas of the hierarchy, so that any distinctions between {\sc Sonority Angles} between 1.5 and 2.0 are made irrelevant.
+
+\bigskip
+
+In this paper, for ease of analysis, I will assume that all {\sc Ident(Son$\measuredangle$)}$<$n constraints are ranked low by default, but that individual {\sc Ident(Son$\measuredangle$)}$<$n constraints can be promoted to dominate a markedness constraint $\mathcal{M}$ against clusters or another faithfulness constraint $\mathcal{F}$, blocking epenthesis for all clusters with a {\sc Sonority Angle} greater than $n$, with the result that either the cluster remains intact, or a competing solution to epenthesis emerges.
+
+An example of {\sc Ident(Son$\measuredangle$)}$<$n blocking epenthesis is given in the sample tableaux below.
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} & {\sc Dep} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc *ComplexCoda} & {\sc Dep} \\[0.5ex]
 \hline \hline a. & & TF & & $\ast$! & \cellcolor{lightgray} \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} & {\sc Dep} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc *ComplexCoda} & {\sc Dep} \\[0.5ex]
 \hline \hline c. & \ding{43} & FT & &\cellcolor{lightgray} $\ast$ & \cellcolor{lightgray} \\
@@
 
-I will illustrate the use of {\sc Ident(SonAngle)}$<$n to block epenthesis in favour of other cluster resolution strategies with an example from the loanword phonology of the Dhaka dialect of Bangla, discussed and analysed in \citep{karim.2011}.
+I will illustrate the use of {\sc Ident(Son$\measuredangle$)}$<$n to block epenthesis in favour of other cluster resolution strategies with an example from the loanword phonology of the Dhaka dialect of Bangla, which is discussed and given an alternative analysis in \citep{karim.2011}.
 Standard Bangla keeps coda clusters in words borrowed from English, but these are simplified in the Dhaka dialect in a variety of ways, including both epenthesis and deletion of one of the consonants in the cluster.
@@
 However, if we retain this ranking, we incorrectly expect RT clusters to be broken up by epenthesis rather than delete the [r].
-This can be resolved by ranking {\sc Ident(SonAngle)}$<$2.3, say, above {\sc Max}(r).
+This can be resolved by ranking {\sc Ident(Son$\measuredangle$)}$<$2.3, say, above {\sc Max}(r).
 This then blocks epenthesis in RT clusters, which have a {\sc Sonority Angle} of 2.35:
 
-\ex. {\sc *ComplexCoda}, {\sc Ident(SonAngle)}$<$2.3  $\gg$ {\sc Max}(r) $\gg$ {\sc Dep}
+\ex. {\sc *ComplexCoda}, {\sc Ident(Son$\measuredangle$)}$<$2.3  $\gg$ {\sc Max}(r) $\gg$ {\sc Dep}
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{park}/} & {\sc *ComplexCoda} & {\sc Ident(SonAngle)}$<$2.3 & {\sc Max}(r) & {\sc Dep} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{park}/} & {\sc *ComplexCoda} & {\sc Ident(Son$\measuredangle$)}$<$2.3 & {\sc Max}(r) & {\sc Dep} \\[0.5ex]
 \hline \hline a. & & \textipa{park} & $\ast$! & & \cellcolor{lightgray} & \cellcolor{lightgray} \\
@@
 
-While other analyses could possibly account for this data (see one such in \citep{karim.2011}), we see that simply ranking {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{F}$ allows us to account for it quite straightforwardly.
+While other analyses could possibly account for this data (see one such in \citep{karim.2011}), we see that simply ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{F}$ allows us to account for it quite straightforwardly.
 
@@
 Thus far, we have not made any particular use of free ranking.
-While ranking {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{M}$ does conflate all clusters with a {\sc Sonority Angle} above $n$, as well as all clusters with a {\sc Sonority Angle} below $n$, preserving only the distinction between {\sc Sonority Angles} greater and less than $n$, this could be accomplished using a universal ranking of the {\sc Ident(SonAngle)}$<$n constraints as well, as illustrated in the following example:
-
-\ex. The {\sc Ident(SonAngle)}$<$n with the smallest $n$ that outranks {\sc *ComplexCoda} determines the cut-off point.
+Although ranking \\ {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$ does conflate all clusters with a {\sc Sonority Angle} above $n$, as well as all clusters with a {\sc Sonority Angle} below $n$, preserving only the distinction between {\sc Sonority Angles} greater and less than $n$, this could be accomplished using a universal ranking of the {\sc Ident(Son$\measuredangle$)}$<$n constraints as well, as illustrated in the following example:
+
+\ex. The {\sc Ident(Son$\measuredangle$)}$<$n with the smallest $n$ that outranks {\sc *ComplexCoda} determines the cut-off point.
 
@@
 
+\bigskip
+
 Where free ranking comes into play is when two output candidates break up different clusters.
@@
 Suppose a triconsonantal cluster /CCC/ has to be broken up either as [C\textipa{@}CC] or [CC\textipa{@}C], and further that [C\textipa{@}CC] violates some additional markedness constraint $\mathcal{M}$.
-Which {\sc Ident(SonAngle)}$<$n constraint outranks $\mathcal{M}$ will then determine the positioning of the epenthetic vowel.
-
-\ex. {\sc Ident(SonAngle)}$<$n $\gg$ $\mathcal{M}$
+Which {\sc Ident(Son$\measuredangle$)}$<$n constraint outranks $\mathcal{M}$ will then determine the positioning of the epenthetic vowel.
+
+\ex. {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$
      \a. Scenario 1: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
-         Since neither violates {\sc Ident(SonAngle)}$<$n, $\mathcal{M}$ determines output.
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n & $\mathcal{M}$ \\[0.5ex]
+         Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n & $\mathcal{M}$ \\[0.5ex]
 \hline \hline a. & \ding{43} & C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $<$n & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
 \hline \hline c. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}  & $<$n & \cellcolor{lightgray} \\
@@
      \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
-         {\sc Ident(SonAngle)}$<$n determines output, overruling $\mathcal{M}$.
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+         {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
 \hline \hline e. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$!  & \cellcolor{lightgray} \\
-\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $>$n & \cellcolor{lightgray}$\ast$ \\
+\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $<$n  & \cellcolor{lightgray}$\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
      \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ n \\
-         Since both candidates violate {\sc Ident(SonAngle)}$<$n, $\mathcal{M}$ determines output.
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$n &$ \mathcal{M}$  \\[0.5ex]
+         Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
 \hline \hline g. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$  & \\
-\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$ \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-Because we have assumed that all other {\sc Ident(SonAngle)}$<$n constraints rank low, certainly below $\mathcal{M}$, the degree to which candidates (g) and (h) violate {\sc Ident(SonAngle)}$<$n is irrelevant --- the distinction between clusters with {\sc Sonority Angles} above $n$ has been conflated.
+\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+Because we have assumed that all other {\sc Ident(Son$\measuredangle$)}$<$n constraints rank low, certainly below $\mathcal{M}$, the degree to which candidates (g) and (h) violate {\sc Ident(Son$\measuredangle$)}$<$n is irrelevant --- the distinction between clusters with {\sc Sonority Angles} above $n$ has been conflated.
 Even if {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3}) exceeds {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}), the outcome is determined by the markedness constraint $\mathcal{M}$.
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Ident(SonAngle)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Ident(Son$\measuredangle$)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
 \hline \hline a. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} &  2.0 $\ast$!  & \cellcolor{lightgray} 2.0 $\ast$ & \cellcolor{lightgray} \\
@@
 
-Under a universal ranking of {\sc Ident(SonAngle)}$<$n constraints, [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] would win in this scenario.
-In an equivalent scenario under free-ranking, where {\sc Ident(SonAngle)}$<$1.5 is the least stringent constraint to outrank $\mathcal{M}$, which in turn outranks all more stringent {\sc Ident(SonAngle)}$<$n constraints, the [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] candidate would win instead.
+Under a universal ranking of {\sc Ident(Son$\measuredangle$)}$<$n constraints, [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] would win in this scenario.
+In an equivalent scenario under free ranking, where {\sc Ident(Son$\measuredangle$)}$<$1.5 is the least stringent constraint to outrank $\mathcal{M}$, which in turn outranks all more stringent {\sc Ident(Son$\measuredangle$)}$<$n constraints, the [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] candidate would win instead.
 There would be conflation of all clusters with {\sc Sonority Angles} below $n$, but distinctions between clusters with {\sc Sonority Angles} would still be relevant.
 
-The example of Chaha will show that free-ranking is necessary, as conflation is observed on both sides of $n$, where {\sc Ident(SonAngle)}$<$n is the most stringent constraint to outrank $\mathcal{M}$.
+The example of Chaha will show that free ranking is necessary, as conflation is observed on both sides of $n$, where {\sc Ident(Son$\measuredangle$)}$<$n is the most stringent constraint to outrank $\mathcal{M}$.
 
@@
 
-As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<$n, defined similarly to {\sc Ident(SonAngle)}$<$n.
+As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<$n, defined similarly to {\sc Ident(Son$\measuredangle$)}$<$n.
 
@@
 The fact that this process of epenthesis does not target obstruent-initial clusters is not problematic under the sonority contour faithfulness approach,
-as the {\sc Ident(SonAngle)} constraints limit epenthesis, rather than trigger it.  By choosing a more limited markedness constraint such as {\sc *Son-C},
+as the {\sc Ident(Son$\measuredangle$)} constraints limit epenthesis, rather than trigger it.  By choosing a more limited markedness constraint such as {\sc *Son-C},
 defined below, we can have epenthesis act only on sonorant-initial clusters.
@@
 Undominated {\sc *ComplexOnset} accounts for the non-existence of initial clusters.
-{\sc *Coda} is ranked low, and therefore medial clusters are left intact.{\sc *ComplexCoda}, dominated by an {\sc Ident(SonAngle)} constraint, explains why some coda clusters are broken up by epenthesis while others are not.
+{\sc *Coda} is ranked low, and therefore medial clusters are left intact.{\sc *ComplexCoda}, dominated by an {\sc Ident(Son$\measuredangle$)} constraint, explains why some coda clusters are broken up by epenthesis while others are not.
 
@@
 
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc *ComplexCoda}
-
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{k1tf}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc *ComplexCoda}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{k1tf}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
 \hline \hline a. & & \textipa{k1tf} & & $\ast$! \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
 \hline \hline c. &  \ding{43} & \textipa{k1rm} & & $\ast$ \\
@@
 
-\ex. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda}
-
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc *ComplexCoda} \\[0.5ex]
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.9 $\gg$ {\sc *ComplexCoda}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc *ComplexCoda} \\[0.5ex]
 \hline \hline a. &   & \textipa{k1rm} & & $\ast$! \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{s1gd}/} & {\sc Dep}(+son) & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{s1gd}/} & {\sc Dep}(+son) & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{s1gd} & & & \cellcolor{lightgray}$\ast$ \\
@@
 
-To summarise, coda epenthesis behaviour in Chaha can be explained by the ranking of a {\sc Ident(SonAngle)}$<$n constraint above the markedness constraint triggering epenthesis, {\sc *ComplexCoda}.
+To summarise, coda epenthesis behaviour in Chaha can be explained by the ranking of a {\sc Ident(Son$\measuredangle$)}$<$n constraint above the markedness constraint triggering epenthesis, {\sc *ComplexCoda}.
 The evidence of the epenthetic behaviour of Chaha coda clusters accords with the {\sc Sonority Angle} prediction that RN should be the most likely to epenthesise out of the falling sonority clusters.
@@
 \ex. Rankings for the four idiolects:
-     \a. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}(+son)
-     \b. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}(+son)
-     \c. {\sc Ident(SonAngle)}$<$1.5, {\sc Dep}(+son) $\gg$ {\sc *ComplexCoda}
-     \c. {\sc Ident(SonAngle)}$<$1.9, {\sc Dep}(+son) $\gg$ {\sc *ComplexCoda}
+     \a. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}(+son)
+     \b. {\sc Ident(Son$\measuredangle$)}$<$1.9 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}(+son)
+     \c. {\sc Ident(Son$\measuredangle$)}$<$1.5, {\sc Dep}(+son) $\gg$ {\sc *ComplexCoda}
+     \c. {\sc Ident(Son$\measuredangle$)}$<$1.9, {\sc Dep}(+son) $\gg$ {\sc *ComplexCoda}
 
@@
 
-The ranking {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}, with all other {\sc Ident(SonAngle)}$<$n constraints being ranked lower than markedness, is responsible for the epenthetic positioning behaviour of this idiolect, as illustrated in the following tableaux.
-
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}
+The ranking {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Align-Left}, with all other {\sc Ident(Son$\measuredangle$)}$<$n constraints being ranked lower than markedness, is responsible for the epenthetic positioning behaviour of this idiolect, as illustrated in the following tableaux.
+
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Align-Left}
      \a. Fall-\{Rise, Plateau\}
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{j@wz1fo} & 1.33 & \cellcolor{lightgray} \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline c. & \ding{43} & \textipa{j@gd1fo} & 1.37 & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline e. & \ding{43} & \textipa{jams1to} & 2.11 $\ast$ & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline g. & & \textipa{j@kfito} & 2.11 $\ast$!  & \cellcolor{lightgray} \\
@@
 {\sc SonAngle}(m,s), at 2.03, is smaller than {\sc SonAngle}(s,t), at 2.11, yet epenthesis occurs on the right, creating the larger {\sc Sonority Angle}.
-This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(SonAngle)}$<$1.5.
-This is possible because I have adopted the position that the {\sc Ident(SonAngle)}$<$n constraints can be freely ranked.
-
-Adopting the converse strategy --- that {\sc Ident(SonAngle)}$<$n constraints have a universal ranking --- would not predict [\textipa{ms1t}]. Instead we would have the following situation:
+This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(Son$\measuredangle$)}$<$1.5.
+This is possible because I have adopted the position that the {\sc Ident(Son$\measuredangle$)}$<$n constraints can be freely ranked.
+
+Adopting the converse strategy --- that {\sc Ident(Son$\measuredangle$)}$<$n constraints have a universal ranking --- would not predict [\textipa{ms1t}]. Instead we would have the following situation:
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$2.1 & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(Son$\measuredangle$)}$<$2.1 & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a.  &\frownie & \textipa{jams1to} & 2.11 $\ast$! & \cellcolor{lightgray}2.11 $\ast$ & \cellcolor{lightgray} \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & & \textipa{j@krimo} & 1.89 $\ast$! &  \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{j@krimo} & 1.89 & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & \frownie & \textipa{j@rmido} & 2.36 $\ast$! & \cellcolor{lightgray} \\
@@
 
-\ex. {\sc Jussive-R} $\gg$ {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc Align-Left}
+\ex. {\sc Jussive-R} $\gg$ {\sc Ident(Son$\measuredangle$)}$<$1.9 $\gg$ {\sc Align-Left}
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Jussive-R} & {\sc Ident(SonAngle)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Jussive-R} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{j@rmido} & & \cellcolor{lightgray}2.36 $\ast$ & \cellcolor{lightgray} \\
@@
 
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-Left Root} \label{CCiCidiolectranking}
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Anchor-Left Root} \label{CCiCidiolectranking}
      \a. Fall-\{Rise, Plateau\}
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{j@wz1fo} & 1.33 & \cellcolor{lightgray}$\ast$ \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-gdf-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
 \hline \hline c. & & \textipa{j@gd1fo} & 1.37 & $\ast$! \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
 \hline \hline e. & & \textipa{jams1to} & 2.11 $\ast$! & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
 \hline \hline g. & & \textipa{j@kf1to} & 2.11 $\ast$!  & \cellcolor{lightgray}$\ast$ \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Root} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Root} \\[0.5ex]
 \hline \hline a. & \frownie & \textipa{j@w1zfo} & 2.03 $\ast$! & \cellcolor{lightgray} \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-sgd-o}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-L Root} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-sgd-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Root} \\[0.5ex]
 \hline \hline c. & \frownie & \textipa{j@s1gdo} & 2.11 $\ast$! & \cellcolor{lightgray} \\
@@
 
-\ex. {\sc Ident(SonAngle)}$<$1.0 $\gg$ {\sc Anchor-L-Root}
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.0 $\gg$ {\sc Anchor-L-Root}
      \a. \begin{center} \renewcommand*\arraystretch{1.2}
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(SonAngle)}$<$1.0 & {\sc Anchor-L Root} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-wzf-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.0 & {\sc Anchor-L Root} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{j@w1zfo} & 2.03 $\ast$ & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-sgd-o}/} & {\sc Ident(SonAngle)}$<$1.0 & {\sc Anchor-L Root} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-sgd-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.0 & {\sc Anchor-L Root} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{j@s1gdo} & 2.11 $\ast$ & \\
@@
 
-In summary, we were able to explain all four CCC idiolects of Chaha by ranking different {\sc Ident(SonAngle)}$<$n constraints higher than either {\sc Align-Left} or {\sc Anchor-Left Root}.
+In summary, we were able to explain all four CCC idiolects of Chaha by ranking different {\sc Ident(Son$\measuredangle$)}$<$n constraints higher than either {\sc Align-Left} or {\sc Anchor-Left Root}.
 
@@
 
-Solutions such as [C\textipa{1}C\textipa{1}CC] and [CC\textipa{1}C\textipa{1}C] are also excluded, as these incur unnecessary violations of {\sc Ident(SonAngle)} and {\sc Dep}.
+Solutions such as [C\textipa{1}C\textipa{1}CC] and [CC\textipa{1}C\textipa{1}C] are also excluded, as these incur unnecessary violations of {\sc Ident(Son$\measuredangle$)} and {\sc Dep}.
 If the middle two consonants C\textsubscript{2} and C\textsubscript{3} are split up by an epenthetic vowel, there is no further need for epenthesis as *CCC is already satisfied by [CC\textipa{1}CC].
@@
 
-Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n.
+Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n.
 Illustrative tableaux are shown below for n=1.5:
 
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Align-Left}
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Align-Left}
      \a. Case 1: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$<$1.5
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-gdf-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-gdf-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{n1gd1fn@} & 0.59 & \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{n1sr1Bn@} & 1.57 $\ast$ &  \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-dmd-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-dmd-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
 \hline \hline a. &  & \textipa{n1dm1dn@} & 2.3 $\ast$!   & \cellcolor{lightgray} \\
@@
 
-Given the general form of the ranking {\sc Ident(SonAngle)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C].
+Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C].
 This preference is overridden when at least one of {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are greater than n and {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) is less than n.
 
-\ex. {\sc Ident(SonAngle)}$<$1.5 $\gg$ {\sc Anchor-Left Rt}
+\ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Anchor-Left Rt}
      \a. Case 1: Both {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) and {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})$<$1.5
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-gdf-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-gdf-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
 \hline \hline a. &  & \textipa{n1gd1fn@} & 0.59 & $\ast$!\\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
 \hline \hline a. &  & \textipa{n1sr1Bn@} & 1.57 $\ast$ & $\ast$! \\
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-sdB-n@}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-sdB-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{n1sd1Bn@} & 0.18 & \cellcolor{lightgray} $\ast$ \\
@@
 
-In this case study, I presented an alternative analysis of Chaha epenthetic positioning to \citet{rose.2000}'s Syllable Contact-based analysis, in which sonority profiles affected epenthesis via the mechanism of sonority-based faithfulness constraints {\sc Ident(SonAngle)}$<$n rather than sonority-based markedness constraints such as Syllable Contact and Sonority Sequencing.
+In this case study, I presented an alternative analysis of Chaha epenthetic positioning to \citet{rose.2000}'s Syllable Contact-based analysis, in which sonority profiles affected epenthesis via the mechanism of sonority-based faithfulness constraints {\sc Ident(Son$\measuredangle$)}$<$n rather than sonority-based markedness constraints such as Syllable Contact and Sonority Sequencing.
 The fact that general constraints on syllable structure such as *CCC and {\sc *ComplexCoda} drove epenthesis eliminated the need for constraints forbidding too much epenthesis, as Rose does in the form of the constraint {\sc *MedialLight}.
@@
 
-In the final tally, the {\sc Sonority Angle}-based approach fares worse on one datapoint and uses approximately the same number of constraints, but manages to accomplish most of the work of the analysis with the only crucial ranking being the placement of a single {\sc Ident(SonAngle)}$<$n constraint with respect to a relevant $\mathcal{M}$ constraint, while in Rose's analysis this work is spread over a number of different sonority-related constraints.
+In the final tally, the {\sc Sonority Angle}-based approach fares worse on one datapoint and uses approximately the same number of constraints, but manages to accomplish most of the work of the analysis with the only crucial ranking being the placement of a single {\sc Ident(Son$\measuredangle$)}$<$n constraint with respect to a relevant $\mathcal{M}$ constraint, while in Rose's analysis this work is spread over a number of different sonority-related constraints.
 
@@
 
-\noindent{\bf Consonant deletion.} The current formulation of {\sc Ident(SonAngle)}$<$n constraints restricts its application to when the consonants of a C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} sequence stand in correspondence.
+\noindent{\bf Consonant deletion.} The current formulation of {\sc Ident(Son$\measuredangle$)}$<$n constraints restricts its application to when the consonants of a C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} sequence stand in correspondence.
 However, another formulation is possible, in which sonority contours are a property of C\textsubscript{1} rather than a property of the whole contour.\footnote{Thanks to Adam Albright for this suggestion.}

### 2013-09-30 paper.tex
Added numbers to SonRise, and added more detailed comparison of SonAngle vs SonRise

@@
 
-\ex. Desiderata for a sonority contour similarity metric \label{desiderata}
-     \a. The more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost.
-     \b. For a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the smaller the faithfulness cost.
+\ex. Desiderata for a sonority contour faithfulness metric \label{desiderata}
+     \a. The more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost. \label{desideratum_a}
+     \b.
+For a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the smaller the faithfulness cost.
+\label{desideratum_b}
 
@@
 \vspace{-3em}
-\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressed}}
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressednumbers}}
 
@@
 
-\ex.    \begin{center}
+\ex. Sample calculations of {\sc SonRise}
+   \begin{center}
     \begin{tabular}{c c | c c | c}
@@
 \vspace{-3em}
-\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityrisehierarchycompressed}}
-
-Observe that of the two desiderata for such a metric, {\sc Sonority Rise} fulfills the first but not the second.
-Consider the falling sonority clusters.
-RN, NF and FT, which all have a sonority distance of -1, have a smaller {\sc Sonority Rise} than NT and RF, with a sonority distance of 2, followed by RT with a sonority distance of 3.
-
-However, of the three, RN has the largest {\sc Sonority Rise}, and therefore is expected to be more resistant to epenthesis than NF and FT.
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityrisehierarchycompressednumbers}}
+
+Observe that of the two desiderata for sonority contour metrics outlined in \ref{desiderata}, {\sc Sonority Rise} fulfills the first but not the second.
+Holding C\textsubscript{1} constant, closing the sonority gap with C\textsubscript{2} does result in a smaller {\sc SonRise} --- compare RT, RF and RN, for example.
+
+However, out of the three clusters with a sonority distance of -1, RN has the largest {\sc Sonority Rise}, and therefore is expected to be more resistant to epenthesis than NF and FT.
+This is contrary to criterion \ref{desideratum_b}.
 If RN undergoes epenthesis, therefore, we predict FT and NF to do the same.
@@
 
+Let us do a more detailed comparison of the two cluster hierarchies:
+
+\ex. Detailed comparison of {\sc Sonority Rise} vs {\sc Sonority Angle} hierarchies:
+
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressed}}
+
+\vspace{-2em}
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityrisehierarchycompressed}}
+
+Within the rising sonority clusters, the predictions of the two hierarchies are identical.
+The differences in predictions are as follows:
+
+\ex.
+\a.
+More sonorous plateaus are more likely to undergo epenthesis under the {\sc Sonority Angle} metric, whereas all the level clusters should have equal likelihood of being broken up by epenthesis.
+     \b. RN is more likely to undergo epenthesis than NF under {\sc Sonority Angle}, and vice versa under {\sc Sonority Rise}.
+     \b. RN is more likely to undergo epenthesis than FT under {\sc Sonority Angle}, and vice versa under {\sc Sonority Rise}.
+     \b. NF is more likely to undergo epenthesis than FT under {\sc Sonority Angle}, and vice versa under {\sc Sonority Rise}.
+     \b. RF is more likely to undergo epenthesis than RT under {\sc Sonority Angle}, and vice versa under {\sc Sonority Rise}.
+     \b. RF is more likely to undergo epenthesis than NT under {\sc Sonority Angle}, and vice versa under {\sc Sonority Rise}.
+     \b. RT and NT are equally likely to undergo epenthesis under {\sc Sonority Angle}, but NT is more likely to undergo epenthesis than RF under {\sc Sonority Rise}.
+
 \subsection{Another dimension of sonority contour faithfulness} \label{depson}
@@
 I will formalise this restriction with the constraint {\sc Dep}(+sonorant).
+
+\ex. {\sc Dep}(+sonorant): do not insert a sonorant region between two obstruents.
+
 The epenthesis of a vowel between two obstruents, which bear the feature [$-$sonorant], necessitates the insertion of a new [+sonorant] feature, whereas when a vowel is epenthesised adjacent to a sonorant, the sonorant's [+sonorant] feature spreads and is shared between the vowel and the sonorant.
 
-This constraint will be used in the analysis of Chaha complex coda epenthesis, which in some idiolects
-cannot occur between obstruents, while in others, it can. My proposal will be that in the former, {\sc Dep}(+sonorant) is higher-ranked, thus blocking epenthesis.
+This constraint will be used in the analysis of Chaha complex coda epenthesis, which in some idiolects cannot occur between obstruents, while in others, it can.
+My proposal will be that in the former, {\sc Dep}(+sonorant) is higher-ranked, thus blocking epenthesis.
 

### 2013-09-30 paper.tex
Converted Irish examples to textipa, added conclusion to machinery section

@@
 
-\ex. Detailed comparison of {\sc Sonority Rise} vs {\sc Sonority Angle} hierarchies:
+\ex. Detailed comparison of {\sc Sonority Angle} vs {\sc Sonority Rise} hierarchies:
 
@@
 
-Syllable Contact applies only across syllable boundaries.
-Therefore, when sonority-driven epenthesis occurs in onsets or codas, other sonority-based markedness constraints must be employed.
+Compared with the cluster hierarchy predicted by {\sc Sonority Angle}, we again see several differences.
+
+\ex. {\sc Sonority Angle} hierarchy, repeated for purposes of comparison:
+
+\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressed}}
+
+I will not enumerate all the differences in predictions, but notice two crucial distinctions: the {\sc Dis}-based Syllable Contact hierarchy predicts equal susceptibility to epenthesis of all the clusters with a {\sc Dis} of +1 (RN, NF and FT), and thus it does not distinguish RN from the remainder of the falling sonority clusters.
+In addition, if NT and RT fail to undergo epenthesis, this predicts that RF should not undergo epenthesis either.
+Both of these are contrary to the empirical evidence of Chaha and Irish.
+
+\bigskip
+
+Another difference between the markedness-based account and the sonority contour faithfulness approach is that Syllable Contact applies only across syllable boundaries, while the {\sc Ident(Son$\measuredangle$)}$<$n constraints are agnostic with regard to syllable structure.
+When sonority-driven epenthesis occurs elsewhere, for example in codas, other sonority-based markedness constraints must be employed.
 One such is Sonority Sequencing \citep{selkirk.1984}, which states that sonority must be strictly increasing in the onset and strictly decreasing in the coda.
-\citep{rose.2000} uses two variants of this constraint, one strict and one non-strict, in her analysis of Chaha.
+In both the Irish and Chaha cases, we see sonority-driven epenthesis occurring both in heterosyllabic and coda cluster contexts, and we will see that adopting the family of {\sc Ident(Son$\measuredangle$}$<$n constraints economises on the number of constraints we need to refer to sonority.
+
+\bigskip
+
+In this section, I have introduced all the necessary machinery to analyse cases of sonority-driven epenthesis in Irish and Chaha, as well as to understand the competing analyses.
+We now proceed to the case study of Irish.
 
@@
 
-\ex. \a. /alb\textipa{@}/ $\rightarrow$ [al\textipa{@b@}] \\
+\ex. \a. /\textipa{alb@}/ $\rightarrow$ [\textipa{al@b@}] \\
          {\it Alba} `Scotland'
-     \b. /dorx\textipa{@}/ $\rightarrow$ [dor\textipa{@x@}] \\
+     \b. /\textipa{dorx@}/ $\rightarrow$ [\textipa{dor@x@}] \\
          {\it dorcha} `dark'
-     \b. /gorm/  $\rightarrow$  [gor\textipa{@}m] \\
+     \b. /\textipa{gorm}/  $\rightarrow$  [\textipa{gor@m}] \\
          {\it gorm} `blue'
-     \b. /banb\textipa{@}/ $\rightarrow$ [ban\textipa{@b@}] \\
+     \b. /\textipa{banb@}/ $\rightarrow$ [\textipa{ban@b@}] \\
          {\it Banba} `a name for Ireland'
-     \b. /kon\textipa{f@}/ $\rightarrow$ [kon\textipa{@f@}] \\
+     \b. /\textipa{konf@}/ $\rightarrow$ [\textipa{kon@f@}] \\
          {\it confadh} `anger'
-     \b. /an\textsuperscript{j}m\textsuperscript{j}/ $\rightarrow$ [an\textsuperscript{j}im\textsuperscript{j}] \\
+     \b. /\textipa{an\textsuperscript{j}m\textsuperscript{j}}/ $\rightarrow$ [\textipa{an\textsuperscript{j}im\textsuperscript{j}}] \\
          {\it ainm} `name'
@@
 
-\ex. \a. /farno\textipa{:g}/ $\rightarrow$ [farno\textipa{:g}], *[far\textipa{@}no\textipa{:g}] \\
+\ex. \a. /\textipa{farno:g}/ $\rightarrow$ [\textipa{farno:g}], *[\textipa{far@no:g}] \\
          {\it fearnog} `alder'
-     \b. /bord/ $\rightarrow$ [bord], *[bor\textipa{@}d] \\
+     \b. /\textipa{bord}/ $\rightarrow$ [\textipa{bord}], *[\textipa{bor@d}] \\
          {\it bord} `table'
-     \b. /kalr\textipa{@}/ $\rightarrow$ [kalr\textipa{@}], *[kal\textipa{@r@}] \\
+     \b. /\textipa{kalr@}/ $\rightarrow$ [\textipa{kalr@}], *[\textipa{kal@r@}] \\
          {\it calra} `calorie'  
@@
 
-\ex. \a. /kork/ $\rightarrow$ [kork], *[kor\textipa{@}k] \\
+\ex. \a. /\textipa{kork}/ $\rightarrow$ [\textipa{kork}], *[\textipa{kor@k}] \\
          {\it Cork} `Cork (place name)' 
-     \b. /kork\textipa{@}/ $\rightarrow$ [kork\textipa{@}], *[kor\textipa{@k@}] \\
+     \b. /\textipa{kork@}/ $\rightarrow$ [\textipa{kork@}], *[\textipa{kor@k@}] \\
          {\it corca} `people' 
-     \b. /korp/  $\rightarrow$ [korp], *[kor\textipa{@p}] \\
+     \b. /\textipa{korp}/  $\rightarrow$ [\textipa{korp}], *[\textipa{kor@p}] \\
          {\it corp} `body' 

### 2013-09-30 paper.tex
All edits to Irish -- DONE

@@
 
-\ex. Ident(SonAngle)$<$1.5 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}
+\ex. Ident(Son$\measuredangle$)$<$1.5 $\gg$ {\sc *ComplexCoda} $\gg$ {\sc Dep}
      \a. Allows epenthesis in rising and level clusters such as stop-fricative TF:
@@
 
+This constraint does not duplicate the work of the {\sc Ident(Son$\measuredangle$)}$<$n constraints, but eliminates the obstruent-initial clusters from consideration, as these are not targeted for epenthesis by any high-ranking constraints.
+
 \ex. {\sc *Son-C} $\gg$ {\sc Dep}
@@
 
-\ex. {\sc Sonority Angles} of sonorant-initial clusters using revised sonority scale
+\ex. {\sc Sonority Angles} of sonorant-initial clusters using revised sonority scale \label{sonorantinitial_sonangle}
 
@@
 
+        \node (RT) at (2.48619449019234 * 15, 0.7) {RT};% 2.35619449019234 - repositioning for visual clarity
         \node (NT) at (2.48619449019234 * 15, 0) {NT}; % 2.35619449019234 - repositioning for visual clarity
+        \node[font=\footnotesize,opacity=0.7] (NTno) at (2.48619449019234 * 15, 1.5) {2.36};
+        \node (RD) at (2.37743866747662 * 15, 0) {RD}; % 2.29743866747662 
+        \node[font=\footnotesize,opacity=0.7] (RDno) at (2.37743866747662 * 15, 1.5) {2.30};
         \node (ND) at (2.28183949564558 * 15, 0) {ND}; % 2.23183949564558 
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (2.28183949564558 * 15, 1.5) {2.23};
+        \node (RF) at (2.19429743558818 * 15, 0) {RF}; % 2.21429743558818 
+        \node[font=\footnotesize,opacity=0.7] (RFno) at (2.19429743558818 * 15, 1.5) {2.21};
         \node (NF) at (2.03444393579570 * 15, 0) {NF};
+        \node[font=\footnotesize,opacity=0.7] (NFno) at (2.03444393579570 * 15, 1.5) {2.03};
+        \node (RN) at (1.89254688119154 * 15, 0) {RN};
+        \node[font=\footnotesize,opacity=0.7] (RNno) at (1.89254688119154 * 15, 1.5) {1.89};
         \node (NN) at (1.24904577239825 * 15, 0) {NN};
+        \node[font=\footnotesize,opacity=0.7] (NNno) at (1.24904577239825 * 15, 1.5) {1.25};
+        \node (RR) at (1.10714871779409 * 15, 0) {RR};
+        \node[font=\footnotesize,opacity=0.7] (RRno) at (1.10714871779409 * 15, 1.5) {1.11};
         \node (NR) at (0.60 * 15, 0) {NR}; % 0.4636476090008
-
-        \node (RT) at (2.48619449019234 * 15, 0.7) {RT};% 2.35619449019234 - repositioning for visual clarity
-        \node (RD) at (2.37743866747662 * 15, 0) {RD}; % 2.29743866747662 
-        \node (RF) at (2.19429743558818 * 15, 0) {RF}; % 2.21429743558818 
-        \node (RN) at (1.89254688119154 * 15, 0) {RN};
-        \node (RR) at (1.10714871779409 * 15, 0) {RR};
+        \node[font=\footnotesize,opacity=0.7] (NRno) at (0.60 * 15, 1.5) {0.46};
 
@@
 
-  \node (2pointlabel) at (2.43 * 15,-1.7) {2.3};
+  \node (2pointlabel) at (2.43 * 15,-1.7) {2.33};
 
@@
 
-\ex. {\sc Ident(SonAngle)$<$2.3} $\gg$ {\sc *Son-C} $\gg$ {\sc Ident(SonAngle)$<$2.4}
+\ex. {\sc Ident(Son$\measuredangle$)$<$2.33} $\gg$ {\sc *Son-C} $\gg$ {\sc Ident(Son$\measuredangle$)$<$2.4}
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{kork}/} & {\sc Ident(SonAngle)$<$2.3} & {\sc *Son-C} & {\sc Ident(SonAngle)$<$2.4} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{kork}/} & {\sc Ident(Son$\measuredangle$)$<$2.33} & {\sc *Son-C} & {\sc Ident(Son$\measuredangle$)$<$2.4} \\[0.5ex]
 \hline \hline a. & \ding{43} & \textipa{kork} & & \cellcolor{lightgray}$\ast$ & \cellcolor{lightgray} \\
-\hline b. & & \textipa{kor@k} & 2.35 $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray}2.35 $\ast$ \\
+\hline b. & & \textipa{kor@k} & 2.36 $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray}2.36 $\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{alb@}/} & {\sc Ident(SonAngle)$<$2.3} & {\sc *Son-C} & {\sc Ident(SonAngle)$<$2.4} \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{alb@}/} & {\sc Ident(Son$\measuredangle$)$<$2.33} & {\sc *Son-C} & {\sc Ident(Son$\measuredangle$)$<$2.4} \\[0.5ex]
 \hline \hline c. & \ding{43} & \textipa{al@b@} & 2.29 & & \cellcolor{lightgray} 2.29 \\
@@
 
-Using the same revised sonority scale, the {\sc Sonority Rise} calculations are as follows for the relevant clusters:
+An analysis based on {\sc Sonority Rise} \citep{flemming.2008} would be largely identical, but the cluster hierarchy would differ:
 
@@
 
-        \node (NT) at (1.66666666666667 * 15, 0) {NT}; 
+        \node[draw,circle,dashed] (NT) at (1.66666666666667 * 15, 0) {NT}; 
+        \node[font=\footnotesize,opacity=0.7] (NTno) at (1.66666666666667  * 15, 1.5) {1.67};
         \node (ND) at (1.5 * 15, 0) {ND}; 
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (1.5 * 15, 1.5) {1.5};
         \node (NF) at (1.33333333333333 * 15, 0) {NF};
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (1.33 * 15, 1.5) {1.33};
         \node (NN) at (1 * 15, 0) {NN};
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (1 * 15, 1.5) {1.0};
         \node (NR) at (0.666666666666667 * 15, 0) {NR}; 
-
-        \node (RT) at (2.5 * 15, 0) {RT};
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (0.666666666666667* 15, 1.5) {0.67};
+
+        \node[draw,circle,dashed] (RT) at (2.5 * 15, 0) {RT};
+        \node[font=\footnotesize,opacity=0.7] (RTno) at (2.5 * 15, 1.5) {2.5};
         \node (RD) at (2.25 * 15, 0) {RD}; 
+        \node[font=\footnotesize,opacity=0.7] (RDno) at (2.25 * 15, 1.5) {2.25};
         \node (RF) at (2 * 15, 0) {RF}; 
+        \node[font=\footnotesize,opacity=0.7] (RFno) at (2 * 15, 1.5) {2.0};
         \node (RN) at (1.5 * 15, 0.7) {RN};
@@
 
-    \node (axisstart) at (0.5 * 15,-1) {};
-    \node (axisend)   at (2.6 * 15,-1) {};
+    \node (axisstart) at (0.5 * 15,-1.5) {};
+    \node (axisend)   at (2.6 * 15,-1.5) {};
     \draw (axisstart) -- (axisend);
-   \node (xaxislabel) at (2.6 * 15,-1.5) {\textsc{Sonority Rise}};
+   \node (xaxislabel) at (2.6 * 15,-2.0) {\textsc{Sonority Rise}};
 
@@
 
-Note that the clusters RF and RD fall between RT and NT on this scale.  Therefore, we cannot clearly separate the clusters that undergo epenthesis
-from the ones that do not if we adopt {\sc Sonority Rise} as the relevant metric.
-
-\bigskip
-
-Carnie's (1994) analysis of these facts is in terms of a Minimal Distancing Constraint with various parameter settings, such as for which direction away from the nucleus it applies (to the right in the Irish case, to account for epenthesis applying to both codas and heterosyllabic clusters).
+Note that the clusters RF and RD fall between RT and NT on this scale.
+Therefore, we cannot separate the clusters that undergo epenthesis from the ones that do not if we adopt {\sc Sonority Rise} as the relevant metric, as we can when we adopt {\sc Sonority Angle} (c.f.
+\ref{sonorantinitial_sonangle}).
+
+\bigskip
+
+%Carnie's (1994) analysis of these facts is in terms of a Minimal Distancing Constraint with various parameter settings, such as for which direction away from the nucleus it applies (to the right in the Irish case, to account for epenthesis applying to both codas and heterosyllabic clusters).
 His preliminary analysis has distance computed according to the following sonority scale:
-
-\ex. \label{carniesonorityscale} \a. 1 - Voiceless stops
-     \b. 2 - Voiced stops
-     \b. 3 - Voiceless fricatives
-     \b. 4 - Voiced fricatives
-     \b. 5 - Sonorants
-
-with a subsequent revision where sonority is computed in terms of the number of nodes that have to be specified to obtain the appropriate manner specification.
+%
+%\ex. \label{carniesonorityscale} \a. 1 - Voiceless stops
+%     \b. 2 - Voiced stops
+%     \b. 3 - Voiceless fricatives
+%     \b. 4 - Voiced fricatives
+%     \b. 5 - Sonorants
+%
+%with a subsequent revision where sonority is computed in terms of the number of nodes that have to be specified to obtain the appropriate manner specification.
 This computation is somewhat complicated, so I will not reproduce it here.
@@
 Voiceless stops have no specified nodes, so sonorant-voiceless stop clusters have a sonority distance of 1, which is the minimal distance tolerated.
-
-A sonority scale that gives nasals and liquids identical sonority values seems unlikely given measurable differences in the phonetic correlates of sonority such as intensity between liquids and nasals \citep{parker.2002}.
+%
+%A sonority scale that gives nasals and liquids identical sonority values seems unlikely given measurable differences in the phonetic correlates of sonority such as intensity between liquids and nasals \citep{parker.2002}.
 This is especially so when the obstruents are spread so widely on the sonority scale.
-I will therefore explore instead an alternative sonority distance-based analysis using Syllable Contact.
-
-\bigskip
-
-We quickly see that Syllable Contact on its own is insufficient as epenthesis in Irish also affects coda clusters. We will need to invoke Sonority Sequencing.
+%I will therefore explore instead an alternative sonority distance-based analysis using Syllable Contact.
+
+Now let us construct a markedness-based analysis for the Irish data.\footnote{\cite{carnie.1994} analyses these facts with a Minimal Distancing Constraint, based on a feature-geometric notion of sonority distance.
+The analysis presented here adheres more closely to the phonetic interpretation of sonority (see, for example, \cite{parker.2002}.}
 
@@
 
-Suppose we define a single markedness constraint that favours all falling sonority clusters regardless of their position in the syllable, i.e.
+Suppose then that we define a single markedness constraint that favours all falling sonority clusters regardless of their position in the syllable, i.e.
 combining Syllable Contact and Sonority Sequencing.
 We require a finer-grained metric to measure how marked a particular cluster is.
-An obvious course of action is to use \citet{gouskova.2002}'s {\sc *Dis} metric, extending its use from the heterosyllabic environment alone to all positions.
+An obvious course of action is to use \citet{gouskova.2002}'s {\sc Dis} metric, extending its use from the heterosyllabic environment alone to all positions.
 
 Using the defined sonority scale, we expect the following markedness hierarchy of sonorant-initial clusters.
+
+\ex. {\sc Dis} values of sonorant-initial clusters using revised sonority scale
 
@@
 
-        \node (NT) at (2 * 5, 0) {NT}; 
+        \node[draw,circle,dashed] (NT) at (2 * 5, 0) {NT}; 
+        \node[font=\footnotesize,opacity=0.7] (RTno) at (2 * 5, 2.5) {2};
         \node (ND) at (1.5 * 5, 0) {ND}; 
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (1.5 * 5, 2.5) {1.5};
         \node (NF) at (1 * 5, 0) {NF};
+        \node[font=\footnotesize,opacity=0.7] (NFno) at (1 * 5, 2.5) {1};
         \node (NN) at (0 * 5, 0) {NN};
+        \node[font=\footnotesize,opacity=0.7] (NNno) at (0 * 5, 2.5) {0};
         \node (NR) at (-1 * 5, 0) {NR}; 
-
-        \node (RT) at (3 * 5, 0) {RT};
+        \node[font=\footnotesize,opacity=0.7] (NRno) at (-1 * 5, 2.5) {-1};
+
+        \node[draw,circle,dashed] (RT) at (3 * 5, 0) {RT};
+        \node[font=\footnotesize,opacity=0.7] (NDno) at (3 * 5, 2.5) {3};
         \node (RD) at (2.5 * 5, 0) {RD}; 
-        \node (RF) at (2 * 5, 0.7) {RF}; 
+        \node[font=\footnotesize,opacity=0.7] (RDno) at (2.5 * 5, 2.5) {2.5};
+        \node (RF) at (2 * 5, 1.5) {RF}; 
         \node (RN) at (1 * 5, 0.7) {RN};

### 2013-10-01 paper.tex
Resolved some formatting issues with brackets

@@
 \usepackage{amssymb} % for angle symbol
-
+\usepackage{longtable}
 \usepackage{amsfonts}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ n \\
+     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
          Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
@@
 
-\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\
+\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\
 
@@
   \ex. \label{idiolects} The four idiolects: \citep[(43)]{rose.2000}
-       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
+       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \citep{leslau.1964} \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
            [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
@@
 	\node (FT) at (2.11121582707*8, 0.5) {FT};
-	\node (bF) at (2.17308367293*8, 1) {bF};
+	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
 	\node (RF) at (2.21429743559*8, 1.5) {RF};
@@
 
-Proceeding to idiolect \ref{idiolectb}, we find that [r]-sonorant clusters are allowed word-finally.
+Proceeding to idiolect \ref{idiolectb}, we find that [r]-sonorant clusters are allowed to undergo epenthesis word-finally.
 Because {\sc Sonority Angle} permits a linear separation of the [r]-sonorant clusters from the remainder of the falling sonority clusters, this is straightforward to explain
@@
   \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
+  \path [line,dotted] (1.5 * 8,1.8) -- (1.91 * 8, 1.8);
 \end{tikzpicture}
@@
 
-{\sc Sonority Rise} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other, it is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}.
-This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters: if RN undergoes epenthesis, we expect that FT and NF should also, but FT never does.
+{\sc Sonority Rise} \citep{flemming.2008} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other.
+It is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}.
+This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters: if RN undergoes epenthesis, we expect that FT and NF should also do so, but FT never does.
+
+\ex. TODO
 
@@
   \node (TF) at (0.8*8,-0.5)   {TF};
-  \node (RN) at (1.5*8,0)   {RN};
+  \node[draw,circle,dashed] (RN) at (1.5*8,0)   {RN};
   \node (NN) at (1*8,0.5)     {NN};
@@
   \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
+  % dividing line
+  \node (dividinglinestart) at (1.15 * 8,1.5) {};
+  \node (dividinglineend)   at (1.15 * 8,-1.3) {};
+  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
 \end{tikzpicture}
@@
 
-\bigskip
+\ex. TODO
+
 \resizebox{\linewidth}{!}{
@@
   \tikzstyle{line} = [draw, -latex']
-  \node (RT) at (3*3,2.0)   {RT};
-  \node (NT) at (2*3,1.5)  {NT};
-  \node (FT) at (1*3,1.0)  {FT};
+  \node (RT) at (3*3,0.5)   {RT};
+  \node (NT) at (2*3,0.5)  {NT};
+  \node (FT) at (1*3,0.5)  {FT};
   \node (TT) at (0*3,0.5)     {TT};
-  \node (RF) at (2*3,2.0)     {RF};
-  \node (NF) at (1*3,1.5)  {NF};
+  \node (RF) at (2*3,1.0)     {RF};
+  \node (NF) at (1*3,1.0)  {NF};
   \node (FF) at (0*3,1.0)   {FF};
   \node (TF) at (-1*3,0.5)   {TF};
-  \node (RN) at (1*3,2.0)   {RN};
+  \node[circle,draw,dashed] (RN) at (1*3,2.0)   {RN};
   \node (NN) at (0*3,1.5)   {NN};
@@
   \node (xaxislabel) at (3.5*3,-0.5) {\textsc{Dis}};
+  % dividing line
+  \node (dividinglinestart) at (0.5 * 3,2.3) {};
+  \node (dividinglineend)   at (0.5 * 3,-0.3) {};
+  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
 \end{tikzpicture}
@@
 The advantage of doing so is that it avoids the difficulty of forbidding [\textipa{Bm}] clusters which we encountered above.
-On the other hand, the sonority contour faithfulness approach can get away without specifically mentioning [r] at all, by virtue of the ability of the {\sc Sonority Angle} hierarchy to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.
+On the other hand, the sonority contour faithfulness approach does not have to single out [r] for special treatment at all, by virtue of the ability of the {\sc Sonority Angle} hierarchy to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.
 
@@
 
-As with coda clusters, there is considerable inter- and intra-speaker variability in epenthetic positioning between idiolects.
-We begin with data from the main idiolect discussed in Section 4.3 of \citep{rose.2000}.
+As with coda clusters, there is considerable inter- and intra-speaker variability in epenthetic positioning.
 
@@
 Triconsonantal clusters must be broken up via epenthesis, indicating that {\sc *CCC} $\gg$ {\sc Dep}.
-If epenthesis occurs either between C\textsubscript{1}C\textsubscript{2} or between C\textsubscript{2}-C\textsubscript{3}, {\sc *CCC} will be satisfied.
+If epenthesis occurs either between C\textsubscript{1}C\textsubscript{2} or between C\textsubscript{2}C\textsubscript{3}, {\sc *CCC} will be satisfied.
 We do not need a separate constraint to prevent double epenthesis occurring to produce *[C\textipa{1}C\textipa{1}C].
+
+\ex. TODO
 
@@
 
-This holds for all the idiolects. Within each idiolect, we need only explain the location of epenthesis.
-
-There are four idiolects to be explained:
+This holds for all the ``idiolects'' reported in \citep{rose.2000}. Within each, we need only explain the location of epenthesis.
+
+There are four idiolects to be explained. Note that these do not appear to correlate systematically with the four coda cluster idiolects.
 
 \ex. \a. ``Default idiolect'', discussed in Section 4.3 of \citep{rose.2000}. \label{defaultCCCidiolect}
-           \a. [C\textipa{1}CC] iff C\textsubscript{1}C\textsubscript{2} is a fall and C\textsubscript{2}-C\textsubscript{3} is a rise or plateau.
+           \a. [C\textipa{1}CC] iff C\textsubscript{1}C\textsubscript{2} is a rise or plateau and C\textsubscript{2}C\textsubscript{3} is a fall.
            \b. [CC\textipa{1}C] otherwise.
@@
      \c. [C\textipa{1}CC] idiolect, discussed in Section 5.2.1 of \citep{rose.2000}. \label{C1CCidiolect}
-           \a. [CC\textipa{1}C] iff C\textsubscript{2}-C\textsubscript{3} is a fall and C\textsubscript{1}C\textsubscript{2} is a rise or plateau.
+           \a. [CC\textipa{1}C] iff C\textsubscript{2}C\textsubscript{3} is a fall and C\textsubscript{1}C\textsubscript{2} is a rise or plateau.
            \b. [C\textipa{1}CC] otherwise.
@@
 \noindent {\bf Default idiolect.} In the default idiolect \ref{defaultCCCidiolect}, epenthesis occurs between C\textsubscript{2} and C\textsubscript{3} to form [CC\textipa{1}C].
-Only when C\textsubscript{1}C\textsubscript{2} constitutes a sonority rise or plateau, and C\textsubscript{2}-C\textsubscript{3} constitutes a sonority fall, does epenthesis occur between C\textsubscript{1} and C\textsubscript{2} to form [C\textipa{1}CC].
+Only when C\textsubscript{1}C\textsubscript{2} constitutes a sonority rise or plateau, and C\textsubscript{2}C\textsubscript{3} constitutes a sonority fall, does epenthesis occur between C\textsubscript{1} and C\textsubscript{2} to form [C\textipa{1}CC].
 Forms and their associated sonority angles are shown in the table below.
@@
 
-\ex. Default idiolect
-
-\begin{tabular}{ccccc}
+\ex. Default idiolect \citep[(24,26,28,30,32)]{rose.2000} \label{defaultidiolectCCCforms}
+
+\begin{longtable}{ccccc}
 	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
@@
     A. & \textipa{j-t-k't'@k'@t'} & \textipa{j1tk'1t'@k'@t'} & 1.37 & 1.37 \\
-\end{tabular}
+\end{longtable}
 
@@
 The default preference in this idiolect is to epenthesise on the right, between C\textsubscript{2} and C\textsubscript{3}.
-I encode this preference with a markedness constraint borrowed from \citep{rose.2000}'s analysis:
+I encode this preference with a markedness constraint borrowed from \cite{rose.2000}'s analysis:
 
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-\textnormal{CCC}-o}/} & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & & \textipa{j@\textnormal{C}i\textnormal{CC}o} & 2,4!,5 \\
-\hline b. & \ding{43} & \textipa{j@\textnormal{CC}i\textnormal{C}o} & 2,3,5 \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-The only time that {\sc Align-Left} is overruled is when breaking up the C\textsubscript{2}-C\textsubscript{3} cluster would be too ``expensive'' in faithfulness terms --- when the cluster consists of a sonority fall --- and breaking up the C\textsubscript{1}C\textsubscript{2} cluster is comparatively cheap, that is, when C\textsubscript{1}C\textsubscript{2} is a sonority rise or plateau.
-In {\sc Sonority Angle} terms, {\sc Align-Left} is overruled only when breaking the C\textsubscript{2}-C\textsubscript{3} cluster would entail creating a {\sc Sonority Angle} greater than 1.5, when the alternative of breaking the C\textsubscript{1}C\textsubscript{2} cluster would create a {\sc Sonority Angle} smaller than 1.5.
+\hline \hline a. & & \textipa{j@\textnormal{C}1\textnormal{CC}o} & 2,4!,5 \\
+\hline b. & \ding{43} & \textipa{j@\textnormal{CC}1\textnormal{C}o} & 2,3,5 \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+The only time that {\sc Align-Left} is overruled is when breaking up the C\textsubscript{2}C\textsubscript{3} cluster would be too ``expensive'' in faithfulness terms --- when the cluster consists of a sonority fall --- and breaking up the C\textsubscript{1}C\textsubscript{2} cluster is comparatively cheap, that is, when C\textsubscript{1}C\textsubscript{2} is a sonority rise or plateau.
+In {\sc Sonority Angle} terms, {\sc Align-Left} is overruled only when breaking the C\textsubscript{2}C\textsubscript{3} cluster would entail creating a {\sc Sonority Angle} greater than 1.5, when the alternative of breaking the C\textsubscript{1}C\textsubscript{2} cluster would create a {\sc Sonority Angle} smaller than 1.5.
 
@@
 \hline \hline a. & \ding{43} & \textipa{j@wz1fo} & 1.33 & \cellcolor{lightgray} \\
-\hline b. & & \textipa{j@wizfo} & 2.03 $\ast$! & \cellcolor{lightgray}$\ast$ \\
+\hline b. & & \textipa{j@w1zfo} & 2.03 $\ast$! & \cellcolor{lightgray}$\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-kft-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline g. & & \textipa{j@kfito} & 2.11 $\ast$!  & \cellcolor{lightgray} \\
-\hline h. & \ding{43} & \textipa{j@kifto} & 0.59 & \cellcolor{lightgray}$\ast$ \\
+\hline \hline g. & & \textipa{j@kf1to} & 2.11 $\ast$!  & \cellcolor{lightgray} \\
+\hline h. & \ding{43} & \textipa{j@k1fto} & 0.59 & \cellcolor{lightgray}$\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(Son$\measuredangle$)}$<$1.5.
-This is possible because I have adopted the position that the {\sc Ident(Son$\measuredangle$)}$<$n constraints can be freely ranked.
+This is possible because I have adopted the position that the {\sc Ident(Son$\measuredangle$)}$<$n constraints can be freely ranked, following \cite{de.lacy.2004}.
 
@@
 
-\vspace{-3em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
+Chaha therefore presents evidence that phonetically-based faithfulness constraints that are related via stringency should be freely rankable, as has been extensively argued for markedness constraints \citep[and others]{de.lacy.2004}.
+
 \bigskip
@@
 The explanation for the special behaviour of RN clusters among triconsonantal clusters in this idiolect is similar to that of RN clusters among coda clusters: the dividing line between the conflated clusters has simply shifted to the right, at 1.9, grouping RN clusters together with sonority rises and plateaus, versus all other falls.
-This is possible using the {\sc Sonority Angle} metric because RN clusters are expected to be the most susceptible to epenthesis of all the falling sonority clusters.
+This is possible using the {\sc Sonority Angle} metric because RN clusters have the smallest angle out of all the falling sonority clusters and therefore are expected to be the most susceptible to epenthesis of these clusters.
 
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & & \textipa{j@krimo} & 1.89 $\ast$! &  \\
-\hline b. & \ding{43} & \textipa{j@kirmo} & 0.12 & $\ast$ \\
+\multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
+\hline \hline a. & & \textipa{j@kr1mo} & 1.89 $\ast$! &  \\
+\hline b. & \ding{43} & \textipa{j@k1rmo} & 0.12 & $\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}		 
@@
 
-Looking across the clusters, we find that all /r/-initial and /n/-initial triconsonantal clusters epenthesise as [CC\textipa{1}C].
+Contrary to expectations, however, all /r/-initial and /n/-initial triconsonantal clusters epenthesise as [CC\textipa{1}C].
 This seems to be due to a morphophonological constraint, as Rose states that ``[t]here is an independent requirement that if the initial root consonant of a triliteral root is /r/, it must appear in a coda in the jussive, realised as [n], except where there is a nasal in the root.'' (412, fn.
@@
 
-\noindent {\bf [C\textipa{1}CC] idiolect.} In the third idiolect \ref{C1CCidiolect} (c.f. Section 5.2 of of \citep{rose.2000}), most clusters epenthesise as [C\textipa{1}CC]. This includes clusters
-
-\ex. Default idiolect
-
-\begin{tabular}{ccccc}
+\noindent {\bf [C\textipa{1}CC] idiolect.} In the third idiolect \ref{C1CCidiolect} (c.f. Section 5.2 of of \citep{rose.2000}), most clusters epenthesise as [C\textipa{1}CC].
+
+\ex. Idiolect \ref{C1CCidiolect} \label{thirdidiolectCCCforms}
+
+\begin{longtable}{ccccc}
 	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
@@
     w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
-\end{tabular}
-
-\bigskip
-
-In this idiolect, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C\textsubscript{2}-C\textsubscript{3} constitutes a sonority rise or plateau, and C\textsubscript{1}C\textsubscript{2} constitutes a sonority fall.
+\end{longtable}
+
+\bigskip
+
+In this idiolect, the default preference is to epenthesise as [C\textipa{1}CC], but this is overridden when C\textsubscript{2}C\textsubscript{3} constitutes a sonority rise or plateau, and C\textsubscript{1}C\textsubscript{2} constitutes a sonority fall.
 
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j-a-mst-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-L Rt} \\[0.5ex]
-\hline \hline e. & & \textipa{jams1to} & 2.11 $\ast$! & \\
-\hline f. & \ding{43} & \textipa{jam1sto} & 2.03 $\ast$ & $\ast$ \\
+\hline \hline e. & & \textipa{jams1to} & 2.11 $\ast$ & \\
+\hline f. & \ding{43} & \textipa{jam1sto} & 2.03 $\ast$ & $\ast$! \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 
-This ranking predicts that fall-fall clusters should epenthesise on the left.
-Items (m) and (n) are accounted for as they are subject to the {\sc Jussive-R} constraint, but the /mst/ cluster in (o) is predicted to surface as [m\textipa{1}st], whereas Rose marks it as being epenthesised as [ms\textipa{1}t] without variation.
-On the other hand, one of Rose's constraint rankings produces this form.
-Moreover, Degif Petros Banksira (p.c.), a native speaker of Chaha, confirms that he produces the form [jam\textipa{1}sto].
+This ranking predicts that fall-fall clusters should epenthesise on the left, but they are all reported to only epenthesise on the right. 
+Of the forms in \ref{thirdidiolectCCCforms}, (m) [\textipa{j@-nf1k-o}] and (n) [\textipa{j@-nf1k-o}] are accounted for, as they are subject to the undominated {\sc Jussive-R} constraint.
+Degif Petros Banksira, a native speaker of Chaha, reports that he breaks up the /mst/ cluster in (o) on the left to form [\textipa{j-a-m1st-o}] (p.c.), although Rose marks it as being epenthesised as [\textipa{j-a-ms1t-o}] without variation.
 Therefore this prediction actually proves correct.
@@
 
-In summary, we were able to explain all four CCC idiolects of Chaha by ranking different {\sc Ident(Son$\measuredangle$)}$<$n constraints higher than either {\sc Align-Left} or {\sc Anchor-Left Root}.
+In summary, we were able to explain all four CCC idiolects of Chaha by privileging either {\sc Align-Left}, which favours epenthesis on the right or {\sc Anchor-Left}, which favours epenthesis on the left, and changing their threshold of application by ranking them with respect to an appropriate {\sc Ident(Son$\measuredangle$)}$<$n constraint.
 
@@
     \a. Idiolect \ref{defaultCCCidiolect}: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Align-L} $\gg$ {\sc Anchor-L Root}
-          \a. [CC\textipa{1}C] unless C\textsubscript{1}C\textsubscript{2} violates {\sc SyllCon}
-               (is a sonority rise or plateau) and C\textsubscript{2}-C\textsubscript{3} would not.
+          \a. $[$CC\textipa{1}C$]$ unless C\textsubscript{1}C\textsubscript{2} violates {\sc SyllCon}
+               (is a sonority rise or plateau) and C\textsubscript{2}C\textsubscript{3} would not.
           \z.
      \b. Idiolect \ref{C1CCidiolect}: {\sc SyllCon} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} 
-          \a. \item [C\textipa{1}CC] unless C\textsubscript{2}-C\textsubscript{3} violates {\sc SyllCon}
+          \a.  $[$C\textipa{1}CC$]$ unless C\textsubscript{2}C\textsubscript{3} violates {\sc SyllCon}
                 (is a sonority rise or plateau) and C\textsubscript{1}C\textsubscript{2} would not.
@@
      \c. Idiolect \ref{wizfidiolect}: {\sc SyllCon(Loose)} $\gg$ {\sc Dep} $\gg$ {\sc Anchor-L Root} $\gg$ {\sc Align-L} $\gg$ {\sc SyllCon}
-          \a. [C\textipa{1}CC] unless C\textsubscript{2}-C\textsubscript{3} violates {\sc SyllCon(Loose)} 
+          \a. $[$C\textipa{1}CC$]$ unless C\textsubscript{2}C\textsubscript{3} violates {\sc SyllCon(Loose)} 
                 (is a sonority rise) and C\textsubscript{1}C\textsubscript{2} would not.
@@
 
-In addition to these, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must again be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C\textsubscript{1}C\textsubscript{2} and C\textsubscript{2}-C\textsubscript{3} constitute violations of {\sc SyllCon}.
+In addition to these, the {\sc *MedialLight} constraint from Rose's analysis of the medial two-consonant clusters must again be invoked to prevent double epenthesis forming [C\textipa{1}C\textipa{1}C] in the case where both C\textsubscript{1}C\textsubscript{2} and C\textsubscript{2}C\textsubscript{3} constitute violations of {\sc SyllCon}.
 
@@
 The only such clusters come from the imperative/jussive CCC stem followed by the consonant-initial suffix -\textipa{n@}.
-The underlying form is /\textipa{n-CCC-n@}/.
+The underlying form is /\textipa{n-\textnormal{CCC}-n@}/.
 They surface either as [\textipa{n1\underline{\textnormal{CC}1\textnormal{C}n}@}] or [\textipa{n1\underline{\textnormal{C}1\textnormal{CC}1n}@}].

### 2013-10-07 paper.tex
Added data section to CCCC

@@
 \author{Michelle A. Fullwood}
-\date{Generals Paper, MIT \\ September 2013}
+\date{Generals Paper, MIT \\ October 2013}
 \begin{document}
@@
 
-\begin{longtable}{ccccc}
+\begin{tabular}{ccccc}
 	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
@@
     A. & \textipa{j-t-k't'@k'@t'} & \textipa{j1tk'1t'@k'@t'} & 1.37 & 1.37 \\
-\end{longtable}
+\end{tabular}
 
@@
     w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
-\end{longtable}
+\end{tabular}
 
@@
 	\node (RR) at (1.10714871779*8, 1) {RR};
-	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
+%	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
 	\node (NN) at (1.2490457724*8, 1) {NN};
@@
   \node (dividingline3end)   at (1.0 * 8,-0.3) {};
+  \node (dividingpoint3label) at (1.0*8, -1.0) {\ref{wizfidiolect}};
   \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;
-  \node (dividingpoint3label2) at (1.0*8, -1.0) {\ref{wizfidiolect}};
+
 \end{tikzpicture}
@@
   \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
+
+  % third dividing line
+  \node (dividingline3start) at (1.15 * 8,1.5) {};
+  \node (dividingline3end)   at (1.15 * 8,-1.5) {};
+  \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;
 \end{tikzpicture}
@@
 
-In this section, I will demonstrate that the rankings already obtained for CCC clusters predict almost exactly which of the CCCC clusters should display variation and in which direction.
+In this section, I will demonstrate that the four rankings already obtained in $\S$\ref{CCCanalysis} for the triconsonantal clusters predict almost exactly which of the quadriconsonantal clusters should display variation, and in which direction.
+
+\subsubsection{Data}
+
+The following table shows the observed behaviour of the quadriconsonantal clusters of Chaha, as reported by \cite{rose.2000}.
+
+\ex. Epenthetic behaviour of CCCC clusters
+
+\begin{center}
+\begin{tabular}{|cc|c|} \hline
+   & Underlying form & Observed surface forms \\ \hline
+ a.& \textipa{sdBn} & \textipa{sd1Bn} \\ 
+ b.& \textipa{wzfn} & \textipa{wz1fn}, \textipa{w1zf1n} \\
+ c.& \textipa{gdfn} & \textipa{gd1fn}, \textipa{g1df1n} \\
+ d.& \textipa{mstn} & \textipa{m1st1n} \\
+ e.& \textipa{dmdn} & \textipa{d1md1n} \\
+ f.& \textipa{drsn} & \textipa{d1rs1n} \\
+ g.& \textipa{sBxn} & \textipa{s1Bx1n} \\
+ h.& \textipa{kftn} & \textipa{k1ft1n}  \\
+ i.& \textipa{ktfn} & \textipa{kt1fn}, \textipa{k1tf1n} \\
+ j.& \textipa{sgdn} & \textipa{sg1dn}, \textipa{s1gd1n} \\
+ k.& \textipa{srBn} & \textipa{sr1Bn}, \textipa{s1rB1n} \\
+ l.& \textipa{krmn} & \textipa{kr1mn}, \textipa{k1rm1n}  \\ \hline
+ \end{tabular}
+\end{center}
 
@@
 Therefore, the only two possible solutions under my approach are [CC\textipa{1}CC] and [C\textipa{1}CC\textipa{1}C].
-Which one is chosen depends on the sonority profile of the clusters, and which of {\sc Align-Left} and {\sc Anchor-Left Root} is dominant.
+Which one is chosen depends on the sonority profile of the clusters, and which of Rose's constraints {\sc Align-Left} and {\sc Anchor-Left Root} is dominant.
 
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & Align-Left & Anchor-Left Root \\[0.5ex]
-\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$ \\
+\hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$! \\
 \hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
@@
 In this paper, I argued for sonority contour faithfulness being the right way to analyse sonority-driven epenthesis, giving case studies in Irish and Chaha as examples.
-I additionally proposed that sonority contour distance should be computed by a metric that obeys two desiderata, % TODO
+I additionally proposed that sonority contour distance should be computed by a metric that obeys two desiderata:
+
+\ex. Desiderata for a sonority contour faithfulness metric 
+     \a. The more positive the gradient of the sonority contour from C\textsubscript{1} to C\textsubscript{2}, the smaller the faithfulness cost. 
+     \b. For a given sonority distance between C\textsubscript{1} and C\textsubscript{2}, the more sonorous C\textsubscript{1} and C\textsubscript{2} are, the smaller the faithfulness cost.
 
@@
 In addition, compared to the {\sc *Dis} metric \citep{gouskova.2002} for measuring sonority distance in Syllable Contact and Sonority Sequencing, and the alternative sonority contour faithfulness metric {\sc Sonority Rise} \citep{flemming.2008}, {\sc Sonority Angle} made the correct predictions that nasal-voiceless stop and liquid-voiceless stop clusters should be the hardest to epenthesise into in Irish, and the prediction that liquid-nasal clusters should be the most susceptible to epenthesis out of the falling sonority clusters in Chaha.
+
+In Chaha, we saw more generally that the family of {\sc Ident(Son$\measuredangle$)}$<$n constraints, coupled with standard syllabic markedness constraints and alignment/anchor constraints preferring epenthesis on the left or right, yielded the complex and variable system of epenthesis positioning in the language with only one error in predictions, making it comparably successful to the existing Syllable Contact-based analysis by \cite{rose.2000}.
 

### 2013-10-07 paper.tex
Changed display of CCCC data

@@
 
-\citet{rose.2000} reformulates this as a violable, but categorical, constraint within the context of Optimality Theory and uses it in an analysis of Chaha sonority-driven epenthesis:
-
-\ex.  \textsc{SyllCon}: The first segment of the onset of a syllable must be lower in sonority than the last segment in the immediately preceding syllable.
+\cite{rose.2000} reformulates this as a violable, but categorical, constraint within the context of Optimality Theory and uses it in an analysis of Chaha sonority-driven epenthesis:
+
+\ex.  \textsc{SyllCon}: The first segment of the onset of a syllable must be lower in sonority than the last segment in the immediately preceding syllable. \citep[(5)]{rose.2000}
 
@@
 
-\ex. \a. {\sc SyllCon}: The first segment of the onset of a syllable must be lower in sonority 
-     \b. {\sc SyllCon(Loose}): The first segment of the onset of a syllable must not be of greater sonority than the last segment of the immediately preceding syllable.
+\ex. \a. {\sc SyllCon}: The first segment of the onset of a syllable must be lower in sonority  \citep[(5)]{rose.2000}
+     \b. {\sc SyllCon(Loose}): The first segment of the onset of a syllable must not be of greater sonority than the last segment of the immediately preceding syllable. \citep[(49)]{rose.2000}
 
@@
 
-In this section, I will demonstrate that the four rankings already obtained in $\S$\ref{CCCanalysis} for the triconsonantal clusters predict almost exactly which of the quadriconsonantal clusters should display variation, and in which direction.
+In this section, I will demonstrate that the four rankings already obtained in $\S$\ref{CCCanalysis} for the triconsonantal clusters generalise without modification to the CCCC clusters, predicting almost exactly which of the quadriconsonantal clusters should display variation, and in which direction.
 
@@
    & Underlying form & Observed surface forms \\ \hline
- a.& \textipa{sdBn} & \textipa{sd1Bn} \\ 
- b.& \textipa{wzfn} & \textipa{wz1fn}, \textipa{w1zf1n} \\
- c.& \textipa{gdfn} & \textipa{gd1fn}, \textipa{g1df1n} \\
- d.& \textipa{mstn} & \textipa{m1st1n} \\
- e.& \textipa{dmdn} & \textipa{d1md1n} \\
- f.& \textipa{drsn} & \textipa{d1rs1n} \\
- g.& \textipa{sBxn} & \textipa{s1Bx1n} \\
- h.& \textipa{kftn} & \textipa{k1ft1n}  \\
- i.& \textipa{ktfn} & \textipa{kt1fn}, \textipa{k1tf1n} \\
- j.& \textipa{sgdn} & \textipa{sg1dn}, \textipa{s1gd1n} \\
- k.& \textipa{srBn} & \textipa{sr1Bn}, \textipa{s1rB1n} \\
- l.& \textipa{krmn} & \textipa{kr1mn}, \textipa{k1rm1n}  \\ \hline
+ a.& \textipa{n-sdB-n@} & \textipa{n1sd1Bn@} \\ 
+ b.& \textipa{n-wzf-n@} & \textipa{n1wz1fn@}, \textipa{n1w1zf1n@} \\
+ c.& \textipa{n-gdf-n@} & \textipa{n1gd1fn@}, \textipa{n1g1df1n@} \\
+ d.& \textipa{n-mst-n@} & \textipa{n1m1st1n@} \\
+ e.& \textipa{n-dmd-n@} & \textipa{n1d1md1n@} \\
+ f.& \textipa{n-drs-n@} & \textipa{n1d1rs1n@} \\
+ g.& \textipa{n-sBx-n@} & \textipa{n1s1Bx1n@} \\
+ h.& \textipa{n-kft-n@} & \textipa{n1k1ft1n@}  \\
+ i.& \textipa{n-ktf-n@} & \textipa{n1kt1fn@}, \textipa{n1k1tf1n@} \\
+ j.& \textipa{n-sgd-n@} & \textipa{n1sg1dn@}, \textipa{n1s1gd1n@} \\
+ k.& \textipa{n-srB-n@} & \textipa{n1sr1Bn@}, \textipa{n1s1rB1n@} \\
+ l.& \textipa{n-krm-n2} & \textipa{n1kr1mn@}, \textipa{n1k1rm1n@}  \\ 
+ m.& \textipa{n-nk'm-n@}& \textipa{n1nk'1mn@} \\
+ n.& \textipa{n-nfk-n@} & \textipa{n1nf1kn@} \\
+ o.& \textipa{n-rmd-n@} & \textipa{n1rm1dn@} \\ 
+ p.& \textipa{n-k'ff-n@} & \textipa{n1k'f1fn@} \\
+ q.& \textipa{n-sdd-n@}  & \textipa{n1sd1dn@} \\ \hline
  \end{tabular}
@@
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c:c|} \hline 
-\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & Align-Left & Anchor-Left Root \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/\textipa{n-\textnormal{CCC}-n@}/} & {\sc Align-Left} & {\sc Anchor-Left Rt} \\[0.5ex]
 \hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$! \\

### 2013-10-08 paper.tex
Added acknowledgments

@@
 
-\ex. TODO
+\ex. No linear separation between the rising and level sonority clusters plus RN from the rest of the falling sonority clusters under the {\sc Sonority Rise} metric.
 
@@
 
-\ex. TODO
+\ex. No linear separation between the rising and level sonority clusters plus RN from the rest of the falling sonority clusters under the {\sc Dis} metric.
 
@@
 
-\ex. TODO
+\ex. {\sc *CCC} $\gg$ {\sc Dep}
 
@@
                       \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
-                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
+%                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
                       \node[left] at  (0,3) {C$_1$}; 
@@
                       \node[right] at (5,6) {V};
+    \coordinate (A) at (0,3);
+    \coordinate (B) at (5,1);
+    \coordinate (C) at (5,6);
+\tkzMarkAngle[size=1.5cm](B,A,C)
+\tkzLabelAngle[pos=2](B,A,C){$\theta$}
 					  % right diagram
                       \draw (15,3) -- (20,1) -- (15,6) ; % falling sonority
-                      \node at (17.5, 2.75) {$\theta$}; % theta label for falling sonority
+%                      \node at (17.5, 2.75) {$\theta$}; % theta label for falling sonority
                       \node[left] at (15,3) {C$_1$}; 
@@
                       \node[right] at (13,6) {V};
+    \coordinate (D) at (15,3);
+    \coordinate (E) at (20,1);
+    \coordinate (F) at (15,6);
+\tkzMarkAngle[size=2.5cm](F,E,D)
+\tkzLabelAngle[pos=3](D,E,F){$\theta$}
 \end{tikzpicture} 
@@
 The answer, currently, is based purely on empirical grounds: if we assume this comparison to be the relevant one, then we expect falling sonority contours to be more susceptible to epenthesis, which contradicts the cross-linguistic evidence.
-It would seem that there is something quite fundamental about the comparison being centred around the rightward context, or release, of C\textsubscript{1}, which may perhaps arise out of phonological processing.
+It would seem that there is something quite fundamental about the comparison being centred around the offset of C\textsubscript{1} rather than the C\textsubscript{1}, which may arise out of perception or phonological processing.
+
+For instance, it is well known that CV cues are much more robust than VC cues. %TODO : citation
+This could
 
@@
 Ultimately, this was not an issue because the behaviour of all such clusters was independently determined by {\sc Jussive-R}, but this raises the question of how {\sc Sonority Angle} should be computed if C\textsubscript{1} changes.
-Currently, it is undefined, as it is unclear how to measure the angle between C\textsubscript{1}C\textsubscript{2}=RF and C\textsubscript{1}V=NV:
-
-\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
+Currently, it is undefined, as it is unclear how to measure the angle between C\textsubscript{1}C\textsubscript{2}=RF and C\textsubscript{1}V=NV (shown below on the left).
+A similar situation arises if C\textsubscript{1}C\textsubscript{2}=NF and C\textsubscript{1}V=FV (shown on the right):
+
+\ex. Two scenarios under which {\sc Sonority Angle} is not well-defined:
+
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
                       \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
@@
                       \node[right] at (5,6) {\textipa{1}};
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % right diagram
+                      \draw (15,2) -- (10,3);
+                      \draw (10,4) -- (15,6) ; % rising sonority
+                      \node[left] at  (10,3) {n}; 
+                      \node[left] at  (10,4) {r}; 
+                      \node[right] at (15,2) {f};
+                      \node[right] at (15,6) {\textipa{1}};
 \end{tikzpicture}
-
-It is of course possible to define the angle as whatever is made by the intersection of the two vectors, but there is insufficient data to support this interpretation.
-Alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.
-
-\bigskip
-
-\noindent {\bf Horizontal distance.} In this paper, I assumed that the horizontal distance between C\textsubscript{1} and C\textsubscript{2}, and C\textsubscript{1} and V, is the same, and arbitrarily fixed at 1 unit, in calculating {\sc Sonority Angle}.
+\end{center}
+
+Several possibilities are possible: retain the sonority of the underlying C\textsubscript{1} for that of the output value; use the sonority of the output C\textsubscript{1} as the underlying value; or take the angle formed by the meeting of the two contours wherever it occurs.
+
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % left diagram
+                      \draw (5,2) -- (0,4);
+                      \draw (0,3) -- (5,6) ; % rising sonority
+                      \node[left] at  (0,4) {r}; 
+                      \node[left] at  (0,3) {n}; 
+                      \node[right] at (5,2) {f};
+                      \node[right] at (5,6) {\textipa{1}};
+                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
+                      \node at (-3, 7.0) {Sonority}; % axis label
+					 % right diagram
+                      \draw (15,2) -- (10,3);
+                      \draw (10,4) -- (15,6) ; % rising sonority
+                      \node[left] at  (10,3) {n}; 
+                      \node[left] at  (10,4) {r}; 
+                      \node[right] at (15,2) {f};
+                      \node[right] at (15,6) {\textipa{1}};
+\end{tikzpicture}
+\end{center}
+
+The case studies here constitute insufficient data to conclude if any of these interpretations is correct.
+It is worth noting, however, that alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.
+
+\bigskip
+
+\noindent {\bf Choice of horizontal distance.} In this paper, I assumed that the horizontal distance between C\textsubscript{1} and C\textsubscript{2}, and C\textsubscript{1} and V, is the same, and arbitrarily fixed at 1 unit, in calculating {\sc Sonority Angle}.
 This is an arbitrary choice, and potentially an important one, as when the horizontal distance gets large, changes occur in the cluster hierarchy, some of which violate the first desideratum for a sonority angle metric:
@@
 
-\noindent {\bf Arbitrariness of the sonority scale.} A third issue faced by any sonority metric is the arbitrariness of the vertical, sonority scale used in this paper.
+\noindent {\bf Choice of sonority scale.} A third issue faced by any sonority metric is the arbitrariness of the vertical, sonority scale used in this paper.
 The scale adopted, which is a relatively standard scale, is rather phonological in nature, placing each sonority class at a distance of 1 from the next, and ignoring all differences between consonants within each class.
@@
 
+\section*{Acknowledgments}
+
+I would like to thank Donca Steriade, Adam Albright, Michael Kenstowicz, Edward Flemming, Suyeon Yun, Gretchen Kern, Hrayr Khanjian, and audiences at the MIT Phonology Circle and Manchester Phonology Meeting for valuable feedback on this project.
+This material is based upon work supported by the National Science Foundation Graduate Research Fellowship Program under Grant No.
+1122374.
+
 \bibliographystyle{apalike}

### 2013-10-09 paper.tex
Second draft done

@@
 
-% faithfulness conflation?
-
-In the final tally, the {\sc Sonority Angle}-based approach fares worse on one datapoint and uses approximately the same number of constraints, but manages to accomplish most of the work of the analysis with the only crucial ranking being the placement of a single {\sc Ident(Son$\measuredangle$)}$<$n constraint with respect to a relevant $\mathcal{M}$ constraint, while in Rose's analysis this work is spread over a number of different sonority-related constraints.
+The more complex case of Chaha three- and four-consonant clusters also revealed that the {\sc Ident(Son$\measuredangle$)}$<$n constraints must be freely-rankable rather than fixed in a universal ranking.
+This allowed for faithfulness conflation of clusters both above and below a markedness constraint.
+
+In the final tally, the {\sc Sonority Angle}-based approach fares worse on one datapoint and uses approximately the same number of constraints, but manages to accomplish most of the work of the analysis by ranking a single {\sc Ident(Son$\measuredangle$)}$<$n constraint with respect to a relevant $\mathcal{M}$ constraint, while in Rose's analysis this work is spread over a number of different sonority-related constraints.
 
@@
 
-For instance, it is well known that CV cues are much more robust than VC cues. %TODO : citation
-This could
+For instance, it is well known that CV cues are much more robust than VC cues \citep{wright.2004}.
+This could be the reason for the offset of the consonant vastly outweighing the onset in terms of importance. Other sources for this asymmetry are also possible.
 
@@
 \noindent {\bf Choice of horizontal distance.} In this paper, I assumed that the horizontal distance between C\textsubscript{1} and C\textsubscript{2}, and C\textsubscript{1} and V, is the same, and arbitrarily fixed at 1 unit, in calculating {\sc Sonority Angle}.
-This is an arbitrary choice, and potentially an important one, as when the horizontal distance gets large, changes occur in the cluster hierarchy, some of which violate the first desideratum for a sonority angle metric:
+This is an arbitrary choice, and potentially an important one.
+While the horizontal distance is of a similar magnitude to the values of the sonority scale, the {\sc Sonority Angles} are more or less as we expect, but when the horizontal distance is made very large, changes occur in the cluster hierarchy, some of which violate the first desideratum for a sonority contour distance metric.
+While it is still true that keeping C\textsubscript{1} fixed, raising C\textsubscript{2} decreases the {\sc Sonority Angle} (compare TR vs TN vs TF vs TT, for example), we no longer have a linear separation of the three broad classes of sonority rises, sonority plateaus and sonority falls.
 
@@
 
-\ex. Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}
+\ex.
+Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}\footnote{The intensity values measured for the three vowel classes are reversed from what one would expect according to phonological sonority \citep[214]{parker.2002}}, but overall this shows a good correlation with scales of phonological sonority.
+The distinction between some of these classes is not significant, including between the high and mid vowels.
 
@@
 
-Using this scale, we obtain the desired empirical results of this paper based on the evidence of Irish and Chaha, that RN is the most epenthesisable of all the falling sonority clusters and tha RT and NT are the clusters most resistant to epenthesis.
+Using this scale, we obtain the desired empirical results of this paper based on the evidence of Irish and Chaha, that RN is the most epenthesisable of all the falling sonority clusters and that RT and NT are the clusters most resistant to epenthesis.
 However, this does not conform to the general principle that for a given sonority distance, the more sonorous the consonants, the more likely a cluster is to undergo epenthesis --- we have NF being harder to epenthesise into than FT, here.
@@
 Moreover, this result is obtained by averaging stops and fricatives to ignore voicing.
-If we leave voicing intact, then these results disappear: fricative-voiceless stops are the most likely to undergo epenthesis of the falling sonority clusters, more so than liquid--nasal clusters, and if RT and NT fail to undergo epenthesis, we expect voiced fricative--voiced stop, nasal--voiceless fricative, and nasal--voiced stop clusters to also resist epenthesis.
+If we leave voicing intact, then these results disappear: fricative--voiceless stops are the most likely to undergo epenthesis of the falling sonority clusters, more so than liquid--nasal clusters, and if RT and NT fail to undergo epenthesis, we expect voiced fricative--voiced stop, nasal--voiceless fricative, and nasal--voiced stop clusters to also resist epenthesis.
 Both of these are contrary to the empirical results of this paper.
@@
 
-\noindent{\bf Consonant deletion.} The current formulation of {\sc Ident(Son$\measuredangle$)}$<$n constraints restricts its application to when the consonants of a C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} sequence stand in correspondence.
-However, another formulation is possible, in which sonority contours are a property of C\textsubscript{1} rather than a property of the whole contour.\footnote{Thanks to Adam Albright for this suggestion.}
-
-\bigskip
-
-\noindent [This section remains to be written]
-
-\ex. TODO: formulate this
-
-A possible application of this looser definition of {\sc Sonority Angle} lies in the deletion of consonants in complex onsets. (pa vs pla) - loanwords, Sanskrit reduplication
+\noindent{\bf Consonant cluster simplification.} The current formulation of {\sc Ident(Son$\measuredangle$)}$<$n constraints restricts its application to when the consonants of a C\textsubscript{1}C\textsubscript{2} and C\textsubscript{1}VC\textsubscript{2} sequence stand in correspondence.
+However, another formulation is possible, in which offset sonority contours are a property of C\textsubscript{1} rather than a property of the whole contour.
+
+\ex.
+\textsc{Ident(Son$\measuredangle$)}$<$n: For every input segment with an output correspondent, assign a violation mark if the angle between the offset sonority vectors from the segment in the input and output have a {\sc Sonority Angle} greater than $n$.
+
+In revising this definition, we open up the possibility of applying {\sc Sonority Angle} to a larger class of phonological phenomena, such as consonant cluster simplification.
+For instance, in Sanskrit, reduplicants (underlined) with complex onsets are simplified:
+
+\ex. \a. \underline{kan}-i-krand `cry out (intensive)'
+     \c. \underline{sa}-swar `sound (perfective)'
+     \c. \underline{tu}-stu `praise (perfective)'
+     \z.
+     \citep{steriade.1988} and \citep{parker.2002}
+
+The observation is that the less sonorous of the two consonants is retained in the onset.
+What governs this choice?
+Traditionally, this has been analysed in terms of {\it the emergence of the unmarked}, with classes of consonants that are less marked in onset position --- i.e.
+less sonorous --- more likely to surface \citep{mccarthy.prince.1999}.
+However, another approach based on sonority contour faithfulness is also possible.
+
+Consider the kan-krand case.
+The sonority contours to be considered are /kr/-[ka].
+Both are rising sonority contours, so the {\sc Sonority Angle} will be fairly small at 0.12.
+Deletion of the /t/ in /stu/, on the other hand, would result in a falling sonority contour /st/ becoming a rising sonority contour [su], incurring a {\sc Sonority Angle} cost of 2.11.
+In both cases, deleting the first consonant would result in no violations of {\sc Ident(Son$\measuredangle$)}$<$n, according to the current definition, but this might violate constraints such as {\sc Left-Anchor}, which insist on an element on the left edge of a stem having a correspondent in the output \citep{mccarthy.prince.1999}.
+The following ranking thus predicts the deletion behaviour seen above.
+
+\ex. {\sc Ident(Son$\measuredangle$)}$<$2.0 $\gg$ {\sc Left-Anchor}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{krand}/} & {\sc Ident(Son$\measuredangle$)}$<$2.0 & {\sc Left-Anchor} \\[0.5ex]
+\hline \hline a. & \ding{43} & \textipa{kan} & 0.12 & \\
+\hline b. & & \textipa{ran} & & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/\textipa{stu}/} & {\sc Ident(Son$\measuredangle$)}$<$2.0 & {\sc Left-Anchor} \\[0.5ex]
+\hline \hline c. & \ding{43} & \textipa{su} & 2.11 $\ast$! & \\
+\hline d. & & \textipa{tu} & & $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+\bigskip
+
+To conclude this section, we see that the possible applications of sonority contour faithfulness are broad, encompassing many sonority-sensitive phonological processes.
+However, to pin down the exact parameters of the metric require more work.
 

### 2013-10-09 paper.tex
Added epenthetic vowel identity section

@@
 
+\noindent {\bf Choice of epenthetic vowel.} Cross-linguistically, the most common epenthetic vowels are [\textipa{1}] and [\textipa{@}], as exemplified by the two case studies here \citep{lombardi.2002}.
+These are also the lowest sonority vowels \citep{parker.2002}.
+This has also been analysed in terms of markedness of the various vowel features \citep{lombardi.2002}, although this leads to problematic implications: if [\textipa{1}] and [\textipa{@}] are so unmarked, why are they not more common across vowel inventories?
+
+Under the sonority contour faithfulness analysis of epenthesis, however, that epenthetic vowels are less sonorous falls out immediately.
+Keeping the height of the epenthetic along the sonority scale as low as possible guarantees the smallest possible {\sc Sonority Angle}.
+
+\ex. Illustration: keeping C\textsubscript{1} -- C\textsubscript{2} fixed, raising the sonority of V increases the {\sc Sonority Angle}
+
+\begin{center}
+\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+                      \draw [<-] (-3,12) -- (-3, 0.5) ; % axis
+                      \node at (-3, 13.0) {Sonority}; % axis label
+					 % left diagram
+    \coordinate (A) at (0,4); % pivot - C1 - F * 3
+    \coordinate (B) at (15,2); % C2 - T * 3
+    \coordinate (C) at (15,12); % V
+    \coordinate (D) at (15,14); % V2
+    \draw (B) -- (A) -- (C);
+    \draw (B) -- (A) -- (D);
+	\tkzMarkAngle[size=1.5](B,A,C);
+	\tkzLabelAngle[pos=2.5](B,A,C){$\theta_1$};
+	\tkzMarkAngle[size=4](B,A,D);
+	\tkzLabelAngle[pos=5.5](B,A,D){$\theta_2$};
+
+    \node[left] at  (A) {F}; 
+    \node[right] at (B) {T};
+    \node[right] at (C) {\textipa{1}};
+    \node[right] at (D) {\textipa{e}};
+    \draw [->,dotted] (C) -- (D);
+\end{tikzpicture} 
+\end{center}
+
+This cannot be the whole story as other vowels are permitted to be epenthetic as well, for example [a], a low and extremely sonorous vowel, is epenthetic in several languages \citep{lombardi.2002}.
+Still, sonority contour faithfulness can potentially explain a large swathe of the epenthetic vowel typology.
+
+\bigskip
+
 To conclude this section, we see that the possible applications of sonority contour faithfulness are broad, encompassing many sonority-sensitive phonological processes.

### 2013-10-09 paper.tex
Lots of minor changes

@@
 
-Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority.
+Vowel epenthesis often appears to preferentially target consonant clusters with rising sonority, as in the following example of English loanwords borrowed into Hawai'ian creole.
+The rising sonority onset cluster is adapted with epenthesis, while the falling sonority cluster is left intact.
+
+\ex. \a. puranti: `plenty'
+    \b. ste: `stay'
+    \z.
+    (\cite{nagara.1972}, cited by \cite{fleischhacker.2005})
+
 There are two broad classes of explanation within Optimality Theory for such sonority-driven epenthesis.
@@
 Thus, epenthesis into such a sequence incurs a smaller faithfulness cost than epenthesis into a cluster of falling sonority.
-This is the basis of the analysis proposed by Fleischhacker (2002, 2005) to explain why rising sonority obstruent-sonorant clusters are more easily epenthesised in
+This is the basis of the analysis proposed by \cite{fleischhacker.2002, fleischhacker.2005} to explain why rising sonority obstruent-sonorant clusters are more easily epenthesised in
 to than falling sonority sibilant-stop clusters.
 
-This faithfulness-based approach raises the question of how the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] should be computed in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
+This raises the question of how the perceptual distance between two sonority contours /C\textsubscript{1}C\textsubscript{2}/ and [C\textsubscript{1}VC\textsubscript{2}] should be computed in terms of the sonority of C\textsubscript{1}, C\textsubscript{2} and V.
 
@@
 sonority-driven epenthesis. I introduce the proposed {\sc Sonority Angle} metric as well as the competing {\sc Sonority Rise} metric \citep{flemming.2008}, 
-then lay out the alternative markedness-based approach to sonority-driven epenthesis, namely Syllable Contact.
+then lay out the alternative markedness-based approach to sonority-driven epenthesis.
 
@@
 
-Section \ref{chaha} is a case study of epenthesis positioning in Chaha.  I detail the facts of epenthesis positioning in Chaha, based on the data given in \citet{rose.2000},
+Section \ref{chaha} is a case study of epenthesis positioning in Chaha.  I detail the facts of epenthesis positioning in Chaha, based on data from \cite{rose.2000},
 and show that the sonority contour faithfulness approach explains these facts, with {\sc Sonority Angle} as the metric for comparing sonority contours.
-I compare it to {\sc Sonority Rise} and show that the former is the more successful analysis, and that overall, the approach just outlined is more economical than the  Syllable Contact-based approach of \citet{rose.2000}.
-
-Section \ref{issues} looks at various issues regarding {\sc Sonority Angle}, such as its robustness. Section \ref{conclusion} concludes.
+I compare it to {\sc Sonority Rise} and show that the former is the more successful analysis, and that overall, the approach just outlined is comparably successful to the Syllable Contact-based approach of \citet{rose.2000}.
+
+Section \ref{issues} discusses various issues regarding {\sc Sonority Angle}, such as its robustness. Section \ref{conclusion} concludes.
 
@@
 The second generalisation is that the more sonorous the C\textsubscript{1}, the more likely
-epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at 2, but vary their distance from V:
-
-\newpage
+epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at 2, but vary their distance from V. Decreasing this distance decreases the {\sc Sonority Angle}.
 
@@
 There are two possible ways to rank the family of {\sc Ident(Son$\measuredangle$)}$<$n constraints.
-One is to fix them in a universal ranking \citep{prince.smolensky.1993}, with least stringent the highest-ranked:
+One is to fix them in a universal ranking \citep{prince.smolensky.1993}, with the least stringent constraint the highest-ranked:
 
@@
 
-\ex. Possible free ranking:
+\ex. Possible free ranking: \label{freerankingex}
      {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Ident(Son$\measuredangle$)}$<$2.0 $\gg$ ...
 
-Depending on what constraints intervene, this may result in conflation of certain areas of the hierarchy, so that any distinctions between {\sc Sonority Angles} between 1.5 and 2.0 are made irrelevant.
+This represents a slight deviation from the P-map hypothesis \citep{steriade.2001} in implementation, though not in spirit.
+Because the constraints form a stringency hierarchy, there cannot be reversals of the cluster hierarchy.
+What may occur is the {\it conflation} of certain areas of the constraint hierarchy, such as all the clusters with {\sc Sonority Angles} between 1.5 and 2.0 in \ref{freerankingex}, depending on what constraints intervene.
+Some illustrative examples are given below.
 
@@
      \a. Allows epenthesis in rising and level clusters such as stop-fricative TF:
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \b. Prevents epenthesis in falling clusters such as FT:
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \ex. {\sc *ComplexCoda} $\gg$ {\sc Max}(r) $\gg$ {\sc Dep}
-
+\vspace{-1em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \ex. {\sc *ComplexCoda}, {\sc Ident(Son$\measuredangle$)}$<$2.3  $\gg$ {\sc Max}(r) $\gg$ {\sc Dep}
-
+\vspace{-1em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
-While other analyses could possibly account for this data (see one such in \citep{karim.2011}), we see that simply ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{F}$ allows us to account for it quite straightforwardly.
+While other analyses could possibly account for this data (see one such in \cite{karim.2011}), we see that simply ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{F}$ allows us to account for it quite straightforwardly.
 
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-\bigskip
+\vspace{0.5em}
 
@@
          Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
       \b. Scenario 2: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
           C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em} \newpage
      \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
          {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
          Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
 
@@
 \noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchycompressed}}
+
+\vspace{-1em}
 
@@
 
+\vspace{-1.5em}
 \begin{center}
@@
 
-The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect \citep[cited in \citep{rose.2000}]{greenberg.1950}.
+The only clusters that give us evidence of this are /\textipa{Bm}/ clusters. These are not seen root-internally due to a high-ranking OCP effect \citep[cited in \cite{rose.2000}]{greenberg.1950}.
 I suggest that there might be an undominated markedness constraint against this cluster -- either OCP(labial) or another constraint based on articulatory or perceptual difficulty -- that outranks all relevant faithfulness constraints.
@@
 
-\bigskip
 \resizebox{\linewidth}{!}{
@@
 In addition, Sonority Sequencing does not allow a divide of the [r]-sonorant clusters versus the remainder of the clusters, whether in Rose's categorical formulation of Sonority Sequencing or a family of {\sc *Dis} constraints.
+
+\newpage
 
@@
 
+\newpage
 \ex. {\sc *CCC} $\gg$ {\sc Dep}
 
+\vspace{-2em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
-\begin{tabular}{ccccc}
+\begin{longtable}{ccccc}
 	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
@@
 
+\vspace{-2em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \ex. \a. Behaviour of clusters with C\textsubscript{2}=/r/ and C\textsubscript{3}=sonorant under idiolect \ref{defaultCCCidiolect}:
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}		 
+\vspace{0.5em}
      \b. Behaviour of clusters with C\textsubscript{2}=/r/ and C\textsubscript{3}=sonorant under idiolect \ref{CRNidiolect}:
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & \ding{43} & \textipa{j@krimo} & 1.89 & \\
-\hline b. & & \textipa{j@kirmo} & 0.12 & $\ast$! \\
+\hline \hline c. & \ding{43} & \textipa{j@krimo} & 1.89 & \\
+\hline d. & & \textipa{j@kirmo} & 0.12 & $\ast$! \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 
-\ex. \begin{center} \renewcommand*\arraystretch{1.2}
+\newpage
+\ex. Current ranking predicts incorrect form for cluster /rmd/.
+
+\vspace{-2em}
+\begin{center} \renewcommand*\arraystretch{1.2}
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
@@
 
-\noindent {\bf [C\textipa{1}CC] idiolect.} In the third idiolect \ref{C1CCidiolect} (c.f. Section 5.2 of of \citep{rose.2000}), most clusters epenthesise as [C\textipa{1}CC].
+\noindent {\bf [C\textipa{1}CC] idiolect.} In the third idiolect \ref{C1CCidiolect} (c.f. Section 5.2 of \cite{rose.2000}), most clusters epenthesise as [C\textipa{1}CC].
 
@@
 
-\begin{tabular}{ccccc}
+\vspace{-1em}
+\begin{longtable}{ccccc}
 	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
@@
     f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
-    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\ \hline
+    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\  \newpage \hline 
     \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [C\textipa{1}CC]} \\ \hline
@@
     w. & \textipa{j-a-mrg-o} & \textipa{jam1rgo} & 0.46 & 2.36 \\ \hline
-\end{tabular}
+\end{longtable}
 
@@
 
+\vspace{-1.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
+\newpage
+
 \ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Anchor-Left Root} \label{CCiCidiolectranking}
      \a. Fall-\{Rise, Plateau\}
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \b. \{Rise, Plateau\}-\{Rise, Plateau\}
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \c. Fall-Fall
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}%h%
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \d. \{Rise, Plateau\}-Fall
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
+\newpage 
 \ex. \a. /\textipa{j@-wzf-o}/ can surface as [\textipa{j@-w1zf-o}], but this is not predicted by any ranking so far, including \ref{CCiCidiolectranking}
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \b. /\textipa{j@-sgd-o}/ can surface as [\textipa{j@-s1gd-o}], but this is not predicted by any ranking so far, including \ref{CCiCidiolectranking}
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \ex. {\sc Ident(Son$\measuredangle$)}$<$1.0 $\gg$ {\sc Anchor-L-Root}
-     \a. \begin{center} \renewcommand*\arraystretch{1.2}
+\vspace{-1em}
+     \begin{center} \renewcommand*\arraystretch{1.2}
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-     \b. \begin{center} \renewcommand*\arraystretch{1.2}
+     \begin{center} \renewcommand*\arraystretch{1.2}
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
@@
 
+\vspace{-2em}
 \begin{center}
-\begin{tabular}{|cc|c|} \hline
+\begin{longtable}{|cc|c|} \hline
    & Underlying form & Observed surface forms \\ \hline
@@
  q.& \textipa{n-sdd-n@}  & \textipa{n1sd1dn@} \\ \hline
- \end{tabular}
+ \end{longtable}
 \end{center}
+
+\vspace{-2em}
 
@@
 \ex. {\sc Align-Left} favours [CC\textipa{1}CC], but {\sc Anchor-Left Rt} favours [C\textipa{1}CC\textipa{1}C].
-
+\vspace{-1em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Align-Left}
+\vspace{-0.5em}
      \a. Case 1: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$<$1.5
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \b.
 Case 2: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$>=$1.5 but so is one of {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) or {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex] 
-\hline \hline a. & \ding{43} & \textipa{n1sr1Bn@} & 1.57 $\ast$ &  \\
-\hline b. & & \textipa{n1s1rB1n@} & 0.22, 1.65$\ast$ & $\ast$! \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\hline \hline c. & \ding{43} & \textipa{n1sr1Bn@} & 1.57 $\ast$ &  \\
+\hline d. & & \textipa{n1s1rB1n@} & 0.22, 1.65$\ast$ & $\ast$! \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
       \c.
 Case 3: {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$>=$1.5 and both {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) and {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})$<$1.5
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{n-dmd-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. &  & \textipa{n1dm1dn@} & 2.3 $\ast$!   & \cellcolor{lightgray} \\
-\hline b. & \ding{43} & \textipa{n1d1md1n@} & 0.27, 0.27 & \cellcolor{lightgray} $\ast$ \\
+\hline \hline e. &  & \textipa{n1dm1dn@} & 2.3 $\ast$!   & \cellcolor{lightgray} \\
+\hline f. & \ding{43} & \textipa{n1d1md1n@} & 0.27, 0.27 & \cellcolor{lightgray} $\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 
+\newpage
 \ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Anchor-Left Rt}
      \a. Case 1: Both {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) and {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4})$<$1.5
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \b.
 Case 2: {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) or {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4}) $>=$1.5, but so is {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{n-srB-n@}/} & {\sc Ident(Son$\measuredangle$)}$<$1.5 & {\sc Anchor-Left Rt} \\[0.5ex]
-\hline \hline a. &  & \textipa{n1sr1Bn@} & 1.57 $\ast$ & $\ast$! \\
-\hline b. & \ding{43} & \textipa{n1s1rB1n@} & 0.22, 1.65$\ast$ &  \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\hline \hline c. &  & \textipa{n1sr1Bn@} & 1.57 $\ast$ & $\ast$! \\
+\hline d. & \ding{43} & \textipa{n1s1rB1n@} & 0.22, 1.65$\ast$ &  \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+\vspace{0.5em}
      \c.
 Case 3: {\sc Sonority Angle}(C\textsubscript{1},C\textsubscript{2}) or {\sc Sonority Angle}(C\textsubscript{3},C\textsubscript{4}) $>=$1.5, and {\sc Sonority Angle}(C\textsubscript{2},C\textsubscript{3})$<$1.5
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 
-There is only one incorrect prediction, namely that /mstn/ should surface as [\textipa{ms1tn}] in idiolects \ref{defaultCCCidiolect} and \ref{CRNidiolect}, but Rose indicates that there is no variation.
+\newpage
+
+There is only one incorrect prediction, namely that /mstn/ should surface as [\textipa{ms1tn}] in idiolects \ref{defaultCCCidiolect} and \ref{CRNidiolect}, but Rose indicates that there is no variation in this form.
 It is possible that this is simply a form that does undergo variation but the predicted [\textipa{ms1tn}] variant has not been observed in Rose's corpus.
@@
 
-\begin{center}
-\begin{tikzpicture} [shorten >=1pt,scale=0.33]
+\vspace{-1em} \hspace{1.5in}
+\begin{tikzpicture} [scale=0.33]
   \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
@@
   % left diagram
-                      \draw (5,1) -- (0,3) -- (5,6) ; % rising sonority
-%                      \node at (1.8, 3.2) {$\theta$}; % theta label for rising sonority
-                      \node[left] at  (0,3) {C$_1$}; 
-                      \node[right] at (5,1) {C$_2$};
-                      \node[right] at (5,6) {V};
     \coordinate (A) at (0,3);
@@
     \coordinate (C) at (5,6);
+  \draw (B) -- (A) -- (C) ; % rising sonority
+  \node[left] at  (A) {C$_1$}; 
+  \node[right] at (B) {C$_2$};
+  \node[right] at (C) {V};
 \tkzMarkAngle[size=1.5cm](B,A,C)
 \tkzLabelAngle[pos=2](B,A,C){$\theta$}
+
 % right diagram
-                      \draw (15,3) -- (20,1) -- (15,6) ; % falling sonority
-%                      \node at (17.5, 2.75) {$\theta$}; % theta label for falling sonority
-                      \node[left] at (15,3) {C$_1$}; 
-                      \node[right] at (20,1) {C$_2$};
-                      \node[right] at (13,6) {V};
     \coordinate (D) at (15,3);
@@
     \coordinate (F) at (15,6);
+    \draw (D) -- (E) -- (F) ; % falling sonority
+    \node[left] at (D) {C$_1$}; 
+    \node[right] at (E) {C$_2$};
+    \node[right] at (F) {V};
 \tkzMarkAngle[size=2.5cm](F,E,D)
@@
 \end{tikzpicture} 
-\end{center}
+\bigskip
 
@@
 
-Several possibilities are possible: retain the sonority of the underlying C\textsubscript{1} for that of the output value; use the sonority of the output C\textsubscript{1} as the underlying value; or take the angle formed by the meeting of the two contours wherever it occurs.
+Several possibilities are possible: retain the sonority of the underlying C\textsubscript{1} for that of the output value; use the sonority of the output C\textsubscript{1} as the underlying value; or take the angle formed by the meeting of the two contours, wherever that occurs.
 

### 2013-10-21 paper.tex
Minor formatting changes

@@
 
-\ex. \label{sonangle_formula} Formula: \textsc{SonAngle} = $arctan(V-C_1) - arctan(C_2-C_1)$
+\ex. \label{sonangle_formula} Formula: {\sc Son$\measuredangle$} = $arctan(V-C_1) - arctan(C_2-C_1)$
 
@@
 
-\ex. \a. \textsc{SonAngle}(NT) =  $arctan(6-3) - arctan(1-3)$ = 2.35
-     \b. \textsc{SonAngle}(TT) =  $arctan(6-1) - arctan(1-1)$ = 1.37
-     \c. \textsc{SonAngle}(TN) =  $arctan(6-1) - arctan(3-1)$ = 0.27
+\ex. \a. {\sc Son$\measuredangle$}(NT) =  $arctan(6-3) - arctan(1-3)$ = 2.35
+     \b. {\sc Son$\measuredangle$}(TT) =  $arctan(6-1) - arctan(1-1)$ = 1.37
+     \c. {\sc Son$\measuredangle$}(TN) =  $arctan(6-1) - arctan(3-1)$ = 0.27
 
@@
 
-\vspace{-3em}
+\vspace{-2em}
 \begin{center} \renewcommand*\arraystretch{1.2}
 \scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Id(SA)}$<$2.0 & {\sc Id(SA)}$<$1.5 & {\sc *CompCoda} & {\sc Id(SA)}$<$1.0 & {\sc Id(SA)}$<$0.5 \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Id(S$\measuredangle$)}$<$2.0 & {\sc Id(S$\measuredangle$)}$<$1.5 & {\sc *CompCoda} & {\sc Id(S$\measuredangle$)}$<$1.0 & {\sc Id(S$\measuredangle$)}$<$0.5 \\[0.5ex]
 \hline \hline a. & & TF & & & $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} \\
@@
 {\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
-\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Id(SA)}$<$2.5 & {\sc Id(SA)}$<$1.5 & {\sc *CompCoda} & {\sc Id(SA)}$<$1.0 & {\sc Id(SA)}$<$0.5 \\[0.5ex]
+\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Id(S$\measuredangle$)}$<$2.5 & {\sc Id(S$\measuredangle$)}$<$1.5 & {\sc *CompCoda} & {\sc Id(S$\measuredangle$)}$<$1.0 & {\sc Id(S$\measuredangle$)}$<$0.5 \\[0.5ex]
 \hline \hline c. & \ding{43}& FT & & & \cellcolor{lightgray} $\ast$ & \cellcolor{lightgray} & \cellcolor{lightgray} \\
@@
 \ex. {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$
-     \a. Scenario 1: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
+     \a. Scenario 1: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}), {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3})$<$n \\
          Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
@@
 \vspace{0.5em}
-      \b. Scenario 2: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
+      \b. Scenario 2: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3})$<$n \\
           C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
@@
 \vspace{0.5em} \newpage
-     \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
+     \c. Scenario 3: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3})$>$n \\
          {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
@@
 \vspace{0.5em}
-     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
+     \d. Scenario 4: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}), {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
          Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
@@
 
-\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\
+\ex. Scenario: {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\
 
@@
   \node (2pointlabel) at (2.0*8,-0.5) {2};
-  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
+  \node (xaxislabel) at (2.7*8,-0.5) {{\sc Son$\measuredangle$}};
   % dividing line
@@
 \begin{longtable}{ccccc}
-	& Underlying form      & Surface form & {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) & {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
+	& Underlying form      & Surface form & {\sc Son$\measuredangle$}(C\textsubscript{1},C\textsubscript{2}) & {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3}) \\ \hline
     \multicolumn{5}{c}{Fall-\{Rise, Plateau\}: [CC\textipa{1}C]} \\ \hline
@@
 For instance, consider the cluster /mst/.
-{\sc SonAngle}(m,s), at 2.03, is smaller than {\sc SonAngle}(s,t), at 2.11, yet epenthesis occurs on the right, creating the larger {\sc Sonority Angle}.
+{\sc Son$\measuredangle$}(m,s), at 2.03, is smaller than {\sc Son$\measuredangle$}(s,t), at 2.11, yet epenthesis occurs on the right, creating the larger {\sc Sonority Angle}.
 This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(Son$\measuredangle$)}$<$1.5.
@@
 
-Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n.
+Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc Son$\measuredangle$}(C\textsubscript{1},C\textsubscript{2}) and {\sc Son$\measuredangle$}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n.
 Illustrative tableaux are shown below for n=1.5:
@@
 Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C].
-This preference is overridden when at least one of {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are greater than n and {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) is less than n.
+This preference is overridden when at least one of {\sc Son$\measuredangle$}(C\textsubscript{1},C\textsubscript{2}) and {\sc Son$\measuredangle$}(C\textsubscript{3},C\textsubscript{4}) are greater than n and {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3}) is less than n.
 
@@
 \begin{tabular}{|l|ccc|c|cccc|} \hline
-         & \multicolumn{3}{c|}{{\sc SonAngles}} & Observed & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
+         & \multicolumn{3}{c|}{{\sc Son$\measuredangle$s}} & Observed & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
  Cluster & C\textsubscript{1},C\textsubscript{2} & C\textsubscript{2},C\textsubscript{3} & C\textsubscript{3},C\textsubscript{4} &  outcomes & \ref{defaultCCCidiolect} & \ref{CRNidiolect} & \ref{C1CCidiolect} & \ref{wizfidiolect} \\ \hline
@@
 
-\begin{center}
-\begin{tikzpicture} [shorten >=1pt,scale=0.33]
-                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
-                      \node at (-3, 7.0) {Sonority}; % axis label
-					 % left diagram
-                      \draw (5,2) -- (0,4);
-                      \draw (0,3) -- (5,6) ; % rising sonority
-                      \node[left] at  (0,4) {r}; 
-                      \node[left] at  (0,3) {n}; 
-                      \node[right] at (5,2) {f};
-                      \node[right] at (5,6) {\textipa{1}};
-                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
-                      \node at (-3, 7.0) {Sonority}; % axis label
-					 % right diagram
-                      \draw (15,2) -- (10,3);
-                      \draw (10,4) -- (15,6) ; % rising sonority
-                      \node[left] at  (10,3) {n}; 
-                      \node[left] at  (10,4) {r}; 
-                      \node[right] at (15,2) {f};
-                      \node[right] at (15,6) {\textipa{1}};
-\end{tikzpicture}
-\end{center}
-
-The case studies here constitute insufficient data to conclude if any of these interpretations is correct.
+The two case studies examined above present insufficient data to conclude if any of these interpretations is correct.
 It is worth noting, however, that alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.
@@
   \node  (0point) at (0.0,0) {};
-  \node (xaxislabel) at (0.06*300,-0.8) {\textsc{SonAngle}};
+  \node (xaxislabel) at (0.06*300,-0.8) {{\sc Son$\measuredangle$}};
 \end{tikzpicture}
@@
 \ex.
-Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}\footnote{The intensity values measured for the three vowel classes are reversed from what one would expect according to phonological sonority \citep[214]{parker.2002}}, but overall this shows a good correlation with scales of phonological sonority.
-The distinction between some of these classes is not significant, including between the high and mid vowels.
+Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}\footnote{The intensity values measured for the three vowel classes are reversed from what one would expect according to phonological sonority \citep[214]{parker.2002}, but overall this shows a good correlation with scales of phonological sonority.
+The distinction between some of these classes is not significant, including between the high and mid vowels.}
 
@@
   \node (2pointlabel) at (2.0*8,-0.5) {2};
-  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
+  \node (xaxislabel) at (2.7*8,-0.5) {{\sc Son$\measuredangle$}};
 \end{tikzpicture}
@@
 
+\vspace{-0.5em}
 \begin{center} \renewcommand*\arraystretch{1.2}
@@
 \hline b. & & \textipa{ran} & & $\ast$! \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-\begin{center} \renewcommand*\arraystretch{1.2}
-\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
+\hline \hline
 \multicolumn{3}{|c||}{Input:~/\textipa{stu}/} & {\sc Ident(Son$\measuredangle$)}$<$2.0 & {\sc Left-Anchor} \\[0.5ex]
@@
 More perceptual experiments and cross-linguistic investigation of sonority-driven epenthesis needs to be done to pin down the specifics of the metric.
-In addition, I discussed two other sonority-based phenomena that may shed additional light on the true nature of sonority contour faithfulness.
+In addition, I discussed three other sonority-based phenomena that may shed additional light on the true nature of sonority contour faithfulness.
 
@@
 
-\bibliographystyle{apalike}
+\bibliographystyle{unified}
 \bibliography{sonangle}

### 2013-10-21 paper.tex
Edits based on MK's comments

@@
 \vspace{0.5em}
-     \d. Scenario 4: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}), {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
+     \d. Scenario 4: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}), {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\ \label{relevantscenario}
          Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
@@
 
-\ex. Scenario: {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\
+\ex. Scenario: {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\ \label{tableauabove}
 
@@
 \multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Ident(Son$\measuredangle$)}$<$1.5 &$ \mathcal{M}$  \\[0.5ex]
-\hline \hline a. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} &  2.0 $\ast$!  & \cellcolor{lightgray} 2.0 $\ast$ & \cellcolor{lightgray} \\
-\hline b.  & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} &  1.7  & \cellcolor{lightgray} 1.7 $\ast$ & \cellcolor{lightgray} $\ast$ \\
-\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
-
-Under a universal ranking of {\sc Ident(Son$\measuredangle$)}$<$n constraints, [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] would win in this scenario.
-In an equivalent scenario under free ranking, where {\sc Ident(Son$\measuredangle$)}$<$1.5 is the least stringent constraint to outrank $\mathcal{M}$, which in turn outranks all more stringent {\sc Ident(Son$\measuredangle$)}$<$n constraints, the [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}] candidate would win instead.
-There would be conflation of all clusters with {\sc Sonority Angles} below $n$, but distinctions between clusters with {\sc Sonority Angles} would still be relevant.
+\hline \hline a. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} &  2.0 $\ast$!  & \cellcolor{lightgray} 2.0 $\ast$ & \cellcolor{lightgray} \\
+\hline b.  &\ding{43}  & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} &  1.7  & \cellcolor{lightgray} 1.7 $\ast$ & \cellcolor{lightgray} $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+As the tableau in \ref{tableauabove} illustrates, under a universal ranking of {\sc Ident(Son$\measuredangle$)}$<$n constraints, [C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}] would be the winning candidate.
+
+Under free-ranking where {\sc Ident(Son$\measuredangle$)}$<$1.5 is the least stringent constraint to outrank markedness, we have the opposite result.
+
+\ex. Opposite result under free ranking where all more stringent {\sc Ident(Son$\measuredangle$)}$<$n constraints are ranked below $\mathcal{M}$.
+
+\vspace{-2em}
+\begin{center} \renewcommand*\arraystretch{1.2}
+\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|} \hline 
+\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} &  {\sc Ident(Son$\measuredangle$)}$<$1.5 &$ \mathcal{M}$ & {\sc Ident(Son$\measuredangle$)}$<$1.9 \\[0.5ex]
+\hline \hline a. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} &  2.0 $\ast$ & & \cellcolor{lightgray} 2.0 $\ast$ \\
+\hline b. &  & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} &  1.7 $\ast$ &  $\ast$! & \cellcolor{lightgray}  1.7 $\ast$ \\
+\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
+
+If both epenthesis sites would result in a {\sc Sonority Angle} larger than the least stringent $n$ to outrank markedness, the candidate that satisfies markedness, [C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}], wins instead.
+There would be conflation of all clusters with {\sc Sonority Angles} above and below $n$.
 
@@
 
-However, out of the three clusters with a sonority distance of -1, RN has the largest {\sc Sonority Rise}, and therefore is expected to be more resistant to epenthesis than NF and FT.
+However, out of the three clusters FT, NF and RN with a sonority distance of -1, RN has the largest {\sc Sonority Rise}, and therefore is expected to be more resistant to epenthesis than NF and FT.
 This is contrary to criterion \ref{desideratum_b}.
-If RN undergoes epenthesis, therefore, we predict FT and NF to do the same.
+If RN undergoes epenthesis, therefore, we predict FT and NF to do the same by the {\sc Sonority Rise} metric.
 
@@
 \a.
-More sonorous plateaus are more likely to undergo epenthesis under the {\sc Sonority Angle} metric, whereas all the level clusters should have equal likelihood of being broken up by epenthesis.
+More sonorous plateaus are more likely to undergo epenthesis under the {\sc Sonority Angle} metric, whereas all the level clusters should have equal likelihood of being broken up by epenthesis under {\sc Sonority Rise}.
      \b. RN is more likely to undergo epenthesis than NF under {\sc Sonority Angle}, and vice versa under {\sc Sonority Rise}.
@@
 
-Epenthesis does not break up onset sonorant-initial clusters.  This is likely due to the fact that
+Epenthesis does not break up word-initial sonorant-C clusters.  This is likely due to the fact that
 with a small number of lexical exceptions, Irish words are stress-initial \citep[26]{o.siadhail.1989}.\footnote{With the exception of Munster Irish, where stress is attracted to syllables containing
@@
     \draw (axisstart) -- (axisend);
-   \node (xaxislabel) at (2.6 * 15,-2.0) {\textsc{Sonority Rise}};
+   \node (xaxislabel) at (2.6 * 15,-2.0) {\textsc{SonRise}};
 
@@
 
-\ex. Table showing epenthesis patterns for clusters of varying sonority patterns:
+\newpage
+
+\ex.
+Table showing epenthesis patterns for clusters of varying sonority patterns:\footnote{No specific examples are available in \citep{rose.2000} for the gaps in the table, but their pattern of epenthesis is implied in the text and Rose's analysis.}
 
@@
 In addition, Sonority Sequencing does not allow a divide of the [r]-sonorant clusters versus the remainder of the clusters, whether in Rose's categorical formulation of Sonority Sequencing or a family of {\sc *Dis} constraints.
-
-\newpage
 
@@
 
-\newpage
 \ex. {\sc *CCC} $\gg$ {\sc Dep}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-krm-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
-\hline \hline c. & \ding{43} & \textipa{j@krimo} & 1.89 & \\
-\hline d. & & \textipa{j@kirmo} & 0.12 & $\ast$! \\
+\hline \hline c. & \ding{43} & \textipa{j@kr1mo} & 1.89 & \\
+\hline d. & & \textipa{j@k1rmo} & 0.12 & $\ast$! \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 
-\newpage
 \ex. Current ranking predicts incorrect form for cluster /rmd/.
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & \frownie & \textipa{j@rmido} & 2.36 $\ast$! & \cellcolor{lightgray} \\
-\hline b. & \ding{43} & \textipa{j@rimdo} & 1.89 & \cellcolor{lightgray}$\ast$ \\
+\hline \hline a. & \frownie & \textipa{j@rm1do} & 2.36 $\ast$! & \cellcolor{lightgray} \\
+\hline b. & \ding{43} & \textipa{j@r1mdo} & 1.89 & \cellcolor{lightgray}$\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \multicolumn{3}{|c||}{Input:~/\textipa{j@-rmd-o}/} & {\sc Jussive-R} & {\sc Ident(Son$\measuredangle$)}$<$1.9 & {\sc Align-Left} \\[0.5ex]
-\hline \hline a. & \ding{43} & \textipa{j@rmido} & & \cellcolor{lightgray}2.36 $\ast$ & \cellcolor{lightgray} \\
-\hline b. & & \textipa{j@rimdo} & $\ast$! & \cellcolor{lightgray}1.89 & \cellcolor{lightgray}$\ast$ \\
+\hline \hline a. & \ding{43} & \textipa{j@rm1do} & & \cellcolor{lightgray}2.36 $\ast$ & \cellcolor{lightgray} \\
+\hline b. & & \textipa{j@r1mdo} & $\ast$! & \cellcolor{lightgray}1.89 & \cellcolor{lightgray}$\ast$ \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
     f. & \textipa{j@-\underline{sgd}-o} & \textipa{j@sg1do}   & 2.11 & 1.37 \\  
-    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\  \newpage \hline 
+    g. & \textipa{j@-sdB-o}   & \textipa{j@sd1Bo}   & 2.11 & 0.18 \\  \hline 
     \multicolumn{5}{c}{\{Rise, Plateau\}-\{Rise, Plateau\}: [C\textipa{1}CC]} \\ \hline
@@
 
-\newpage
-
 \ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Anchor-Left Root} \label{CCiCidiolectranking}
@@
 
-\newpage 
 \ex. \a. /\textipa{j@-wzf-o}/ can surface as [\textipa{j@-w1zf-o}], but this is not predicted by any ranking so far, including \ref{CCiCidiolectranking}
@@
 \hline \hline a. & & \textipa{n1\textnormal{C.C}1\textnormal{C}.n@} & 2,3,5,6 & $\ast$! \\
-\hline b. & \ding{43} & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
+\hline b. & & \textipa{n1.\textnormal{C}1\textnormal{C.C}1.n@} & 2,4!,5,7 & \\
 \hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
@@
 \vspace{0.5em}
+ \newpage
       \c.
@@
 
-\newpage
 \ex. {\sc Ident(Son$\measuredangle$)}$<$1.5 $\gg$ {\sc Anchor-Left Rt}
@@
 
-\newpage
-
 There is only one incorrect prediction, namely that /mstn/ should surface as [\textipa{ms1tn}] in idiolects \ref{defaultCCCidiolect} and \ref{CRNidiolect}, but Rose indicates that there is no variation in this form.
@@
 The answer, currently, is based purely on empirical grounds: if we assume this comparison to be the relevant one, then we expect falling sonority contours to be more susceptible to epenthesis, which contradicts the cross-linguistic evidence.
-It would seem that there is something quite fundamental about the comparison being centred around the offset of C\textsubscript{1} rather than the C\textsubscript{1}, which may arise out of perception or phonological processing.
+It would seem that there is something quite fundamental about the comparison being centred around consonant offsets rather than onsets, which may arise out of perception or phonological processing.
 
@@
 
-\noindent {\bf Changes in C\textsubscript{1}.} In the discussion of Chaha triconsonantal clusters in  $\S$\ref{CCCanalysis}, I glossed over how the metric should be computed if C\textsubscript{1} changes.
-This was an issue in clusters such as /rfk/, which emerge as [nf\textipa{1}k] due to morphophonological processes.
+\noindent {\bf Changes in C\textsubscript{1}.} In the discussion of Chaha triconsonantal clusters in  $\S$\ref{CCCanalysis}, I glossed over how the metric should be computed if C\textsubscript{1} changes from the input to the output.
+This was the case in clusters such as /rfk/, which emerge as [nf\textipa{1}k] due to morphophonological processes.
 Ultimately, this was not an issue because the behaviour of all such clusters was independently determined by {\sc Jussive-R}, but this raises the question of how {\sc Sonority Angle} should be computed if C\textsubscript{1} changes.
-Currently, it is undefined, as it is unclear how to measure the angle between C\textsubscript{1}C\textsubscript{2}=RF and C\textsubscript{1}V=NV (shown below on the left).
-A similar situation arises if C\textsubscript{1}C\textsubscript{2}=NF and C\textsubscript{1}V=FV (shown on the right):
+Currently, it is undefined, as it is unclear how to measure the angle between underlying /C\textsubscript{1}C\textsubscript{2}/=/RF/ and surface [C\textsubscript{1}V]=[NV] (shown below on the left).
+A similar situation arises if underlying /C\textsubscript{1}C\textsubscript{2}/=/NF/ and surface [C\textsubscript{1}V]=[FV] (shown on the right):
 
@@
 
-Several possibilities are possible: retain the sonority of the underlying C\textsubscript{1} for that of the output value; use the sonority of the output C\textsubscript{1} as the underlying value; or take the angle formed by the meeting of the two contours, wherever that occurs.
+Several solutions are possible: retain the sonority of the underlying C\textsubscript{1} for that of the output value; use the sonority of the output C\textsubscript{1} as the underlying value; or take the angle formed by the meeting of the two contours, wherever that occurs.
 
 The two case studies examined above present insufficient data to conclude if any of these interpretations is correct.
-It is worth noting, however, that alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.
+It is worth noting, however, that alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] is trivial even when the underlying and surface C\textsubscript{1}'s differ.
 
@@
 
+\newpage
 \ex. {\sc Sonority Angle} hierarchy for a horizontal distance of 100 units.
@@
 
-Additionally, since this horizontal distance is along the dimension of time, the assumption that the two horizontal distance for C\textsubscript{1}C\textsubscript{2} is the same as that for C\textsubscript{1}V is likely incorrect.
+Additionally, since this horizontal distance is along the dimension of time, the assumption that the horizontal distance for C\textsubscript{1}C\textsubscript{2} is the same as that for C\textsubscript{1}V is likely incorrect.
 If we choose different values for these two horizontal distances, the cluster hierarchy would also be likely to change.
@@
 
+\newpage
 \ex.
@@
 
-So far, I have employed the {\sc Sonority Angle} metric purely in the analysis of sonority-driven epenthesis. However, there are other possible applications.
+So far, I have employed the {\sc Sonority Angle} metric solely in the analysis of sonority-driven epenthesis. However, there are other possible applications.
 
@@
 
+\newpage
 \ex. \a. Syncope allowed when falling sonority cluster is created
